### 2013-09-02 research/MCR report/main.tex
initial commit to research-2

%Mid-Year Cadidature Review Report 
%Updated on 23/08/2012 at 15.30

\documentclass{article}  
\usepackage{a4wide}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{tabulary}
\usepackage[sort]{cite}
%\usepackage[sort,nocompress]{cite}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{pdfpages}

%\title{\Huge bfseries{Towards a green optical Internet 
%jnvsjkvnsfjkvnfkjsv 
%dfdfd
%}} 
%\author{\textsf{M. Nishan Dharmaweera}}

%\year{April, 2004} 
%\department{\emph{Department of Electrical and Computer Systems Engineering}}
%\title{Towards a Green Optical Internet}
%\author{Nishan Dharmaweera \and Rajendran Parthiban \and Y. Ahmet \c{S}ekercio\u{g}lu}
\begin{document}

\begin{titlepage}
\begin{center}
{\huge \bfseries Energy harvesting using aeroelastic galloping}\\[2.5cm]
{\LARGE \bfseries H.G.K.G Jayatunga}\\[2.5cm]
\textsc{\Large Supervisors:\\[0.5cm] Dr. Tan Boon Thong \\[0.4cm] Dr. Justin Leontini \\[0.5cm] Dr Huang Yew Mun}\\[6.5cm]
\textsc{\Large Ph.D. Mid-Candidature Review Report}\\

\vfill
\textsc{\Large $27^{\text{th}}$ September 2013}
\end{center}
\end{titlepage}
%\titlepage
%\maketitle
\tableofcontents

\section{Introduction}
The search for alternative energy sources which could be categorised under the ”green”label has become important area of research in the modern word. Solar, wind power andwave power are some of the examples of these sources. Recently,a new branch of research has been developing to extract energy from flow induced vibrations. It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.
A simple structure that is susceptible to flow-induced vibrations that are suitable for energy extraction are slender structures,such as cylinders, elastically mounted perpendicular to a fluid stream. With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping. Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV. Some of their significant work includes investigating the influence  of physical parameters such as mass ratio (the ratio of the mass of the cylinder and the displaced fluid), Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}). However,the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated. Some theoretical work was carried out by (\cite{Barrero-Gil2010a}). Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).Therefore it is preferable to investigate further the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.

\section{Research focus}
 This research contributes to the existing knowledge on energy extraction from flow induced vibrations. This research focuses investigating methods to optimise the energy transfer from fluid-to-body when galloping by using theoretical methods (i.e Quasi-steady state theory and DNS simulations). Therefore the project was separated into two main phases.

\begin{enumerate}[]
\item Phase 1: To optimise the mechanical portion of the system 
\item Phase 2: To optimise the fluid dynamics portion of the system 
\end{enumerate}

\section{Research objectives}

\section{Research progress}

From the literature survey, we identified both optical-circuit switching (OCS) and optical-burst switching (OBS) to be more energy efficient in comparison to point-to-point (pt-pt) and optical-packet switching (OPS) technologies. However, both OCS and OBS face a number of challenges. Therefore, in stage two of this study, we attempted to generate novel mechanisms to increase energy efficiency in OCS and OBS based optical fiber backbone networks. 
\begin{itemize}
\item 
\end{itemize}

\begin{itemize}
\item

\end{itemize}
Finally, in stage four of this study, we intend to explore and develop novel frameworks to increase energy efficiency in an optical fiber backbone network, by utilizing either sleep mode of operation, ALR or MLR techniques. As the reader might have noticed, both sleep mode of operation and MLR were used in the two previous two stages in conjunction with OBS and WBS technologies. We are currently analysing the existing literature, and are in the process of developing an energy-aware network configuration where line cards and links in the network could move back and forth between sleep and active states depending on the network load.

With respect to the PhD thesis, each of the above stages (literature survey and the three approaches) are intended to be converted into a chapter. This is to be followed by a chapter covering the discussion and the conclusion (Appendix). During my PhD, the three main approaches are being studied concurrently. Therefore, as of today, certain tasks from each different stage have been completed. The remaining tasks are to be completed before the end of the allocated time period as explained in the Gantt chart shown in Figure 1. In conclusion, 60\% of the research work has been completed to date with 70\% of the objectives being successfully accomplished.

%\begin{figure}[h]
%\centering
%\includegraphics[width=\textwidth]{./Gantt}
%\caption{Revised Gantt Chart}
%\label{fig:Gantt}
%\end{figure}

\section{Difficulties and challenges} 
%
%\begin{enumerate}
%      
%\end{enumerate}
\bibliographystyle{elsarticle-harv}
\bibliography{../bibtex/MCR}
\appendix
%\begin{center}
%\section*{\LARGE Appendix 1}
%\addcontentsline{toc}{section}{Appendix 1} 
%\end{center}
Proposed table of contents of the final PhD thesis:
\begin{enumerate}
\item Introduction
\begin{enumerate}[i]
\item Looking forward
\item Scope of the thesis
\item Organization of the thesis
\item Objectives
\item Contributions
\item Publications 
\end{enumerate}
\item Power consumption in optical core network
\begin{enumerate}[i]
\item Introduction
\item Core network architecture
\item Core node architecture 
\item Power consumption values
\item Node-based approaches
\item Traffic engineering-based approaches
\item Network engineering-based approaches
\end{enumerate}
\item Node-based energy efficiency
\begin{enumerate}[i]
\item Introduction
\item General network model
\item Problem definition
\item Cost model
\item Energy and cost efficient algorithm
\item Framework for energy efficient OBS network
\item Summary
\end{enumerate}
\item Traffic engineering-based energy efficiency
\begin{enumerate}[i]
\item Introduction
\item Grooming based network model
\item Problem definition
\item Sparse grooming 
\item Waveband grooming 
\item Summary
\end{enumerate}
\item Network engineering-based energy efficiency \begin{enumerate}[i]
\item Introduction
\item MLR based network model
\item Problem definition
\item MLR based WBS network
\item Sleep mode enabled core network
\item Summary
\end{enumerate}
\item Conclusion
\begin{enumerate}[i]
\item Introduction
\item Summary of the work
\item Future directions
\end{enumerate}
\end{enumerate}
Each sub-section mentioned above could be further divided into sections, if necessary. For example, 3(v) could be divided as 3(v)(a) "ILP formulation", 3(v)(b) "Heuristic algorithm" and 3(v)(c) "Evaluation"
\newpage
\centering
\vspace*{2.5in}
\section*{\LARGE Appendix 2}
\addcontentsline{toc}{section}{Appendix 2} 
\includepdf[page={-}]{ICTpaper.pdf}
\end{document}

### 2013-09-02 research/paper/Theory/mathematical_model.tex
initial commit to research-2

\section{Background theory}

\subsection{Mathematical model (Quasi-steady )}

 One of the widely used mathematical model to predict the system response under galloping is the Quasi-steady state (QSS) model, incorporated by \cite{Parkinson1964} for a square cross section. The equation of motion of the body under galloping is given by Eq. \eqref{equationofmotion}. The forcing term $F_y$ is given by Eq.\eqref{lift equation}.

 \input{../figure/sketch-1}

\begin{equation}
\label{equationofmotion}
(m+m_a)\ddot{y}+c\dot{y}+ky=F_y
\end{equation}

\begin{equation}
\label{lift equation}
F_y=\frac{1}{2}\rho U^2\mathcal{A}C_y
\end{equation}

 In the QSS  model $C_y$ is determined by an interpolating polynomial based on the stationary lift and drag data. The order of the interpolation polynomial has varied from study to study. For  example a $7^{th}$ polynomial order was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}. \cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order polynomial neither provides a significantly better result nor does it exhibit an additional amplitudes of oscillation. Thus a $7 ^{th}$ order interpolating polynomial was incorporated in this present study.

\begin{equation}
\label{cy ploynomial}
C_y(\theta)=a_1\left(\frac{\dot{y}}{U}\right)+a_3\left(\frac{\dot{y}}{U}\right)^3+a_5\left(\frac{\dot{y}}{U}\right)^5+a_7\left(\frac{\dot{y}}{U}\right)^7
\end{equation}

%\begin{equation}
%\label{modified_equation_of_motion}
%\ddot{y}+c^*\dot{y}+k^*y=\frac{1}{2}\rho U^2A
%\end{equation}

\cite{Joly2012} reported a reduction of displacement amplitude at low mass ratios. Therefore in order to account for it {\Tan what is "it" ??} a sinusoidal forcing function to the RHS of the oscillator model (Eq. \eqref{equationofmotion})was introduced, in order to represent forcing due to VIV. This method provided satisfactory results with the numerical simulations obtained at low mass ratios. In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation. $\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively. Thus, the final equation is given by Eq. \eqref{final_equation_motion}.

\begin{equation}
\label{final_equation_motion}
(m{+}m_a)\ddot{y}{+}c{+}\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}
\end{equation}

This equation could be solved by time integration methods. In  this study  `Ode 45' routine in MATLAB was used to obtain the solutions.

\subsection{Calculation of average power}

 The dissipated power due to the mechanical damping could be expressed as the harvested power output assuming that the other  power dissipation due to internal damping such as friction of the system is negligible. Therefore the mean power output could be given by Eq. \eqref{power}.

 \begin{equation}
 \label{power}
P_{mean}=\frac{1}{T}\int_{0}^{T}(c\dot{y})\dot{y} dt
 \end{equation}

 \input{../figure/cy_vs_theta}
 \vspace{20mm}
 \input{../figure/coefficient-table}

\subsection{Parameters used}

The stationary data and the fluid-structure interaction (FSI) data were obtained using a higher order spectral element code which simulate 2D laminar flow. The Reynolds number was kept at 165 as it was pointed out by \cite{Sheard2009} and \cite{Tong2008} that the 3 dimensional transition for a square cylinder occurs at approximately Re=160. $F_0$ was kept at $0.4937$ which was obtained by using a simple linear interpolation on the data presented in \cite{Joly2012}. $\omega_s$ was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$. Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$. The average power was obtained by using Eq. \eqref{power} with data sets consisting substantial amount of peaks. Power data  at Re=22300 were obtained using input $C_y$ data in \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers. $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165. These parameters  were used throughout this study unless otherwise specified.

 FSI data were obtained for the oscillating (free-vibration) scenario. The Naiver-Stokes equations were solved using an accelerated frame of reference using the previously mentioned code. A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution. The details of the method could be found in \cite{Thompson2006,Thompson1996a}. This code was incorporated in \cite{Leontini2011,Leontini2007a}  where it was employed in a fluid-structure interaction problems.

 The computational domain consists of 690 quadrilateral macro elements where majority of the elements were concentrated near the square section. A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet. A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and Re $165$. A 9th order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

### 2013-09-02 research/paper/figure/coefficient-table.tex
initial commit to research-2

\begin{table}[ht]

\begin{center}
\setlength{\unitlength}{\textwidth}

\begin{tabular}{c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
\\[0.2ex]
Case & $a_1$ & $a_3$ & $a_5$ & $a_7$ \\ [0.8ex] % inserts table 
%heading
\hline 
\\[0.8ex]% inserts single horizontal line
Re=165 & 1.3 & 125.3 & 1825.73 & 8765.3 \\[0.8ex] % inserting body of the table
Re=22300 & 2.69 & 168 & 1670 & 59900 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}

\caption{Coefficient values used in the 7th order interpolation polynomial for high ($Re=22300$) and low ($Re=165$) Reynolds numbers. These data are used as input data to calculate the RHS of Eq.\ref{final_equation_motion} throughout this study.}

\label{table:nonlin} % is used to refer this table in the text
\end{center}
\end{table}

### 2013-09-02 research/paper/figure/collapsed_data.tex
initial commit to research-2

\begin{figure}
  \setlength{\unitlength}{\textwidth}

        \begin{picture}(1,0.52)

      % % % Parkinson Data 
      \put(0.025,0.27){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/velocity_amp_collapsed_parkinson.eps}}
      \put(0.495,0.27){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/velocity_amp_collapsed_re165.eps}}

      \put(0.025,0.02){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_parkinson.eps}}
      \put(0.495,0.02){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_re_165.eps}}

      \put(0.23,0.00){ $c\rho\mathcal{A}U$}
      \put(0.73,0.00){ $c\rho\mathcal{A}U$}

      \put(0.01,0.405){$\frac{V}{D}$}

      \put(0,0.13){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
      \put(0.085,0.475){\small(a)}
      \put(0.555,0.475){\small(b)}
      \put(0.085,0.225){\small(c)}
      \put(0.555,0.225){\small(d)}

    \end{picture}

  \caption{Velocity amplitude and mean power as functions of the damping factor. Data presented in (a) and (c)  were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}). Data presented in (b)and (d)  were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+). The collapsed data implies that there is no frequency selection and the tuning parameter of the mechanical side of the system is the damping constant to obtain an optimum power output.}
    \label{fig:collpased_data}
\end{figure}

\ %vspace{10cm}

### 2013-09-02 research/paper/figure/cy_vs_theta.tex
initial commit to research-2

\begin{figure}

  \setlength{\unitlength}{\textwidth}
  \begin{picture}(1,0.25)(0,0.8)

    % % %90
      \put(0.025,0.81){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/lift_curve_165.eps}}
      \put(0.495,0.81){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/lift_curve_park.eps}}
 	\put(0.02,0.93){ \large $C_y$} 	
% 	\put(0.56,1.02){ $\theta$}

        \put(0.25,0.8){ $\theta$} 	
        \put(0.75,0.8){ $\theta$}

        \put(0.105,1.01){(a)}
        \put(0.565,1.01){(b)}
      \end{picture}

  \caption{Lift coefficient, $C_y$ \JL{$C_y$ is upper case here, lower case on the figure. Make them match what is in the nomenclature}, as a function of incidence angle $\theta$, for a static square cross section. (a) Data from simulations at $Re=165$  (b) data from \cite{Parkinson1964} at $Re=22300$. Points ($\bullet$) are measurements from the simulations. The solid lines in both plots are 7th-order interpolating polynomial used to predict the fluid forcing for the QSS model.}
    \label{fig:lift_curves}
\end{figure}

### 2013-09-02 research/paper/figure/m_star_collapsed.tex
initial commit to research-2

\begin{figure}
\setlength{\unitlength}{\textwidth}

  \begin{picture}(1,0.35)(0,0.75)

  \put(0.15,0.76){\includegraphics[width=0.7\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}

 	\put(0.11,0.95){\large $\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

 	 	\put(0.45,0.75){ $c\rho\mathcal{A}U$}

  \end{picture}

  \caption{Mean power as a function of damping factor. Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 and $\zeta=0.1$. A reduction of maximum mean power can be observed when $m^*<40$. For $m^*>40$, the maximum power is essentially independent of $m^*$.}
    \label{fig:m_star_collapsed}
\end{figure}

### 2013-09-02 research/paper/figure/qss_fsi.tex
initial commit to research-2

\begin{figure}
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(1,0.25)
    % % %90
    \put(0.02,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/fsi_displacement.eps}}
    \put(0.36,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/fsi_velocity.eps}}
    \put(0.72,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/fsi_power.eps}}

    \put(0.03,0.17){$\frac{A}{D}$}
    \put(0.36,0.17){$\frac{V}{D}$}
    \put(0.68,0.17){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

    \put(0.18,0.0){\ustar} 	
    \put(0.51,0.0){\ustar}
    \put(0.87,0.0){\ustar}

    \put(0.092,0.21){\small(a)}
    \put(0.42,0.21){\small(b)}
    \put(0.78,0.21){\small(c)}

  \end{picture}

  \caption{Comparison of data generated using the quasi-static theory (\ding{83}) and full DNS simulations (\ding{108}). (a) Displacement amplitude, (b) velocity amplitude and (c) mean power as functions of \ustar. Data were obtained at $Re=165$ and $\zeta=0.075$. An average difference of $34\%$ is observed for both displacement and velocity amplitude. However, the essential physics i.e the rise and fall of mean power, is captured by DNS simulations.}
    \label{fig:FSI_QSS_compare}
\end{figure}

### 2013-09-02 research/paper/figure/uncollapsed_data.tex
initial commit to research-2

\begin{figure}
  \setlength{\unitlength}{\textwidth}

  \begin{picture}(1,0.72)
%(0,0.35)

    % % %Parkinson Data 
    \put(0.025,0.48){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/displacement_amp_re_parkinson_1.eps}}
    \put(0.025,0.25){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/velocity_amp_re_parkinson.eps}}
    \put(0.025,0.02){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_re_parkinson.eps}}

    % Re 165 Data 
    \put(0.495,0.48){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/displacement_amp_re165.eps}}
    \put(0.495,0.25){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/velocity_amp_re165.eps}}
    \put(0.495,0.02){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_re_165.eps}}

%    \put(0.25,0.93){\ustar}
%    \put(0.8,0.93){\ustar}
%    \put(0.25,0.63){\ustar}
%   \put(0.8,0.63){\ustar}
    \put(0.25,0.0){\ustar}
    \put(0.75,0.0){\ustar}

    \put(0.00,0.685){$\frac{A}{D}$}
%    \put(0.52,1.075){$\frac{A}{D}$}
    \put(0.00,0.44){$\frac{V}{D}$}
%    \put(0.52,0.83){$\frac{V}{D}$}
    \put(-0.01,0.15){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
%    \put(0.5,0.54){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

    \put(0.085,0.685){\small(a)}
    \put(0.555,0.685){\small(b)}
    \put(0.085,0.455){\small(c)}
    \put(0.555,0.455){\small(d)}
    \put(0.085,0.225){\small(e)}
    \put(0.555,0.225){\small(f)}   
  \end{picture}

%  \vspace{-4cm}
  \caption{Velocity amplitude, displacement amplitude and mean power  as functions of $U^*$. Data presented in (a), (c) and (e) were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}). Data presented in (b),(d) and (f) were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+). The multiple branches for the higher Re are due to the hysteresis between two solutions.}

  \label{fig:uncollapsed_data}
\end{figure}

### 2013-09-02 research/paper/figure/velocity_compare.tex
initial commit to research-2

\begin{figure}
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(1,0.3)(0,0.8)
    % % %90
    \put(0.025,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_60_0.075.eps}}
    \put(0.495,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_165_0.175.eps}}

    \put(0.03,0.95){ $\frac{V}{D}$} 	
    % \put(0.56,1.02){ $\frac{V}{D}$}

    \put(0.25,0.805){ $\frac{tU}{D}$} 	
    \put(0.73,0.805){ $\frac{tU}{D}$}

    \put(0.095,1.03){(a)}
    \put(0.565,1.03){(b)}

  \end{picture}

  \caption{Time histories of velocity at two different $\zeta$ and $U^*$ which produce the same mean power ($1.2\times10^{-3}$). Data presented in (a) are at $\ustar=60$, $\zeta=0.075$ and (b) are at $\ustar=165$, $\zeta=0.175$. Both data sets were obtained using Quasi-steady state assumption using input $C_y$ parameters at $Re=165$. Shedding is evident in both signals as a high frequency fluctuation but the amplitude of the slower fluctuations remains constant in both cases.}
    \label{fig:time_hostory_velocity_same_power}
\end{figure}

### 2013-09-02 research/paper/introduction/intro-1.0.tex
initial commit to research-2

\section{Introduction}

The search for alternate energy sources which could be categorised  under the "green" label has become important area of research in the modern word. Solar, wind power and wave power are some of the examples of these sources.  Recently,a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}). It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.

A simple structure that is susceptible to flow-induced vibrations that are suitable for energy extraction are slender structures,such as cylinders, elastically mounted perpendicular to a fluid stream. With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping. Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV. Some of their significant work includes investigating the influence  of physical parameters such as mass ratio (the ratio of the mass of the cylinder and the displaced fluid), Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}). However,the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated. Some theoretical work was carried out by (\cite{Barrero-Gil2010a}). Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).Therefore it is preferable to investigate further the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.

Real life energy harvesting systems use high damping ratios where the energy generator (e.g electrical generator) puts a significant amount of damping into the system. Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems in laminar flow.

According to \cite{Paidoussis2010},\cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.  \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines. A non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory. Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model. It essentially used a curve fit of the transverse force to predict the galloping response. The study managed to achieve a good agreement with experimental (wind tunnel) data.\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio, which the  (QSS) model fails to reproduce. The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory. In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio the mass-damping ($m^*\zeta$) parameter should be kept low as well as the frequency of oscillations should be carefully matched \hilight{have a good agreement with the size of the cross section}. Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

### 2013-09-02 research/paper/nomenclature.tex
initial commit to research-2

\textbf{Nomenclature}

\begin{tabular}{ll}
$a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
$C_y$ & instantaneous lift \\
$F_y$ & force due to $C_y$  \\ 
$\rho$ & fluid density  \\
$m$ & mass of the body \\
$m_a$ & added mass \\
$c$ & damping constant/damping factor \\
$k$ & spring constant \\
$U_i$ & induced velocity \\
$\theta$ & induced angle of incidence \\
$U$ & freestream velocity \\
$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration   \\
$A$ & displacement amplitude\\
$\mathcal{A}$ & cross sectional area\\ 
$F_0$& force due to shedding \\
$\omega_s$& vortex shedding frequency \\
$t$ & time \\
$P_{mean}$& mean power \\
$f=\frac{1}{2\pi}\sqrt{\frac{k}{m}}$& natural frequency of the system \\
$\omega_n= 2 \pi f$& natural frequency of the system  \\
$D$ & characteristic length of the body  \\
$m^*=\frac{m}{\rho \times \text{Volume of the body}}$& mass ratio \\
$U^*=\frac{U}{f \times D}$& reduced velocity  \\
$\zeta= \frac{c}{2 m \omega_n}$& damping ratio \\
$P_t$   & power transferred to the body by the fluid \\
$P_d$& power dissipated due to mechanical damping  \\
$Re$& Reynolds number  \\
$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle \\
& \\
& \\
\end{tabular}

### 2013-09-02 research/paper/results/results-2.3.tex
initial commit to research-2

\section{Results}

\subsection{Stationary data}

The stationary $C_y$ data obtained using DNS simulations (Fig.\ref{cy ploynomial}(a))have a good agreement with data presented in \cite{Joly2012}. In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed. The peak value of $C_y$ is  significantly lower at low  at \reynoldsnumber=165. The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165. This agrees with the findings of \cite{Luo2003}. It was concluded by \cite{Luo2003} that hysteresis occur due to the inflection point found in the $C_y$ curve. Therefore hysteresis is not expected at \reynoldsnumber=165. The range where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0-6^0$) compared to \reynoldsnumber=22300 ($0^0-15^0$). This is quite significant due to the fact that it will effect the direction of power transfer which will be explained in subsections later. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a lot less power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.

\input{../figure/uncollapsed_data}

\subsection{Displacement,velocity and power output as a function of reduced velocity}

 The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ Fig.\ref{fig:uncollapsed_data} (a) and (b). The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers. This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}. Hysteresis could be observed at higher Reynolds numbers.

 \subsubsection*{Power vs $U^*$}

 The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$. A shift of the peak power could be observed as $\zeta$ increases. However, the magnitude of the peaks remain constant for all the values of $\zeta$. A similar observation could be made from the results of \cite{Barrero-Gil2010a}. It could be observed that unlike VIV the  system has no preferred frequency. Although the onset of galloping and the point where peak power occur at different $U^*$ when the damping ratio is changed, the peak power remains constant regardless of $U^*$.

 \subsection{Galloping response and natural frequency}

 If the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective (disregarding the shedding term as the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency), it is obvious the forcing term on RHS of the equation is only dependent on transverse velocity($\dot{y}$) which is essentially the input power of the system. On the RHS, the mechanical damping or system damping is the only term that takes out power at any instant. This could be expressed as the product of damping force and the velocity ($P_d$). The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces i.e there is zero net energy in or out of the system when averaged over a period. Therefore that the system is governed by the transverse velocity rather than the natural frequency.

 Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency. The effect of fixing $\zeta$ and increasing $U^*$ actually decreases damping constant for a fixed free-stream velocity. ($U^*=\frac{U}{f \times D}$, $\zeta= \frac{c}{2 m \omega_n}$ ). Both these effects leads to the multiple lines that are horizontally transpose when $\zeta$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)). Therefore the effect of $\zeta$ essentially scales up the damping coefficient for a fixed $U^*$.

 A single set of results for a given $C_y$ curve could be obtained for the displacement, velocity and power were plotted as a function of damping constant $c$ 
(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)). Fig.\ref{fig:time_hostory_velocity_same_power} clearly shows that a similar velocity amplitude could be obtained for a given damping factor provided that the small fluctuations are disregarded.

\input{../figure/collapsed_data}

\input{../figure/velocity_compare}

 Power could be expressed as the product of force and velocity. Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected . Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output powe when the reduced velocity is increased. The key regions consists of region 1 where the $P_m$ increases with \ustar, region 2 where $P_m$ becomes maximum and region 3 where $P_m$ decreases with \ustar. It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative. Maximum amount of power could be transferred within the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{../FnP/sketch_1}
\caption{ Three key regions taken into account to analyse the time histories of power in a typical mean power vs. $U^*$ curve at $Re=165$. In region 1, high damping suppresses oscillation, hence the power output is low. In region 2, the damping is close to the optimum for power transfer. In region 3, the low damping means little energy is extracted from the fluid.}
\label{fig:regions_1}
\end{figure}

 At region 1 where $U^*=90$ (region 1) the damping constant is high and therefore a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ Fig. \ref{fig:power_time_histories} (a). Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$. Hence both $P_d$ and $P_t$ becomes sinusoidal. However, due to the higher damping  $\theta$ does not go to the region which produces the peak power.

At region 2 ($U^*=165$) the mean power output is at its maximum. $P_t$ is not a pure sinusoidal signal. However, the  signal remains periodic. From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)). In this case at certain point in time $\theta$ arrives at the region where $F_y$ decreases but does not become negative when the angle is increased. Therefore, the force $F_y$ and $P_t$ reduces as the velocity further increased. This is because $\theta = tan^{-1}(\frac{\dot{y}}{U})$ and $\theta$ is proportional to  transverse velocity. As the velocity $\dot{y}$ is sinusoidal, $\theta$ recovers back and this leads to two `peaks'  in a single half cycle.

 At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output. Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle. This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive. As the force opposes the direction of travel, the power becomes negative. On the other hand from an energy perspective we could see that the mechanical damping is not sufficient to dissipate out the energy transferred from the fluid to the structure (as `$c$' is substantially low), therefore  part of this energy is transferred back to the fluid which is depicted as a negative power region in Fig.\ref{fig:power_time_histories} (c).

\input{../figure/time_histories}

\subsection{Effect of $m^*$}

 \input{../figure/m_star_collapsed}

The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$. However, at $m^* \leq 30$ an effect of $m^*$ it could be observed. The peak value of the mean power curve reduces with $m^*$. This may be due to the fact that as the inertia of the system is reduced and galloping becomes weak. Therefore shedding become dominant. This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.

 \input{../figure/qss_fsi}

\subsection{Comparison with FSI simulations}
 Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig. \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)). Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data. Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare}(c)). However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased. The reasoning behind this fact is that galloping is weak at Re 165  and therefore fluid damping has a significant effect. It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$. As power is function of $(\dot{y})^2$ the error between QSS and FSI power becomes significantly large.

 Put conclusion here

%\section{Conclusion}

 % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2013-09-03 research/paper/Theory/mathematical_model.tex
corrections made Dr Kenny's partially done

@@
 
- In the QSS  model $C_y$ is determined by an interpolating polynomial based on the stationary lift and drag data.
+ In the QSS  model $C_y$ is determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various angles of attack.
 The order of the interpolation polynomial has varied from study to study.
@@
 
-\cite{Joly2012} reported a reduction of displacement amplitude at low mass ratios.
-Therefore in order to account for it {\Tan what is "it" ??} a sinusoidal forcing function to the RHS of the oscillator model (Eq.
-\eqref{equationofmotion})was introduced, in order to represent forcing due to VIV.
-This method provided satisfactory results with the numerical simulations obtained at low mass ratios.
+\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing.
+This enables to model to provide accurate predictions even at low mass ratios where galloping \hilight{....} suppressed or not present.
 In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation.
@@
 
- The dissipated power due to the mechanical damping could be expressed as the harvested power output assuming that the other  power dissipation due to internal damping such as friction of the system is negligible.
-Therefore the mean power output could be given by Eq.
-\eqref{power}.
+ The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq. \eqref{power}.
 
@@
 
-The stationary data and the fluid-structure interaction (FSI) data were obtained using a higher order spectral element code which simulate 2D laminar flow.
+The stationary data and the fluid-structure interaction (FSI) data were obtained using a higher order spectral element code to simulate the two-dimensional laminar flow.
 The Reynolds number was kept at 165 as it was pointed out by \cite{Sheard2009} and \cite{Tong2008} that the 3 dimensional transition for a square cylinder occurs at approximately Re=160.
 $F_0$ was kept at $0.4937$ which was obtained by using a simple linear interpolation on the data presented in \cite{Joly2012}.
-$\omega_s$ was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$.
+Shedding frequency $\omega_s$ was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$.
 Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$.

### 2013-09-03 research/paper/introduction/intro-1.0.tex
corrections made Dr Kenny's partially done

@@
 
-A simple structure that is susceptible to flow-induced vibrations that are suitable for energy extraction are slender structures,such as cylinders, elastically mounted perpendicular to a fluid stream.
+An elastically mounted slender structure such as cylinders \hilight{......} which  are susceptible to flow-induced vibrations has the potential for energy extraction.
 With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping.
 Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV.
-Some of their significant work includes investigating the influence  of physical parameters such as mass ratio (the ratio of the mass of the cylinder and the displaced fluid), Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}).
+Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}).
 However,the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated.
 Some theoretical work was carried out by (\cite{Barrero-Gil2010a}).
-Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).Therefore it is preferable to investigate further the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.
+Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).
+This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.
 
-Real life energy harvesting systems use high damping ratios where the energy generator (e.g electrical generator) puts a significant amount of damping into the system.
-Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems in laminar flow.
+Energy harvesting systems have high damping ratios because the energy generator (e.g electrical generator) puts a significant amount of damping into the system.
+Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.
 
@@
 It essentially used a curve fit of the transverse force to predict the galloping response.
-The study managed to achieve a good agreement with experimental (wind tunnel) data.\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio, which the  (QSS) model fails to reproduce.
+The study managed to achieve a good agreement with experimental data.\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio, which the  (QSS) model fails to reproduce.
 The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.

### 2013-09-04 research/paper/Theory/mathematical_model.tex
applied kenny's changes

@@
 \cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing.
-This enables to model to provide accurate predictions even at low mass ratios where galloping \hilight{....} suppressed or not present.
+This enables to model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present.
 In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation.
@@
 The Reynolds number was kept at 165 as it was pointed out by \cite{Sheard2009} and \cite{Tong2008} that the 3 dimensional transition for a square cylinder occurs at approximately Re=160.
-$F_0$ was kept at $0.4937$ which was obtained by using a simple linear interpolation on the data presented in \cite{Joly2012}.
-Shedding frequency $\omega_s$ was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$.
+$F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \cite{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.
+
+Shedding frequency $\omega_s$, was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$.
 Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$.
 The average power was obtained by using Eq.
-\eqref{power} with data sets consisting substantial amount of peaks.
-Power data  at Re=22300 were obtained using input $C_y$ data in \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers.
+\eqref{power}
+
+and the averaging was done over no less than 20 galloping periods.
+Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (\ref{table:cy-coefficients}) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers.
 $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.

### 2013-09-04 research/paper/introduction/intro-1.0.tex
applied kenny's changes

@@
 
-An elastically mounted slender structure such as cylinders \hilight{......} which  are susceptible to flow-induced vibrations has the potential for energy extraction.
+An elastically mounted slender structure such as cylinders which  are susceptible to flow-induced vibrations has the potential for energy extraction.
 With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping.

### 2013-09-04 research/paper/results/results-2.3.tex
applied kenny's changes

@@
 
-The stationary $C_y$ data obtained using DNS simulations (Fig.\ref{cy ploynomial}(a))have a good agreement with data presented in \cite{Joly2012}.
+The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a))have a good agreement with data presented in \cite{Joly2012}.
 In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed.
-The peak value of $C_y$ is  significantly lower at low  at \reynoldsnumber=165.
+The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) .
 The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165.
@@
 Therefore hysteresis is not expected at \reynoldsnumber=165.
-The range where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0-6^0$) compared to \reynoldsnumber=22300 ($0^0-15^0$).
-This is quite significant due to the fact that it will effect the direction of power transfer which will be explained in subsections later.
-Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a lot less power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.
+The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$).
+This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angle because fluid forces are acting in the direction of travel of the oscillating cylinder.
+Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction.
+Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a significant reduction in power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.
 
@@
 This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}.
-Hysteresis could be observed at higher Reynolds numbers.
+Hysteresis could be observed for the case with a higher Reynolds number.
 

### 2013-09-04 research/paper/introduction/intro-1.0.tex
uploaded 6.16mp Malaysian time

@@
 It essentially used a curve fit of the transverse force to predict the galloping response.
-The study managed to achieve a good agreement with experimental data.\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio, which the  (QSS) model fails to reproduce.
+The study managed to achieve a good agreement with experimental data.
+The QSS model equation when solved using analytically using sinusoidal solution mehod cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
 The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.

### 2013-09-05 research/paper/figure/collapsed_data.tex
new files added

@@
 
-        \begin{picture}(1,0.52)
+        \begin{picture}(1,0.74)
 
       % % % Parkinson Data 
+      \put(0.025,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/displacement_amp_collapsed_parkinson.eps}}
       \put(0.025,0.27){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/velocity_amp_collapsed_parkinson.eps}}
@@
       \put(0.495,0.02){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_re_165.eps}}
+      \put(0.495,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/displacement_amp_collpased_re165.eps}}
 
@@
 
-      \put(0.01,0.405){$\frac{V}{D}$}
+      \put(0.01,0.405){$\frac{V}{D}$}\
+       \put(0.01,0.63){$\frac{A}{D}$}
 
       \put(0,0.13){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
-      \put(0.085,0.475){\small(a)}
-      \put(0.555,0.475){\small(b)}
-      \put(0.085,0.225){\small(c)}
-      \put(0.555,0.225){\small(d)}
+
+      \put(0.085,0.709){\small(a)}
+      \put(0.555,0.709){\small(b)}
+      \put(0.085,0.475){\small(c)}
+      \put(0.555,0.475){\small(d)}
+      \put(0.085,0.225){\small(e)}
+      \put(0.555,0.225){\small(f)}
 
@@
 
-  \caption{Velocity amplitude and mean power as functions of the damping factor.
-Data presented in (a) and (c)  were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}).
-Data presented in (b)and (d)  were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+).
+  \caption{Displacement amplitude, velocity amplitude and mean power as functions of the damping factor.
+Data presented in (a),(c) and (e)  were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}).
+Data presented in (b), (d) and (f)  were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+).
 The collapsed data implies that there is no frequency selection and the tuning parameter of the mechanical side of the system is the damping constant to obtain an optimum power output.}

### 2013-09-05 research/paper/results/results-2.3.tex
new files added

@@
 Therefore hysteresis is not expected at \reynoldsnumber=165.
-The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$).
+The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$).
 This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angle because fluid forces are acting in the direction of travel of the oscillating cylinder.
@@
  The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$.
-A shift of the peak power could be observed as $\zeta$ increases.
+The value of \ustar at which the peak power occurs increases with $\zeta$.
 However, the magnitude of the peaks remain constant for all the values of $\zeta$.
-A similar observation could be made from the results of \cite{Barrero-Gil2010a}.
+\cite{Barrero-Gil2010a} also showed a similar trend.
+The higher Reynolds number case clearly showed the hysteresis range starting from marginally before the peak value and extend for about \hilight{the \ustar values}.
 It could be observed that unlike VIV the  system has no preferred frequency.
@@
 
- If the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective (disregarding the shedding term as the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency), it is obvious the forcing term on RHS of the equation is only dependent on transverse velocity($\dot{y}$) which is essentially the input power of the system.
+ Now the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective.
+The shedding forces can be neglected because the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency, for the cases that exhibit galloping.
+It is obvious that the forcing term on LHS of the equation is only dependent on transverse velocity($\dot{y}$) which is essentially the input power of the system.
 On the RHS, the mechanical damping or system damping is the only term that takes out power at any instant.
 This could be expressed as the product of damping force and the velocity ($P_d$).
-The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces i.e there is zero net energy in or out of the system when averaged over a period.
-Therefore that the system is governed by the transverse velocity rather than the natural frequency.
+The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period).
+Therefore the system is governed by the transverse velocity rather than the natural frequency.
 
- Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency.
-The effect of fixing $\zeta$ and increasing $U^*$ actually decreases damping constant for a fixed free-stream velocity.
+ Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because they scale with the natural frequency of the system.
+The effect of fixing $\zeta$ and increasing $U^*$ actually decreases the damping constant for a fixed free-stream velocity.
 ($U^*=\frac{U}{f \times D}$, $\zeta= \frac{c}{2 m \omega_n}$ ).
@@
 
- A single set of results for a given $C_y$ curve could be obtained for the displacement, velocity and power were plotted as a function of damping constant $c$ 
+ The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$
 (Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).

### 2013-09-06 research/paper/results/results-2.3.tex
commit some modifications...

@@
 (Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).
-Fig.\ref{fig:time_hostory_velocity_same_power} clearly shows that a similar velocity amplitude could be obtained for a given damping factor provided that the small fluctuations are disregarded.
+This further emphasizes that the galloping system is not frequency dependent.
+It is possible to obtain a different similar power output at different values of \usta when the damping constant \hilight{...}, is kept fixed.
+An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding.
+As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.
 

### 2013-09-09 research/paper/results/results-2.3.tex
uploaded 4.22 pm

@@
 This further emphasizes that the galloping system is not frequency dependent.
-It is possible to obtain a different similar power output at different values of \usta when the damping constant \hilight{...}, is kept fixed.
+It is possible to obtain a different similar power output at different values of \ustar when the damping constant \hilight{...}, is kept fixed.
 An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding.
@@
 Maximum amount of power could be transferred within the peak region.
-At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.
+At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.
 
@@
 
- At region 1 where $U^*=90$ (region 1) the damping constant is high and therefore a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ Fig.
+ At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.
 \ref{fig:power_time_histories} (a).
 Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.
-Hence both $P_d$ and $P_t$ becomes sinusoidal.
-However, due to the higher damping  $\theta$ does not go to the region which produces the peak power.
+The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic foce increases with the incident angle (i.e.
+$0<\theta \leq < 4^0$ in \ref{fig:lift_curves}) Hence both $P_d$ and $P_t$ becomes sinusoidal.
+In this case, power output is limited by the low fluid forces present at lwo incident angles.
+
+  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output.
+Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle.
+This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive.
+The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e.
+$0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)).
+In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times.
+From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low.
+Therefore this excess energy is trasnferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)
 
@@
 From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)).
-In this case at certain point in time $\theta$ arrives at the region where $F_y$ decreases but does not become negative when the angle is increased.
-Therefore, the force $F_y$ and $P_t$ reduces as the velocity further increased.
-This is because $\theta = tan^{-1}(\frac{\dot{y}}{U})$ and $\theta$ is proportional to  transverse velocity.
-As the velocity $\dot{y}$ is sinusoidal, $\theta$ recovers back and this leads to two `peaks'  in a single half cycle.
-
- At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output.
-Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle.
-This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive.
-As the force opposes the direction of travel, the power becomes negative.
-On the other hand from an energy perspective we could see that the mechanical damping is not sufficient to dissipate out the energy transferred from the fluid to the structure (as `$c$' is substantially low), therefore  part of this energy is transferred back to the fluid which is depicted as a negative power region in Fig.\ref{fig:power_time_histories} (c).
+In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e.
+$\theta=4^0$ in \ref{cy ploynomial} (a)).
+The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity.
 

### 2013-09-09 research/paper/results/results-2.3.tex
uploaded 11.03 pm

@@
 However, at $m^* \leq 30$ an effect of $m^*$ it could be observed.
-The peak value of the mean power curve reduces with $m^*$.
-This may be due to the fact that as the inertia of the system is reduced and galloping becomes weak.
-Therefore shedding become dominant.
+Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
 This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.
+The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in \ref{fig:power_time_histories}.
+While the time avergae of both quantities are the same, instantaneously they are not.
+Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle.
+In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.
 

### 2013-09-11 research/paper/introduction/intro-1.0.tex
uploaded 11 sept 2013

@@
 \cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory.
-In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio the mass-damping ($m^*\zeta$) parameter should be kept low as well as the frequency of oscillations should be carefully matched \hilight{have a good agreement with the size of the cross section}.
+In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio
+ the mass-damping ($m^*\zeta$) parameter should be kept low as well as the frequency of oscillations should be carefully matched with the size of the cross section.
 Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

### 2013-09-12 research/paper/results/results-2.3.tex
uploaded 4.07 12 Sep 2013

@@
 Hysteresis could be observed for the case with a higher Reynolds number.
+This was achieved by manipulating the initial conditions (initial displacement) of the system.
+The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude.
+Although a third state could be achieved theoretically, it was not possible to achieve numerically.
+This was also observed by \cite{Vio2007}.
 
@@
 \cite{Barrero-Gil2010a} also showed a similar trend.
-The higher Reynolds number case clearly showed the hysteresis range starting from marginally before the peak value and extend for about \hilight{the \ustar values}.
+The higher Reynolds number case clearly showed hysteresis in the power data.
+The range of hysteresis tend to increase with increasing $\zeta$.
 It could be observed that unlike VIV the  system has no preferred frequency.
@@
 
- The data presented in \ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c$
+ The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c\rho\mathcal{A}U$
 (Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).
 This further emphasizes that the galloping system is not frequency dependent.
-It is possible to obtain a different similar power output at different values of \ustar when the damping constant \hilight{...}, is kept fixed.
-An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disragard the high frequencies due to shedding.
+It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $c\rho\mathbb{A}U$, is kept fixed.
+An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
 As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.
@@
 Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.
-The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic foce increases with the incident angle (i.e.
+The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e.
 $0<\theta \leq < 4^0$ in \ref{fig:lift_curves}) Hence both $P_d$ and $P_t$ becomes sinusoidal.
-In this case, power output is limited by the low fluid forces present at lwo incident angles.
+In this case, power output is limited by the low fluid forces present at low incident angles.
+In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.
 
@@
 From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low.
-Therefore this excess energy is trasnferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)
+Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)
 
-At region 2 ($U^*=165$) the mean power output is at its maximum.
+At region 2 ($U^*=165$).
 $P_t$ is not a pure sinusoidal signal.
@@
 The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity.
+The mean power output is at its maximum.
+This is due to the fact that this region is a best compromise between region 1 and 3.
+The damping is substantially high to obtain a high power output while not too high to hinder the induced angle of attack entering the region where the forcing is high.
 
@@
 
- Put conclusion here
-
-%\section{Conclusion}
+\section{Conclusion}
 

### 2013-09-13 research/paper/results/results-2.3.tex
uploaded 6.59

@@
 However, at $m^* \leq 30$ an effect of $m^*$ it could be observed.
-Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
+Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.
+c When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
 This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.
 The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in \ref{fig:power_time_histories}.
-While the time avergae of both quantities are the same, instantaneously they are not.
+While the time average of both quantities are the same, instantaneously they are not.
 Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle.

### 2013-09-14 research/paper/introduction/intro-1.0.tex
uploaded 7.45

@@
 The study managed to achieve a good agreement with experimental data.
-The QSS model equation when solved using analytically using sinusoidal solution mehod cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
+The QSS model equation when solved using analytically using sinusoidal solution method cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
 The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
 \cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory.
-In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio
- the mass-damping ($m^*\zeta$) parameter should be kept low as well as the frequency of oscillations should be carefully matched with the size of the cross section.
+In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low.
 Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.

### 2013-09-14 research/paper/results/results-2.3.tex
uploaded 7.45

@@
 
+In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods.
+The system is not frequency dependent but more dependent on the velocity amplitude of they system.
+It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant.
+By anaylizing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($c\rho\mathcal{A}U$) should be high, but not too high enough to hinder the induced angle of attack reaching the region of higher forcing.
+The reduction in power at low mass ratios was due to the fact that the instantaneous $P_t$ and $P_d$ are not the same.
+Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
+
  % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

### 2013-09-15 research/paper/results/results-2.3.tex
Sketch completed..

@@
 
- Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because they scale with the natural frequency of the system.
+ Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because the scale with the natural frequency of the system.
 The effect of fixing $\zeta$ and increasing $U^*$ actually decreases the damping constant for a fixed free-stream velocity.
@@
 This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.
-The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in \ref{fig:power_time_histories}.
+The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in Fig.\ref{fig:power_time_histories}.
 While the time average of both quantities are the same, instantaneously they are not.
@@
 In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods.
-The system is not frequency dependent but more dependent on the velocity amplitude of they system.
+The system is not frequency dependent but more dependent on the velocity amplitude of the system.
 It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant.

### 2013-09-17 research/paper/Theory/mathematical_model.tex
Updated 17 Sep

@@
  One of the widely used mathematical model to predict the system response under galloping is the Quasi-steady state (QSS) model, incorporated by \cite{Parkinson1964} for a square cross section.
-The equation of motion of the body under galloping is given by Eq.
-\eqref{equationofmotion}.
+The equation of motion of the body under galloping is given by Eq.\eqref{equationofmotion}.
 The forcing term $F_y$ is given by Eq.\eqref{lift equation}.
@@
 $\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively.
-Thus, the final equation is given by Eq.
-\eqref{final_equation_motion}.
+Thus, the final equation is given by Eq.\eqref{final_equation_motion}.
 
@@
 
- The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq. \eqref{power}.
+ The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq.\eqref{power}.
 
@@
  \input{../figure/cy_vs_theta}
- \vspace{20mm}
+
  \input{../figure/coefficient-table}
@@
 
-Shedding frequency $\omega_s$, was set to $0.98$ winch was obtained by performing a power spectral analysis of the stationary data at $0^0$.
+Shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^0$.
 Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$.
-The average power was obtained by using Eq.
-\eqref{power}
+The average power was obtained by using Eq.\eqref{power}
 
 and the averaging was done over no less than 20 galloping periods.
-Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (\ref{table:cy-coefficients}) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers.
+Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers.
 $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
@@
 A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet.
-A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and Re $165$.
-A 9th order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.
+A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and \reynoldsnumber=$165$.
+A $9^{th}$ order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

### 2013-09-17 research/paper/introduction/intro-1.0.tex
Updated 17 Sep

@@
 
-The search for alternate energy sources which could be categorised  under the "green" label has become important area of research in the modern word.
+The search for alternate energy sources which could be categorised  under the ``green" label has become important area of research in the modern word.
 Solar, wind power and wave power are some of the examples of these sources.
-Recently,a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}).
+Recently, a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}).
 It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.
@@
 Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV.
-Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties(\cite{Raghavan2010a} ,\cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}).
-However,the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated.
+Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties (\cite{Raghavan2010a} , \cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}).
+However, the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated.
 Some theoretical work was carried out by (\cite{Barrero-Gil2010a}).
-Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow "lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).
+Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow ``lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).
 This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.
@@
 Energy harvesting systems have high damping ratios because the energy generator (e.g electrical generator) puts a significant amount of damping into the system.
-Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.
+Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.
+Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.
 
-According to \cite{Paidoussis2010},\cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.
+According to \cite{Paidoussis2010}, \cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.
 \cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines.
-A non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory.
+A weakly non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory.
 Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model.
@@
 The study managed to achieve a good agreement with experimental data.
-The QSS model equation when solved using analytically using sinusoidal solution method cannot predict cases with low mass ratios  .\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
+The QSS model equation when solved analytically using sinusoidal solution method cannot predict cases with low mass ratios.
+\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
 The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.

### 2013-09-17 research/paper/results/results-2.3.tex
Updated 17 Sep

@@
 
-The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a))have a good agreement with data presented in \cite{Joly2012}.
+The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}.
 In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed.
@@
 
- The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios ,$\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve)  curve could be obtained for the velocity amplitude  and power were plotted as a function of  non dimensionalised  damping constant $c\rho\mathcal{A}U$
+ The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve).
+These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $c\rho\mathcal{A}U$
 (Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).
@@
 The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected .
-Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output powe when the reduced velocity is increased.
-The key regions consists of region 1 where the $P_m$ increases with \ustar, region 2 where $P_m$ becomes maximum and region 3 where $P_m$ decreases with \ustar.
+Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased.
+The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar.
 It has been established earlier that the damping factor is a function of $U^*$.
@@
 Maximum amount of power could be transferred within the peak region.
-At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.
+At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.
+Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.
 
@@
 The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e.
-$0<\theta \leq < 4^0$ in \ref{fig:lift_curves}) Hence both $P_d$ and $P_t$ becomes sinusoidal.
+$0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
 In this case, power output is limited by the low fluid forces present at low incident angles.
@@
 From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low.
-Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in \ref{fig:power_time_histories} (c)
+Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)
 
@@
 Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.
-c When galloping excitation is suppressed al low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
+When the galloping excitation is suppressed at low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
 This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.
-The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_t$ in Fig.\ref{fig:power_time_histories}.
+The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_d$ in Fig.\ref{fig:power_time_histories}.
 While the time average of both quantities are the same, instantaneously they are not.
@@
 Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data.
-Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare}(c)).
+Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)).
 However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased.
-The reasoning behind this fact is that galloping is weak at Re 165  and therefore fluid damping has a significant effect.
+The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect.
 It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$.

### 2013-09-24 research/MCR report/main.tex
uploaded new MCR files

@@
 \usepackage{pdfpages}
+\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
 
@@
 The search for alternative energy sources which could be categorised under the ”green”label has become important area of research in the modern word.
-Solar, wind power andwave power are some of the examples of these sources.
+Solar, wind power and wave power are some of the examples of these sources.
 Recently,a new branch of research has been developing to extract energy from flow induced vibrations.
@@
  This research contributes to the existing knowledge on energy extraction from flow induced vibrations.
-This research focuses investigating methods to optimise the energy transfer from fluid-to-body when galloping by using theoretical methods (i.e Quasi-steady state theory and DNS simulations).
+The main focus is investigating methods to optimise the energy transfer from fluid-to-body when galloping by using theoretical methods (i.e Quasi-steady state theory and DNS simulations).
 Therefore the project was separated into two main phases.
@@
 \section{Research objectives}
+\
 
@@
 
-From the literature survey, we identified both optical-circuit switching (OCS) and optical-burst switching (OBS) to be more energy efficient in comparison to point-to-point (pt-pt) and optical-packet switching (OPS) technologies.
-However, both OCS and OBS face a number of challenges.
-Therefore, in stage two of this study, we attempted to generate novel mechanisms to increase energy efficiency in OCS and OBS based optical fiber backbone networks.
+\subsection{Phase-1}
+
+At this point in time  Phase 1 has been completed which is investigating the behaviour of the mechanical portion of the system.
+The following conclusions were made.
+Further information could be found in \hilight{Appendix}
 \begin{itemize}
-\item 
+\item   the system is not frequency dependent, but more dependent on the velocity amplitude.
 \end{itemize}
@@
 \begin{itemize}
-\item
+\item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
+\end{itemize}
 
+\begin{itemize}
+\item It was observed that a reduction in power at low mass ratios ($m^*\leq30$).The reduction in power at low mass ratios was due to the fact that the instantaneous power transferred from fluid-to-body and power dissipated out from mechanical damping are not the same.
+Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
 \end{itemize}
-Finally, in stage four of this study, we intend to explore and develop novel frameworks to increase energy efficiency in an optical fiber backbone network, by utilizing either sleep mode of operation, ALR or MLR techniques.
-As the reader might have noticed, both sleep mode of operation and MLR were used in the two previous two stages in conjunction with OBS and WBS technologies.
-We are currently analysing the existing literature, and are in the process of developing an energy-aware network configuration where line cards and links in the network could move back and forth between sleep and active states depending on the network load.
 
-With respect to the PhD thesis, each of the above stages (literature survey and the three approaches) are intended to be converted into a chapter.
-This is to be followed by a chapter covering the discussion and the conclusion (Appendix).
-During my PhD, the three main approaches are being studied concurrently.
-Therefore, as of today, certain tasks from each different stage have been completed.
-The remaining tasks are to be completed before the end of the allocated time period as explained in the Gantt chart shown in Figure 1.
-In conclusion, 60\% of the research work has been completed to date with 70\% of the objectives being successfully accomplished.
+\subsection{Phase-2}
+
+As previously mentioned the fluid dynamics portion of the system is studied in phase-2.
+
+\subsection{Creation of the negative lift}
+
+In order to carry out an optimisation study on the fluid dynamics portion of the system, it is essential to study underlying fluid mechanics for galloping.
+It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system.
+Therefore it is essential to know how exactly this lift occur.
+According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is crated by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody.
+If a square cross section is taken as an example as the cross section have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other.
+Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body.
+The lift force become its maximum when the shear layer closer to the boy re attaches at the trailing edge.
+As the angle of attack is increased beyond that point, The separated shear layer in the opposite side of the body (which was initially not close to the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force.
+This explanation was validated by \cite{Luo1994} by experimental flow visualisation.
+
+Therefore two parameters could be identified which governs the lift
+
+\begin{itemize}
+\item{ The characteristics of the afterbody}
+\item{Shear layer separation}
+\end{itemize}
+
+\cite{Luo1994} have done some interesting studies on the lift characteristics on trapezoidal bodies.
+Which essentially the top and bottom sides of a square were tapered away systematically until it becomes triangle which is depicted in \hilight{Figure}.
+
+\input{./figures/luo_sketch}
 
@@
 \vspace*{2.5in}
-\section*{\LARGE Appendix 2}
-\addcontentsline{toc}{section}{Appendix 2} 
-\includepdf[page={-}]{ICTpaper.pdf}
+
 \end{document}

### 2013-10-12 research/MCR report/main.tex
uploaded 12-10-2013

@@
 \section{Introduction}
-The search for alternative energy sources which could be categorised under the ”green”label has become important area of research in the modern word.
+The search for alternative energy sources which could be categorised under the ”green” label has become important area of research in the modern word.
 Solar, wind power and wave power are some of the examples of these sources.
@@
 Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body.
-The lift force become its maximum when the shear layer closer to the boy re attaches at the trailing edge.
+The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge.
 As the angle of attack is increased beyond that point, The separated shear layer in the opposite side of the body (which was initially not close to the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force.

### 2013-10-12 research/paper/figure/m_star_collapsed.tex
uploaded 12-10-2013

@@
 \begin{figure}
+
 \setlength{\unitlength}{\textwidth}
+\fbox{
+  \begin{picture}(1,0.32)
 
-  \begin{picture}(1,0.35)(0,0.75)
+       \put(0.07,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
+       \put(0.36,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/mean_power_collapsed_noshed_mstar.eps}}
+       \put(0.65,0.03){\includegraphics[width=0.3\unitlength]{../FnP/gnuplot/fsi_power.eps}}
 
-  \put(0.15,0.76){\includegraphics[width=0.7\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
+        \put(0.03,0.17){\large $\frac{P_{m}}{\rho \mathcal{A}U^3}$}
 
- 	\put(0.11,0.95){\large $\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
+        \put(0.2,0.0){$\frac{c}{\rho\mathcal{A}U}$} 	
+        \put(0.49,0.0){$\frac{c}{\rho\mathcal{A}U}$}
+        \put(0.78,0.0){$\frac{c}{\rho\mathcal{A}U}$}
 
- 	 	\put(0.45,0.75){ $c\rho\mathcal{A}U$}
+        \put(0.133,0.21){\small(a)}
+        \put(0.42,0.21){\small(b)}
+        \put(0.715,0.21){\small(c)}
 
   \end{picture}
+  }
 
@@
 \end{figure}
+
+Mean power as a function of damping factor at Re

### 2013-10-12 research/paper/results/results-2.3.tex
uploaded 12-10-2013

@@
  The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve).
-These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $c\rho\mathcal{A}U$
+These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $\frac{c}{\rho\mathcal{A}U}$
 (Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).
@@
 In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times.
-From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $c\rho\mathcal{A}U$ is substantially low.
+From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low.
 Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)
@@
 
-In this paper, the power transfer of a square body under aero elastic galloping is analysed by using quasi-steady state model and numerical methods.
-The system is not frequency dependent but more dependent on the velocity amplitude of the system.
-It could be proven from the collapsed plots in terms of non-dimensionalised (using flow parameters) damping constant.
-By anaylizing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($c\rho\mathcal{A}U$) should be high, but not too high enough to hinder the induced angle of attack reaching the region of higher forcing.
-The reduction in power at low mass ratios was due to the fact that the instantaneous $P_t$ and $P_d$ are not the same.
-Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
+In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration.
+The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system.
+This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters).
+By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.
 

### 2013-10-15 research/MCR report/main.tex
15-oct

@@
 \begin{enumerate}[]
-\item Phase 1: To optimise the mechanical portion of the system 
-\item Phase 2: To optimise the fluid dynamics portion of the system 
+\item Phase 1: Optimise the mechanical characteristics of the system.
+\item Phase 2: Optimise the fluid dynamics portion of the system 
 \end{enumerate}
@@
 \section{Research objectives}
-\
 
@@
 
-At this point in time  Phase 1 has been completed which is investigating the behaviour of the mechanical portion of the system.
+Phase 1 has been completed which is investigating the behaviour of the mechanical characteristics of the system.
 The following conclusions were made.
 Further information could be found in \hilight{Appendix}
+
 \begin{itemize}
 \item   the system is not frequency dependent, but more dependent on the velocity amplitude.
-\end{itemize}
-
-\begin{itemize}
 \item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
-\end{itemize}
-
-\begin{itemize}
-\item It was observed that a reduction in power at low mass ratios ($m^*\leq30$).The reduction in power at low mass ratios was due to the fact that the instantaneous power transferred from fluid-to-body and power dissipated out from mechanical damping are not the same.
-Therefore the mechanical system requires adequate inertia to store a portion of power transferred from the fluid to the body to sustain galloping.
 \end{itemize}
@@
 
-\subsection{Creation of the negative lift}
+\subsubsection{Creation of the negative lift}
 
@@
 It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system.
-Therefore it is essential to know how exactly this lift occur.
+Therefore it is essential to have an understanding on how exactly this lift occur.
 According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is crated by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody.
-If a square cross section is taken as an example as the cross section have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other.
+If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other.
 Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body.
 The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge.
-As the angle of attack is increased beyond that point, The separated shear layer in the opposite side of the body (which was initially not close to the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force.
-This explanation was validated by \cite{Luo1994} by experimental flow visualisation.
+As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force.
+This explanation was validated by \cite{Luo1994} by conducting flow visualisation experimentally.
 
@@
 Which essentially the top and bottom sides of a square were tapered away systematically until it becomes triangle which is depicted in \hilight{Figure}.
+\input{./figures/luo_sketch}.
+According to the data presented \cite{Luo1994} the highest lift is produced by the triangle.
+However, the maximum lift occur at a very large angle of attack ($\theta\approx 34^0 $) compared to a square cross section ($\theta\approx 12^0 $).
 
-\input{./figures/luo_sketch}
+According to the literature survey carried out so far, investigations have been carried out only for
 
@@
 
-\section{Difficulties and challenges} 
-%
+%\section{Difficulties and challenges} 
+%%
+%%\begin{enumerate}
+%%      
+%%\end{enumerate}
+%\bibliographystyle{elsarticle-harv}
+%\bibliography{../bibtex/MCR}
+%\appendix
+%%\begin{center}
+%%\section*{\LARGE Appendix 1}
+%%\addcontentsline{toc}{section}{Appendix 1} 
+%%\end{center}
+%Proposed table of contents of the final PhD thesis:
 %\begin{enumerate}
-%      
+%\item Introduction
+%\begin{enumerate}[i]
+%\item Looking forward
+%\item Scope of the thesis
+%\item Organization of the thesis
+%\item Objectives
+%\item Contributions
+%\item Publications 
 %\end{enumerate}
-\bibliographystyle{elsarticle-harv}
-\bibliography{../bibtex/MCR}
-\appendix
-%\begin{center}
-%\section*{\LARGE Appendix 1}
-%\addcontentsline{toc}{section}{Appendix 1} 
-%\end{center}
-Proposed table of contents of the final PhD thesis:
-\begin{enumerate}
-\item Introduction
-\begin{enumerate}[i]
-\item Looking forward
-\item Scope of the thesis
-\item Organization of the thesis
-\item Objectives
-\item Contributions
-\item Publications 
-\end{enumerate}
-\item Power consumption in optical core network
-\begin{enumerate}[i]
-\item Introduction
-\item Core network architecture
-\item Core node architecture 
-\item Power consumption values
-\item Node-based approaches
-\item Traffic engineering-based approaches
-\item Network engineering-based approaches
-\end{enumerate}
-\item Node-based energy efficiency
-\begin{enumerate}[i]
-\item Introduction
-\item General network model
-\item Problem definition
-\item Cost model
-\item Energy and cost efficient algorithm
-\item Framework for energy efficient OBS network
-\item Summary
-\end{enumerate}
-\item Traffic engineering-based energy efficiency
-\begin{enumerate}[i]
-\item Introduction
-\item Grooming based network model
-\item Problem definition
-\item Sparse grooming 
-\item Waveband grooming 
-\item Summary
-\end{enumerate}
-\item Network engineering-based energy efficiency \begin{enumerate}[i]
-\item Introduction
-\item MLR based network model
-\item Problem definition
-\item MLR based WBS network
-\item Sleep mode enabled core network
-\item Summary
-\end{enumerate}
-\item Conclusion
-\begin{enumerate}[i]
-\item Introduction
-\item Summary of the work
-\item Future directions
-\end{enumerate}
-\end{enumerate}
-Each sub-section mentioned above could be further divided into sections, if necessary.
+%\item Power consumption in optical core network
+%\begin{enumerate}[i]
+%\item Introduction
+%\item Core network architecture
+%\item Core node architecture 
+%\item Power consumption values
+%\item Node-based approaches
+%\item Traffic engineering-based approaches
+%\item Network engineering-based approaches
+%\end{enumerate}
+%\item Node-based energy efficiency
+%\begin{enumerate}[i]
+%\item Introduction
+%\item General network model
+%\item Problem definition
+%\item Cost model
+%\item Energy and cost efficient algorithm
+%\item Framework for energy efficient OBS network
+%\item Summary
+%\end{enumerate}
+%\item Traffic engineering-based energy efficiency
+%\begin{enumerate}[i]
+%\item Introduction
+%\item Grooming based network model
+%\item Problem definition
+%\item Sparse grooming 
+%\item Waveband grooming 
+%\item Summary
+%\end{enumerate}
+%\item Network engineering-based energy efficiency \begin{enumerate}[i]
+%\item Introduction
+%\item MLR based network model
+%\item Problem definition
+%\item MLR based WBS network
+%\item Sleep mode enabled core network
+%\item Summary
+%\end{enumerate}
+%\item Conclusion
+%\begin{enumerate}[i]
+%\item Introduction
+%\item Summary of the work
+%\item Future directions
+%\end{enumerate}
+%\end{enumerate}
+%Each sub-section mentioned above could be further divided into sections, if necessary.
 For example, 3(v) could be divided as 3(v)(a) "ILP formulation", 3(v)(b) "Heuristic algorithm" and 3(v)(c) "Evaluation"
-\newpage
-\centering
-\vspace*{2.5in}
+%\newpage
+%\centering
+%\vspace*{2.5in}
 

### 2013-10-17 research/MCR report/main.tex
6.25 17 OCT

@@
 \end{itemize}
-
+ %\input{./figures/luo_sketch}.
 \cite{Luo1994} have done some interesting studies on the lift characteristics on trapezoidal bodies.
 Which essentially the top and bottom sides of a square were tapered away systematically until it becomes triangle which is depicted in \hilight{Figure}.
-\input{./figures/luo_sketch}.
 According to the data presented \cite{Luo1994} the highest lift is produced by the triangle.
@@
 
-According to the literature survey carried out so far, investigations have been carried out only for
+\subsubsection{Optimising the cross sectional shape}
+According to the literature survey done so far, investigations have been carried out only on cross sections with basic shapes.
+
+\begin{itemize}
+\item{Square}
+\item{Triangle}
+\item{Trapezium}
+\end{itemize}
+
+Our hypothesis is that the cross section could be further optimised to get a higher power output by incorporating a complex shape which is a combination of the basic shapes.
+The current suggestion is that to analyse the characteristics of a hybrid shape of square and triangle.
+The idea is to delay the shear layer reattachment.
+which may result in having a larger band of induced angles where the forcing is substantially high.
+This will eventually then lead to a higher mean power output.
+
+\begin{itemize}
+\item{The stationary $c_y$ data of basic cross sections (i.e square, triangle and trapezium) will be obtained using DNS simulations at laminar flow.
+The data will be compared with existing literature.
+The time averaged pressure fields will be obtained in order to analyse the behaviour of the shear layers.}
+\item{The stationary data of the complex shape shown in \hilight{Figure} will be obtained together with the time average pressure fields where the behaviour of the shear layers could be analysed.}
+\item{Based on the initial results an optimisation study will be carried out by changing $l$ and $h$. The quasi-steady model will be used to obtain the power output.}
+\item{FSI simulations will be carried out and the power output will be compared with the data obtained using quasi-steady model.}
+\end{itemize}
 
@@
 %%\end{center}
-%Proposed table of contents of the final PhD thesis:
-%\begin{enumerate}
-%\item Introduction
-%\begin{enumerate}[i]
-%\item Looking forward
-%\item Scope of the thesis
-%\item Organization of the thesis
-%\item Objectives
-%\item Contributions
-%\item Publications 
-%\end{enumerate}
-%\item Power consumption in optical core network
-%\begin{enumerate}[i]
-%\item Introduction
-%\item Core network architecture
-%\item Core node architecture 
-%\item Power consumption values
-%\item Node-based approaches
-%\item Traffic engineering-based approaches
-%\item Network engineering-based approaches
-%\end{enumerate}
-%\item Node-based energy efficiency
-%\begin{enumerate}[i]
-%\item Introduction
-%\item General network model
-%\item Problem definition
-%\item Cost model
-%\item Energy and cost efficient algorithm
-%\item Framework for energy efficient OBS network
-%\item Summary
-%\end{enumerate}
-%\item Traffic engineering-based energy efficiency
-%\begin{enumerate}[i]
-%\item Introduction
-%\item Grooming based network model
-%\item Problem definition
-%\item Sparse grooming 
-%\item Waveband grooming 
-%\item Summary
-%\end{enumerate}
-%\item Network engineering-based energy efficiency \begin{enumerate}[i]
-%\item Introduction
-%\item MLR based network model
-%\item Problem definition
-%\item MLR based WBS network
+Proposed table of contents of the final PhD thesis:
+\begin{enumerate}
+\item Preliminary remarks 
+\item A review of literature
+\begin{enumerate}[i]
+\item Introduction
+\item Flow induced vibrations 
+\item Flow induced vibrations as a mechanism of energy harvesting
+\item Aeroelastic galloping
+\item Behaviour of shear layer 
+\end{enumerate}
+\item Methodology and validation
+\begin{enumerate}[i]
+\item Introduction
+\item Governing equations and quasi-steady state model 
+\item Numerical methods and boundary conditions 
+\item The governing equations for the DNS method: Naiver-Stokes and continuity  
+\item Discretisation  
+\item Integration of substep equation 
+\item Boundary conditions 
+\item Spectral element method
+\item Convergence and validation studies 
+\item Summary
+\end{enumerate}
+\item Galloping response and natural frequency
+\begin{enumerate}[i]
+\item Introduction
+\item
+
+\end{enumerate}
+\item Effect of mechanical parameters on power output
+\begin{enumerate}[i]
+\item Introduction
+\item Natural frequency 
+\item Damping constant 
+\item Mass ratio
 %\item Sleep mode enabled core network
-%\item Summary
-%\end{enumerate}
-%\item Conclusion
+\item Summary
+\end{enumerate}
+\item{Optimisation of the cross sectional shape for a better power output}
+\item{FSI validation}
+\item Conclusion
 %\begin{enumerate}[i]
@@
 %\end{enumerate}
-%\end{enumerate}
+\end{enumerate}
 %Each sub-section mentioned above could be further divided into sections, if necessary.

### 2013-10-22 research/paper/figure/m_star_collapsed.tex
uploaded 22-oct 2013 6.36

--- 2013-09-02 research/paper/figure/m_star_collapsed.tex
@@
 \begin{figure}
+
 \setlength{\unitlength}{\textwidth}
+\fbox{
+  \begin{picture}(1,0.3)(0.0,0.45)
 
-  \begin{picture}(1,0.35)(0,0.75)
+       \put(0.025,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
+       \put(0.495,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_noshed_mstar.eps}}
 
-  \put(0.15,0.76){\includegraphics[width=0.7\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
+        \put(-0.01,0.637){\large $\frac{P_{m}}{\rho \mathcal{A}U^3}$}
 
- 	\put(0.11,0.95){\large $\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
+        \put(0.23,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$} 	
+        \put(0.73,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$}
 
- 	 	\put(0.45,0.75){ $c\rho\mathcal{A}U$}
+     \put(0.085,0.709){\small(a)}
+     \put(0.555,0.709){\small(b)}
 
   \end{picture}
+  }
 

### 2013-10-22 research/paper/figure/mstar_parkinson.tex
uploaded 22-oct 2013 6.36

\begin{figure}
  \setlength{\unitlength}{\textwidth}
\fbox{
        \begin{picture}(1,0.3)(0.0,0.45)

      % % % Parkinson Data 
      \put(0.025,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar_175.eps}}      \put(0.495,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_parkinson_10.eps}}

      \put(0.23,0.48){ $\displaystyle\frac{c}{\rho\mathcal{A}U}$}
      \put(0.73,0.48){ $\displaystyle\frac{c}{\rho\mathcal{A}U}$}

      \put(0.0,0.63){\large$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}

      \put(0.085,0.709){\small(a)}
      \put(0.555,0.709){\small(b)}

    \end{picture}
}
  \caption{}
    \label{fig:collpased_data}
\end{figure}

\ %vspace{10cm}

### 2013-10-31 research/paper/figure/m_star_collapsed.tex
uploaded 31 OCt 2013

@@
 \setlength{\unitlength}{\textwidth}
-\fbox{
+
   \begin{picture}(1,0.3)(0.0,0.45)
@@
   \end{picture}
-  }
 
   \caption{Mean power as a function of damping factor.
-Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 and $\zeta=0.1$.
-A reduction of maximum mean power can be observed when $m^*<40$.
-For $m^*>40$, the maximum power is essentially independent of $m^*$.}
+Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 (a) with and (b) without the shedding term in Eq.\ref{final_equation_motion}.
+A reduction of maximum mean power can be observed when $m^*<40$ with shedding while the maximum power is essentially independent of $m^*$ when shedding is disregarded.}
     \label{fig:m_star_collapsed}
 \end{figure}
-
-Mean power as a function of damping factor at Re

### 2013-10-31 research/paper/figure/mstar_parkinson.tex
uploaded 31 OCt 2013

@@
   \setlength{\unitlength}{\textwidth}
-\fbox{
+
         \begin{picture}(1,0.3)(0.0,0.45)
@@
     \end{picture}
-}
-  \caption{}
-    \label{fig:collpased_data}
+  \caption{Mean power as a function of damping factor.
+Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios: $m^*=1164$ (\ding{83}), $m^*=100$ (\ding{116}), $m^*=50$ (\ding{108}), $m^*=10$ (+), $m^*=5$ (\ding{110}) and $m^*=1$ ($\times)$ at \ustar=175.
+Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{83}) and \ustar=375 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$.
+The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.}
+
+    \label{fig:mstarcollapsed_parkinson}
 \end{figure}

### 2013-10-31 research/paper/figure/time_history_msar_mass.tex
uploaded 31 OCt 2013

\begin{figure}

   \setlength{\unitlength}{\textwidth}

   \begin{picture}(1,0.399)(0.01,0.77)
     % % % 90
     \put(0.03,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_75.eps}}   
     \put(0.36,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_175.eps}}
     \put(0.68,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_375.eps}}

     \put(0.03,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_75.eps}}   
     \put(0.36,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_175.eps}}
     \put(0.68,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_375.eps}}

     \put(0.55,0.79){$\displaystyle{\frac{tU}{D}}$}
     \put(0.2,0.79){$\displaystyle{\frac{tU}{D}}$}
     \put(0.85,0.79){$\displaystyle{\frac{tU}{D}}$}

      \put(0.02,1.07){$\displaystyle\frac{V}{D}$}
     \put(0.02,0.9){$\displaystyle\frac{A}{D}$}

     \put(0.08,0.9997){(a)}    
     \put(0.4,0.9997){(b)}    
     \put(0.72,0.9997){(c)}
     \put(0.08,0.8){(d)}    
     \put(0.4,0.8){(e)}    
     \put(0.72,0.8){(f)}

   \end{picture}

  \caption{ Time histories of velocity. Data presented at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different mass ratios: (a) $m^*=1164$, (b) $m^*=10$ and (a) $m^*=5$. As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal as a result of reduction of frequency.}

  \label{time_hostory_mstar_mass}
\end{figure}

### 2013-10-31 research/paper/figure/time_history_msar_ustar.tex
uploaded 31 OCt 2013

\begin{figure}

  \setlength{\unitlength}{\textwidth}

 \begin{picture}(1,0.399)(0.01,0.77)
     % % % 90
     \put(0.03,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_1164.eps}}   
     \put(0.36,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_10.eps}}
     \put(0.68,1){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/vel_time_history_5.eps}}

     \put(0.03,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_1164.eps}}   
     \put(0.36,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_10.eps}}
     \put(0.68,0.82){\includegraphics[width=0.35\unitlength]{../FnP/gnuplot/dis_time_history_5.eps}}

     \put(0.55,0.79){$\displaystyle{\frac{tU}{D}}$}
     \put(0.2,0.79){$\displaystyle{\frac{tU}{D}}$}
     \put(0.85,0.79){$\displaystyle{\frac{tU}{D}}$}

      \put(0.02,1.07){$\displaystyle\frac{V}{D}$}
     \put(0.02,0.9){$\displaystyle\frac{A}{D}$}

     \put(0.08,0.9997){(a)}    
     \put(0.4,0.9997){(b)}    
     \put(0.72,0.9997){(c)}
     \put(0.08,0.8){(d)}    
     \put(0.4,0.8){(e)}    
     \put(0.72,0.8){(f)}

   \end{picture}

  \caption{Time histories of velocity. Data presented at \reynoldsnumber=22300, $m^*=10$ and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different reduced velocities: (a) $\ustar=75$, (b) $\ustar=175$ and (a) $\ustar=375$. As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal due to the reduction in inertia.}

  \label{time_history_mstar}
\end{figure}

### 2013-10-31 research/paper/results/results-2.3.tex
uploaded 22-oct 2013 6.36
uploaded 31 OCt 2013

@@
 
- At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.
-\ref{fig:power_time_histories} (a).
+ At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a).
 Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.
@@
  \input{../figure/m_star_collapsed}
+ \input{../figure/mstar_parkinson}
 
-The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}) was constant beyond $m^*=30$.
+The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant beyond $m^*=30$.
 However, at $m^* \leq 30$ an effect of $m^*$ it could be observed.
 Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.
-When the galloping excitation is suppressed at low $m^*$, the system will exhibit a weak response as a result of forcing from vortex shedding.
-This was also reported by \cite{Joly2012} where galloping amplitude was reduced at low $m^*$.
-The suppression of galloping as $m^*$ is reduced can be explained by looking at the difference between the instantaneous power transfer between fluid to the structure $P_t$ and the power taken out by the mechanical damping $P_d$ in Fig.\ref{fig:power_time_histories}.
-While the time average of both quantities are the same, instantaneously they are not.
-Therefore the mechanical system is required to store power in certain points of the cycle and release it at another portion of the cycle.
-In cases where $m^*$ is very low, the system lack adequate inertia to store this power which leads to suppression of galloping.
+However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b).
+An influence of vortex shedding on power is present.
+This maybe dude to the reduction in inertia as the mass ratio is decreased.
+
+At \reynoldsnumber=22300 two major phenomena was present.
+The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson}(a)).
+The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson}(b)).
+It should be noted that the influence of $U^*$ was observed only for low mass ratios.
+The velocity time traces of example cases of both scenarios Fig.\ref{time_history_mstar} and \ref{time_history_mstar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.
+
+\input{../figure/time_history_msar_mass}
+
+\input{../figure/time_history_msar_ustar}
 

### 2013-11-08 research/paper/results/results-2.3.tex
uploaded 10.23 November 8th

@@
 
-At \reynoldsnumber=22300 two major phenomena was present.
-The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson}(a)).
-The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson}(b)).
+At \reynoldsnumber=22300 two major phenomena could be observed.
+The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)).
+The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)).
 It should be noted that the influence of $U^*$ was observed only for low mass ratios.
-The velocity time traces of example cases of both scenarios Fig.\ref{time_history_mstar} and \ref{time_history_mstar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.
+The velocity time traces of example cases of both scenarios Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.
+The displacement signal tend to become more triangular.
+the reason behind the increase in power while reducing mass ratio is due to the fact that the inertia of the system becomes low.
+Therefore the body accelerate faster and attains higher velocity quickly.
+Therefore the time period where the body sustains high velocity increases which will lead to an increase in time period where the body in influenced by the higher forcing, which leads to a higher power output.
+As for the case to where the mean power increases with increasing $U^*$ for a given low mass ratio, the exploration tend to be similar where the only difference being that the at high $U^*$ the period of oscillation tend to increase therefore the body sustains higher velocities for a longer time leading to a higher power output.
 
@@
 By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.
+The effect of mass ratio was could also be observed where at \reynoldsnumber=165 the mean power tend to decrease at $m^*<40$ which was found out to be an influence of vortex shedding.
+At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios.
+The cause for this was found out to be the fact that as the mass ratios decreases the due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
 

### 2013-11-10 research/MCR report/main.tex
uploaded 22-oct 2013 6.36
uploaded 10-11-2013 2.03 pm

@@
 \usepackage{tabulary}
-\usepackage[sort]{cite}
+%\usepackage[sort]{cite}
 %\usepackage[sort,nocompress]{cite}
@@
 
+\begin{itemize}
+\item To understand the underpinning mechanical parameters of the system and find methods to optimize it to obtain a higher power output 
+\item To understand the governing fluid mechanics of a system under aeroelastic galloping 
+\item To identify methods to manipulate and control the fluid mechanics to obtain a better power output.  
+\end{itemize}
+
 \section{Research progress}
@@
 \begin{itemize}
-\item   the system is not frequency dependent, but more dependent on the velocity amplitude.
+\item   The system is not frequency dependent, but more dependent on the velocity amplitude.
 \item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
+\item An effect of the mass ratio could be observed as the mass ratio reduces for both higher and lower Reynolds numbers. 
 \end{itemize}
@@
 Therefore it is essential to have an understanding on how exactly this lift occur.
-According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is crated by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody.
+According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is created by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody.
 If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other.
@@
 \end{enumerate}
-\item Galloping response and natural frequency
+\item Power analysis for high and low Reynolds numbers
 \begin{enumerate}[i]
 \item Introduction 
-\item
-
-\end{enumerate}
-\item Effect of mechanical parameters on power output
-\begin{enumerate}[i]
-\item Introduction
+\item Stationary data 
 \item Natural frequency 
@@
 \item Mass ratio
-%\item Sleep mode enabled core network
 \item Summary 
 \end{enumerate}
-\item{Optimisation of the cross sectional shape for a better power output}
-\item{FSI validation}
+
+\item Optimisation of the cross sectional shape 
+\item FSI validation
 \item Conclusion
@@
 \end{enumerate}
-%Each sub-section mentioned above could be further divided into sections, if necessary.
-For example, 3(v) could be divided as 3(v)(a) "ILP formulation", 3(v)(b) "Heuristic algorithm" and 3(v)(c) "Evaluation"
-%\newpage
-%\centering
-%\vspace*{2.5in}
 

### 2013-11-10 research/paper/figure/time_history_msar_mass.tex
uploaded 10-11-2013 2.03 pm

@@
 
-  \caption{ Time histories of velocity.
-Data presented at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different mass ratios: (a) $m^*=1164$, (b) $m^*=10$ and (a) $m^*=5$.
-As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal as a result of reduction of frequency.}
+  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$.
+The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$.
+The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
 

### 2013-11-11 research/paper/figure/mstar_parkinson.tex
uploaded 2.54 11-11-2013

@@
 Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios: $m^*=1164$ (\ding{83}), $m^*=100$ (\ding{116}), $m^*=50$ (\ding{108}), $m^*=10$ (+), $m^*=5$ (\ding{110}) and $m^*=1$ ($\times)$ at \ustar=175.
-Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{83}) and \ustar=375 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$.
+Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$.
 The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.}

### 2013-11-11 research/paper/figure/time_history_msar_mass.tex
uploaded 2.54 11-11-2013

@@
 The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$.
-The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
+The time histories of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
 

### 2013-11-11 research/paper/figure/time_history_msar_ustar.tex
uploaded 10.23 November 8th
uploaded 2.54 11-11-2013

@@
 
-  \caption{Time histories of velocity.
-Data presented at \reynoldsnumber=22300, $m^*=10$ and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different reduced velocities: (a) $\ustar=75$, (b) $\ustar=175$ and (a) $\ustar=375$.
-As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal due to the reduction in inertia.}
+  \caption{  Time histories of displacement and velocity at \reynoldsnumber=22300, $m^*=10$ and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$.
+The velocity time histories are presented for: (a) \ustar=75; (b) \ustar=175 (c) \ustar=375.
+The time histories of displacement are presented for: (a) \ustar=75; (b) \ustar=175; (c) \ustar=375.
+As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal.}
 
-  \label{time_history_mstar}
+  \label{time_history_mstar_ustar}
 \end{figure}

### 2013-11-11 research/paper/figure/time_history_msar_mass.tex
uploaded 12.01 11/11 2013

--- 2013-11-10 research/paper/figure/time_history_msar_mass.tex
@@
 The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$.
-The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
+The time histories of displacement are presented for: (d) $m^*=1164$; (e) $m^*=10$; (f) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
 

### 2013-11-12 research/paper/Theory/mathematical_model.tex
uploaded 10.23 12-11-2013

@@
 The order of the interpolation polynomial has varied from study to study.
-For  example a $7^{th}$ polynomial order was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}.
+For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}.
 \cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order polynomial neither provides a significantly better result nor does it exhibit an additional amplitudes of oscillation.
@@
 
-This equation could be solved by time integration methods. In  this study  `Ode 45' routine in MATLAB was used to obtain the solutions.
+This equation could be solved by time integration methods.
+In  this study  `Ode 45' routine in MATLAB was used to obtain the solutions.
+However in certain cases (low mass ratios) `Ode 15s' routine was used when Ode 45 tend to diverge.
 

### 2013-11-12 research/paper/figure/time_history_msar_mass.tex
uploaded 10.23 12-11-2013

--- 2013-11-10 research/paper/figure/time_history_msar_mass.tex
@@
 The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$.
-The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
+The time histories of displacement are presented for: (d) $m^*=1164$; (e) $m^*=10$; (f) $m^*=5$   As the mass ratio decreases the velocity signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
 

### 2013-11-12 research/paper/figure/time_history_msar_ustar.tex
uploaded 12.01 11/11 2013
uploaded 10.23 12-11-2013

@@
 The velocity time histories are presented for: (a) \ustar=75; (b) \ustar=175 (c) \ustar=375.
-The time histories of displacement are presented for: (a) \ustar=75; (b) \ustar=175; (c) \ustar=375.
-As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal.}
+The time histories of displacement are presented for: (d) \ustar=75; (e) \ustar=175; (f) \ustar=375.
+As the mass ratio decreases the velocity signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal.}
 

### 2013-11-12 research/paper/results/results-2.3.tex
uploaded 10.23 12-11-2013

@@
 The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}.
-In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b))  several differences could be observed.
+In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b)),  several differences could be observed.
 The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) .
@@
 The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$).
-This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angle because fluid forces are acting in the direction of travel of the oscillating cylinder.
+This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder.
 Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction.
@@
 
- The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ Fig.\ref{fig:uncollapsed_data} (a) and (b).
+ The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ (Fig.\ref{fig:uncollapsed_data} (a) and (b)).
 The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers.
@@
  The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$.
-The value of  \ustar at which the peak power occurs increases with $\zeta$.
+The value of  \ustar at which the peak power occur increases with $\zeta$.
 However, the magnitude of the peaks remain constant for all the values of $\zeta$.
@@
 On the RHS, the mechanical damping or system damping is the only term that takes out power at any instant.
-This could be expressed as the product of damping force and the velocity ($P_d$).
+This could be expressed as the product of the damping force and the velocity ($P_d$).
 The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period).
@@
 This further emphasizes that the galloping system is not frequency dependent.
-It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $c\rho\mathbb{A}U$, is kept fixed.
+It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed.
 An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
@@
 Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient.
-Hence the damping coefficient reduces when you move from region 1 to 3.Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative.
+Hence the damping coefficient reduces when you move from region 1 to 3.
+Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative.
 Maximum amount of power could be transferred within the peak region.
@@
 An influence of vortex shedding on power is present.
-This maybe dude to the reduction in inertia as the mass ratio is decreased.
+This maybe due to the reduction in inertia as the mass ratio is decreased.
 
@@
 At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios.
-The cause for this was found out to be the fact that as the mass ratios decreases the due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
+The cause for this was found out to be the fact that as the mass ratio decreases, due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
 

### 2013-11-12 research/MCR report/main.tex
uploaded 8.06 12/11/2013

@@
 Solar, wind power and wave power are some of the examples of these sources.
-Recently,a new branch of research has been developing to extract energy from flow induced vibrations.
+Recently, a new branch of research has been developing to extract energy from flow induced vibrations.
 It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.
@@
 \item Phase 1: Optimise the mechanical characteristics of the system.
-\item Phase 2: Optimise the fluid dynamics portion of the system 
+\item Phase 2: Optimise the fluid dynamics of the galloping excitation.
 \end{enumerate}
@@
 \item To understand the underpinning mechanical parameters of the system and find methods to optimize it to obtain a higher power output 
-\item To understand the governing fluid mechanics of a system under aeroelastic galloping 
-\item To identify methods to manipulate and control the fluid mechanics to obtain a better power output.  
+\item To understand the governing fluid mechanics of a system under aeroelastic galloping and identify methods to manipulate and control the fluid mechanics to obtain a better power output.  
 \end{itemize}
@@
 \item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
-\item An effect of the mass ratio could be observed as the mass ratio reduces for both higher and lower Reynolds numbers. 
+%\item An effect of the mass ratio could be observed as the mass ratio reduces for both higher and lower Reynolds numbers. 
 \end{itemize}
@@
 \begin{itemize}
-\item{ The characteristics of the afterbody}
-\item{Shear layer separation}
+\item The characteristics of the afterbody
+\item Shear layer separation
+\item Shear layer reattachment
+
 \end{itemize}
@@
 The current suggestion is that to analyse the characteristics of a hybrid shape of square and triangle.
-The idea is to delay the shear layer reattachment.
-which may result in having a larger band of induced angles where the forcing is substantially high.
+The idea is to delay the shear layer reattachment by tapering away the afterbody of the square cross section.
+This may result in having a larger band of induced angles where the forcing is substantially high.
 This will eventually then lead to a higher mean power output.
+
+\input{./figures/proposed_sketch}
 
@@
 The time averaged pressure fields will be obtained in order to analyse the behaviour of the shear layers.}
-\item{The stationary data of the complex shape shown in \hilight{Figure} will be obtained together with the time average pressure fields where the behaviour of the shear layers could be analysed.}
-\item{Based on the initial results an optimisation study will be carried out by changing $l$ and $h$. The quasi-steady model will be used to obtain the power output.}
+\item{The stationary data of the complex shape shown in Fig.\ref{fig:complex_shape} will be obtained together with the time average pressure fields where the behaviour of the shear layers could be analysed.}
+\item{Based on the initial results an optimisation study will be carried out by changing $\frac{d}{l}$. The quasi-steady model will be used to obtain the power output.}
 \item{FSI simulations will be carried out and the power output will be compared with the data obtained using quasi-steady model.}
@@
 %%\end{enumerate}
-%\bibliographystyle{elsarticle-harv}
-%\bibliography{../bibtex/MCR}
+\bibliographystyle{elsarticle-harv}
+\bibliography{../bibtex/paper}
 %\appendix
@@
 \item Mass ratio
+\item FSI validation 
 \item Summary 
@@
 \item Optimisation of the cross sectional shape 
+\begin{enumerate}[i]
+\item Introduction 
+\item Stationary data of basic shapes  
+\item Stationary data of the hybrid cross section
+\item Flow analysis  
+\item Optimisation of the hybrid cross section 
+\item Power analysis 
 \item FSI validation
+\item Summary 
+\end{enumerate}
+
 \item Conclusion

### 2013-11-13 research/MCR report/main.tex
uploaded 13-11-2013 7.05 pm

@@
 \usepackage{graphicx}
-\usepackage{url}
+%\usepackage{url}
 \usepackage{tabulary}
@@
 \usepackage{booktabs}
-\usepackage{placeins}
+%\usepackage{placeins}
 \usepackage{caption}
@@
 %\author{Nishan Dharmaweera \and Rajendran Parthiban \and Y. Ahmet \c{S}ekercio\u{g}lu}
+
 \begin{document}
@@
 Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body.
-The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge.
+The lift force become its maximum when the shear layer closer to the body reattaches at the trailing edge.
 As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force.
@@
 \bibliographystyle{elsarticle-harv}
+
 \bibliography{../bibtex/paper}
-%\appendix
-%%\begin{center}
-%%\section*{\LARGE Appendix 1}
-%%\addcontentsline{toc}{section}{Appendix 1} 
-%%\end{center}
+\appendix
+\begin{center}
+\section*{\LARGE Appendix 1}
+\addcontentsline{toc}{section}{Appendix 1} 
+\end{center}
 Proposed table of contents of the final PhD thesis:

### 2013-11-13 research/paper/results/results-2.3.tex
uploaded 13-11-2013 7.05 pm

@@
 By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.
-The effect of mass ratio was could also be observed where at \reynoldsnumber=165 the mean power tend to decrease at $m^*<40$ which was found out to be an influence of vortex shedding.
+The effect of mass ratio was could also be observed where at \reynoldsnumber=165.
+The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding.
 At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios.
-The cause for this was found out to be the fact that as the mass ratio decreases, due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
+The cause for this was found out to be the fact that when the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
 

### 2013-11-14 research/paper/results/results-2.3.tex
Added m_star part

@@
 
-The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant beyond $m^*=30$.
-However, at $m^* \leq 30$ an effect of $m^*$ it could be observed.
-Not only the peak value but overall reduction in the mean power could be observed when $m^*$ was reduced.
+The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*<30$ in the low \reynoldsnumber case.
+However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
 However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b).
-An influence of vortex shedding on power is present.
-This maybe due to the reduction in inertia as the mass ratio is decreased.
+The suppression of galloping response at low $m^*$ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}.
+This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding.
+The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping.
+Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.
 
-At \reynoldsnumber=22300 two major phenomena could be observed.
-The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)).
+At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$.
+The overall mean power tend to increase  as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)).
 The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)).
 It should be noted that the influence of $U^*$ was observed only for low mass ratios.
-The velocity time traces of example cases of both scenarios Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.
-The displacement signal tend to become more triangular.
-the reason behind the increase in power while reducing mass ratio is due to the fact that the inertia of the system becomes low.
-Therefore the body accelerate faster and attains higher velocity quickly.
-Therefore the time period where the body sustains high velocity increases which will lead to an increase in time period where the body in influenced by the higher forcing, which leads to a higher power output.
-As for the case to where the mean power increases with increasing $U^*$ for a given low mass ratio, the exploration tend to be similar where the only difference being that the at high $U^*$ the period of oscillation tend to increase therefore the body sustains higher velocities for a longer time leading to a higher power output.
+The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave.
+The corresponding displacement signal tend to become more like a triangular wave.
+When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity.
+Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
+However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^0$ degrees which correspond to a transverse velocity of $\frac{\dot{y}}{U}=$.
+Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output.
+For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at ???
+being more dominant on the overall mass of the system when m* is reduced.
 

### 2013-11-14 research/paper/results/results-2.3.tex
Committing small changes to varying mstar section

@@
 
-The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*<30$ in the low \reynoldsnumber case.
+The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for \JL{$m^*>30$} in the low \reynoldsnumber\ case.
 However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
@@
 Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
-However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^0$ degrees which correspond to a transverse velocity of $\frac{\dot{y}}{U}=$.
+However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^\circ$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=$ \JL{?}.
 Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output.

### 2013-11-14 research/paper/figure/mstar_parkinson.tex
Committing small changes to varying mstar section
uploaded..14-11-2013

--- 2013-10-22 research/paper/figure/mstar_parkinson.tex
@@
     \end{picture}
+  \caption{Mean power as a function of damping factor.
+Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios:$m^*=1$ ($\times$), $m^*=5$ (\ding{110}), $m^*=10$ (+), $m^*=50$ (\ding{108})), $m^*=100$ (\ding{116}) and $m^*=1164$ (\ding{83}) at \ustar=175.
+Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$.
+The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.
 }
-  \caption{}
-    \label{fig:collpased_data}
+
+    \label{fig:mstarcollapsed_parkinson}
 \end{figure}

### 2013-11-14 research/paper/results/results-2.3.tex
uploaded..14-11-2013

--- 2013-11-14 research/paper/results/results-2.3.tex
@@
 
-The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*<30$ in the low \reynoldsnumber case.
+The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*>30$ in the low \reynoldsnumber\ case.
 However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
@@
 Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
-However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^0$ degrees which correspond to a transverse velocity of $\frac{\dot{y}}{U}=$.
+However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^\circ$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.1$.
 Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output.

### 2013-11-15 research/paper/results/results-2.3.tex
added efficiency values

@@
 Although the onset of galloping and the point where peak power occur at different $U^*$ when the damping ratio is changed, the peak power remains constant regardless of $U^*$.
+The efficiency of the system could defined as the ratio of $P_m$ and the energy of the fluid per unit length which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}).
+It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
+The peak efficiency in \cite{Barrero-Gil2010a} is lower than what this study obtained.
+This maybe due to the fact that \cite{Barrero-Gil2010a} used a 3rd order polynomial as the function of force prediction.
 
@@
 The effect of mass ratio was could also be observed where at \reynoldsnumber=165.
+The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
 The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding.

### 2013-11-15 research/paper/results/results-2.3.tex
uploaded after corrections for m_star ready for Kenny's Perusal

@@
 It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
-The peak efficiency in \cite{Barrero-Gil2010a} is lower than what this study obtained.
-This maybe due to the fact that \cite{Barrero-Gil2010a} used a 3rd order polynomial as the function of force prediction.
+The peak efficiency in \cite{Barrero-Gil2010a} is approximatly $5\%$ than what this study obtained.
+This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near the maximum force compared to the $7^{th}$ order polynomial used in this study
 
@@
 Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
-However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $6 ^\circ$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.1$.
+However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.0.235$.It is estimated that the efficiency limit i.e $\ustar \rightarrow \infty$  and $m^* \rightarrow 0$ will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.
+Physical systems may not realize the full potential due to practical limitations.
 Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output.
-For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at ???
-being more dominant on the overall mass of the system when m* is reduced.
+For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.
 

### 2013-11-18 research/paper/Theory/mathematical_model.tex
uploaded-18-11-2013

@@
 For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}.
-\cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order polynomial neither provides a significantly better result nor does it exhibit an additional amplitudes of oscillation.
+\cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order polynomial doesn't provides a significantly better result.
 Thus a $7 ^{th}$ order interpolating polynomial was incorporated in this present study.
@@
 
-\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing.
+ It is expected that vortex shedding will be well correlated across the span and provide significant forcing at low \reynoldsnumber.\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing to model this.
 This enables to model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present.
-In this study, the forcing due to VIV is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation.
+In this study, the forcing due to vortex shedding in low \reynoldsnumber cases is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation.
 $\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively.
@@
 In  this study  `Ode 45' routine in MATLAB was used to obtain the solutions.
-However in certain cases (low mass ratios) `Ode 15s' routine was used when Ode 45 tend to diverge.
+However in certain cases (low mass ratios) `Ode 15s' routine was used when Ode 45 had issues with stability due to the non-linear nature of the forcing.
 
@@
 
-The stationary data and the fluid-structure interaction (FSI) data were obtained using a higher order spectral element code to simulate the two-dimensional laminar flow.
+The stationary data and the fluid-structure interaction (FSI) data were obtained using a high order spectral element routine to simulate the two-dimensional laminar flow.
 The Reynolds number was kept at 165 as it was pointed out by \cite{Sheard2009} and \cite{Tong2008} that the 3 dimensional transition for a square cylinder occurs at approximately Re=160.
@@
 
- FSI data were obtained for the oscillating (free-vibration) scenario.
+ Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model.
+The inlet was placed $20D$ while the outlet situated $60D$ away from the centroid of the body.
+The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study.
 The Naiver-Stokes equations were solved using an accelerated frame of reference using the previously mentioned code.

### 2013-11-18 research/paper/introduction/intro-1.0.tex
uploaded-18-11-2013

@@
 
-The search for alternate energy sources which could be categorised  under the ``green" label has become important area of research in the modern word.
+The search for alternate energy sources which could be categorised  under the ``green" label has become an important area of research in the modern word.
 Solar, wind power and wave power are some of the examples of these sources.
@@
 An elastically mounted slender structure such as cylinders which  are susceptible to flow-induced vibrations has the potential for energy extraction.
-With regards to a slender body two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping.
+With regards to a slender bodies, two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping.
 Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV.
-Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties (\cite{Raghavan2010a} , \cite{Lee2011b}) and location (effect of the bottom boundary) (\cite{Raghavan2009}).
+Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties (\cite{Raghavan2010a} , \cite{Lee2011b}) and influence of proximity to solid boundary (\cite{Raghavan2009}).
 However, the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated.
 Some theoretical work was carried out by (\cite{Barrero-Gil2010a}).
-Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow ``lock-in" range of reduced velocities(ratio between the freestream velocity and the product of the natural frequency of the system and the characteristic length).
+Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow ``lock-in" range of reduced velocities(\ustar).
 This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.
-
-Energy harvesting systems have high damping ratios because the energy generator (e.g electrical generator) puts a significant amount of damping into the system.
-Therefore it is crucial to investigate  the behaviour of aeroleastic galloping scenarios at high damping ratios in order to optimise the system to obtain a acceptable power output.
-Hence the focus of this paper is concentrated on investigating the mechanical power output of high-damped galloping systems.
 
@@
 \cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
-The Parkinson's equation was essentially modified to account for the vortex shedding and managed to produce the effects to the amplitude at low mass ratios.
-\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using quasi-steady state theory.
+The Parkinson's equation when modified to account for the vortex shedding and and solved numerically, to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
+\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
 In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low.
-Another interesting conclusion was that energy conversion systems which uses galloping could operate over  a large range of flow velocities unlike VIV energy harvesting systems where the factor of energy conversion has a strong dependence on the incoming flow velocity.
+He studied the influence of the characteristics of the $C_y$ curve on maximum power output.

### 2013-11-18 research/paper/nomenclature.tex
Sketch completed..
uploaded-18-11-2013

@@
-\textbf{Nomenclature}
+\section*{Nomenclature}
+%\textbf{Nomenclature}
 
@@
 $a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
-$C_y$ & instantaneous lift \\
+$C_y$ & instantaneous force coefficient normal to the freesream velocity \\
 $F_y$ & force due to $C_y$  \\ 

### 2013-11-18 research/paper/results/results-2.3.tex
uploaded-18-11-2013

@@
 
-The stationary $C_y$ data obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}.
+The stationary the force characteristic data ($C_y$) as a function of incident angle obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}.
 In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b)),  several differences could be observed.
@@
 Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction.
-Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300 leads one to expect a significant reduction in power at\reynoldsnumber=165 compared to \reynoldsnumber=2230.
+Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300, it is expected that power output at \reynoldsnumber=165 is significantly lower than at \reynoldsnumber=22300.
 

### 2013-11-19 research/paper/figure/cy_vs_theta.tex
uploaded with Kenny's corrections

@@
 
-  \caption{Lift coefficient, $C_y$ \JL{$C_y$ is upper case here, lower case on the figure.
-Make them match what is in the nomenclature}, as a function of incidence angle $\theta$, for a static square cross section.
+  \caption{Lift coefficient, $C_y$, as a function of incidence angle $\theta$, for a static square cross section.
 (a) Data from simulations at $Re=165$  (b) data from \cite{Parkinson1964} at $Re=22300$.
 Points ($\bullet$) are measurements from the simulations.
-The solid lines in both plots are 7th-order interpolating polynomial used to predict the fluid forcing for the QSS model.}
+The solid lines in both plots are 7th-order interpolating polynomial used to predict the fluid forcing for the QSS model.
+$C_y$ is the force coefficient of the force which occurs normal to the induced velocity.}
     \label{fig:lift_curves}

### 2013-11-19 research/paper/figure/uncollapsed_data.tex
new files added
uploaded 12.01 11/11 2013
uploaded with Kenny's corrections

@@
 
-    \put(0.00,0.685){$\frac{A}{D}$}
+    \put(0.00,0.6){$\displaystyle\frac{A}{D}$}
 %    \put(0.52,1.075){$\frac{A}{D}$}
-    \put(0.00,0.44){$\frac{V}{D}$}
+    \put(0.00,0.4){$\displaystyle\frac{V}{D}$}
 %    \put(0.52,0.83){$\frac{V}{D}$}
-    \put(-0.01,0.15){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
+    \put(-0.025,0.15){$\displaystyle\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
 %    \put(0.5,0.54){$\frac{P_{m}}{\rho \mathcal{A}U^3 }$}
@@
   \caption{Velocity amplitude, displacement amplitude and mean power  as functions of $U^*$.
-Data presented in (a), (c) and (e) were calculated using input data at $Re=22300$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}).
-Data presented in (b),(d) and (f) were obtained using input data at $Re=165$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+).
+Data presented in (a), (c) and (e) were calculated using input data at $Re=22300$ and $m^*=1163$ obtained by \cite{Parkinson1964} at three different damping ratios: $\zeta=0.0125$ (\ding{83}), $\zeta=0.015$ (\ding{116}) and $\zeta=0.0175$ (\ding{108}).
+Data presented in (b),(d) and (f) were obtained using input data at $Re=165$ and $m^*=20$ at three different damping ratios: $\zeta=0.075$ ($\times$), $\zeta=0.1$ (\ding{117}) and $\zeta=0.15$ (+).
 The multiple branches for the higher Re are due to the hysteresis between two solutions.}

### 2013-11-19 research/paper/nomenclature.tex
uploaded with Kenny's corrections

@@
 $a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
-$C_y$ & instantaneous force coefficient normal to the freesream velocity \\
+$C_y$ & instantaneous force coefficient normal to the induced velocity \\
 $F_y$ & force due to $C_y$  \\ 

### 2013-11-19 research/paper/results/results-2.3.tex
uploaded with Kenny's corrections

@@
 Hysteresis could be observed for the case with a higher Reynolds number.
-This was achieved by manipulating the initial conditions (initial displacement) of the system.
+Different solutions could be obtained by manipulating the initial conditions (initial displacement) of the system.
 The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude.
-Although a third state could be achieved theoretically, it was not possible to achieve numerically.
+Although a third state could be simulate theoretically, it was not possible to achieve numerically.
 This was also observed by \cite{Vio2007}.
@@
 However, the magnitude of the peaks remain constant for all the values of $\zeta$.
-\cite{Barrero-Gil2010a} also showed a similar trend.
+\cite{Barrero-Gil2010a} also observed a similar behaviour.
 The higher Reynolds number case clearly showed hysteresis in the power data.
@@
 It could be observed that unlike VIV the  system has no preferred frequency.
-Although the onset of galloping and the point where peak power occur at different $U^*$ when the damping ratio is changed, the peak power remains constant regardless of $U^*$.
-The efficiency of the system could defined as the ratio of $P_m$ and the energy of the fluid per unit length which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}).
+Although the onset of galloping and the point where peak power occur at different $U^*$ values when the damping ratio is varied, the peak power remains constant regardless of $U^*$.
+The efficiency of the system could defined as the ratio of the time average power output to $P_{mean}$ the kinetic energy in the fluid per which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}).
 It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
-The peak efficiency in \cite{Barrero-Gil2010a} is approximatly $5\%$ than what this study obtained.
-This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near the maximum force compared to the $7^{th}$ order polynomial used in this study
+The peak efficiency in \cite{Barrero-Gil2010a} is approximately $5\%$ than what this study obtained.
+This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.
 
@@
 This could be expressed as the product of the damping force and the velocity ($P_d$).
-The inertia and the stiffness terms governs the frequency of the system but the forces associated by those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period).
+The inertia and the stiffness terms governs the frequency of the system but the forces associated with those terms are conservative forces (i.e there is zero net energy in or out of the system when averaged over a period).
 Therefore the system is governed by the transverse velocity rather than the natural frequency.
@@
 This further emphasizes that the galloping system is not frequency dependent.
-It is possible to obtain a different similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed.
+It is possible to obtain a similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed.
 An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
@@
 Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative.
-Maximum amount of power could be transferred within the peak region.
+The maximum amount of power that could be transferred occurs near the peak region.
 At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.
@@
 The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e.
-$0<\theta \leq < 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
+$0<\theta \leq 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
 In this case, power output is limited by the low fluid forces present at low incident angles.
@@
 Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle.
-This is because $\theta$  passes the point where both $\theta$ and $C_y$ (therefore $F_y$) are positive.
-The high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e.
+This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e.
 $0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)).
@@
 This is due to the fact that this region is a best compromise between region 1 and 3.
-The damping is substantially high to obtain a high power output while not too high to hinder the induced angle of attack entering the region where the forcing is high.
+The damping is substantially high to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.
 
@@
 Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
-However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.0.235$.It is estimated that the efficiency limit i.e $\ustar \rightarrow \infty$  and $m^* \rightarrow 0$ will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.
+However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.
 Physical systems may not realize the full potential due to practical limitations.
@@
 It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$.
-As power is function of $(\dot{y})^2$ the error between QSS and FSI power becomes significantly large.
+As power is a function of $(\dot{y})^2$ the error between QSS and FSI power is compounded.
 
@@
 In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration.
-The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system.
-This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters).
+At higher $m^*$ ($m^8>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ .
 By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.
 The effect of mass ratio was could also be observed where at \reynoldsnumber=165.
-The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
+The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300  when $\frac{c}{\rho \mathcal{A}U}=0.314$ and $\frac{c}{\rho \mathcal{A}U}=1.04$ respectively.
 The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding.
 At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios.
-The cause for this was found out to be the fact that when the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
+When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
+The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$
 

### 2013-11-21 research/paper/introduction/intro-1.0.tex
Committing comments on abstract and introduction.

@@
 
-The search for alternate energy sources which could be categorised  under the ``green" label has become an important area of research in the modern word.
+The search for alternate energy sources with minimal environmental impact has become an important area of research in the modern word.
 Solar, wind power and wave power are some of the examples of these sources.
-Recently, a new branch of research has been developing to extract energy from flow induced vibrations(\cite{Bernitsas2008a-concept}).
+Recently, a new branch of research has been developing to extract energy from flow induced vibrations \citep{Bernitsas2008a-concept}.
 It has been hypothesized that this technique may work efficiently in areas where regular turbines cannot.
 
-An elastically mounted slender structure such as cylinders which  are susceptible to flow-induced vibrations has the potential for energy extraction.
-With regards to a slender bodies, two common types of   flow induced vibrations are Vortex Induced Vibrations (VIV) and aeroelastic galloping.
+An elastically-mounted slender structure such as a cylinder which is susceptible to flow-induced vibrations has the potential for energy extraction.
+With regards to slender bodies, two common types of flow-induced vibrations are vortex-induced vibrations (VIV) and aeroelastic galloping.
 Significant research has been carried out by Bernitsas and his team on extracting useful energy from VIV.
-Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties (\cite{Raghavan2010a} , \cite{Lee2011b}) and influence of proximity to solid boundary (\cite{Raghavan2009}).
+Some of their significant work includes investigating the influence  of physical parameters such as mass ratio, Reynolds number, mechanical properties \citep{Raghavan2010a, Lee2011b} and the influence of the proximity of a solid boundary \citep{Raghavan2009}.
 However, the possibility of extracting energy using aeroelastic galloping has not been thoroughly investigated.
-Some theoretical work was carried out by (\cite{Barrero-Gil2010a}).
-Utilizing galloping may be a more viable method to harness energy from flow induced vibrations as it is not bounded by a narrow ``lock-in" range of reduced velocities(\ustar).
+Some theoretical work was carried out by \citet{Barrero-Gil2010a}.
+Utilizing galloping may be a more viable method to harness energy from flow-induced vibrations as it is not bounded by a narrow ``lock-in'' range of reduced velocities (\ustar).
 This study further explores the possibility of harnessing energy from flow induced vibrations using aeroelastic galloping.
 
-According to \cite{Paidoussis2010}, \cite{Glauert1919} has provided a criterion for galloping by considering the auto-rotation of an aerofoil.
-\cite{DenHartog1956}  has provided a theoretical explanation for galloping for iced electric transmission lines.
-A weakly non-linear theoretical aeroelastic model to predict the response of galloping was developed by \cite{Parkinson1964} based on the quasi-steady state (QSS) theory.
+According to \citet{Paidoussis2010}, \citet{Glauert1919} provided a criterion for galloping by considering the auto-rotation of an aerofoil.
+\citet{DenHartog1956} provided a theoretical explanation for galloping for iced electric transmission lines.
+A weakly non-linear theoretical aeroelastic model to predict the response of galloping was developed by \citet{Parkinson1964} based on the quasi-steady state (QSS) theory.
 Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model.
@@
 The study managed to achieve a good agreement with experimental data.
-The QSS model equation when solved analytically using sinusoidal solution method cannot predict cases with low mass ratios.
-\cite{Joly2012} have observed that finite element simulations shows a sudden change in amplitudes  below a critical values of the mass ratio.
-The Parkinson's equation when modified to account for the vortex shedding and and solved numerically, to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
-\cite{Barrero-Gil2010a} have investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
+
+However, the QSS model equation when solved analytically using the sinusoidal solution method cannot predict the response for cases with low mass ratios.
+\citet{Joly2012} observed that finite element simulations show a sudden change in amplitude below a critical value of the mass ratio.
+The model equation defined in \citet{Parkinson1964} was modified to account for the vortex shedding and and solved numerically to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
+\citet{Barrero-Gil2010a} investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
 In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low.
-He studied the influence of the characteristics of the $C_y$ curve on maximum power output.
+The same study investigated the influence of the characteristics of the $C_y$ curve on maximum power output.
+
+\JL{Kasun: This is not finished! How does your current study build on these results? Do your conclusions differ from those of Barrero-Gil and Joly?}
+
+\JL{Also, you need to give a description of what is coming in the paper. Something like:
+
+Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically.
+The focus is on the power extraction potential as a function of mass ratio.
+To this end, a series of mass ratios are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 165$, a case that should remain laminar and essentially two-dimensional; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
+Both cases require the input of transverse force coefficients $C_y$ as a function of angle of attack $\alpha$ for a fixed body.
+These data are provided from direct numerical simulations for the $\reynoldsnumber = 165$ case, while the data provided by \citet{Parkinson1964} are used for the $\reynoldsnumber = 22300$ case.
+
+The structure of the paper is as follows.
+Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used.
+Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\alpha$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber\ cases.
+For the low \reynoldsnumber\ case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem.
+Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.}

### 2013-11-21 research/paper/nomenclature.tex
Committing comments on abstract and introduction.

@@
 $\mathcal{A}$ & cross sectional area\\ 
-$F_0$& force due to shedding \\
+$F_0$& amplitude of the oscillatory force due to shedding \\
 $\omega_s$& vortex shedding frequency \\

### 2013-11-21 research/paper/Theory/mathematical_model.tex
Committing comments on abstract and introduction.
Committing mathematical_model.tex

@@
 \section{Background theory}
+\label{sec:theory}
 
-\subsection{Mathematical model (Quasi-steady )}
+\subsection{The quasi-steady state (QSS) model}
 
- One of the widely used mathematical model to predict the system response under galloping is the Quasi-steady state (QSS) model, incorporated by \cite{Parkinson1964} for a square cross section.
-The equation of motion of the body under galloping is given by Eq.\eqref{equationofmotion}.
-The forcing term $F_y$ is given by Eq.\eqref{lift equation}.
+The base quasi-steady state (QSS) model was first developed by \citet{Parkinson1964} for a square cross section. The equation of motion of the body  is given by 
+\begin{equation}
+\label{equationofmotion}
+(m+m_a)\ddot{y}+c\dot{y}+ky=F_y,
+\end{equation}
+where the forcing term $F_y$ is given by
+\begin{equation}
+\label{lift equation}
+F_y=\frac{1}{2}\rho U^2\mathcal{A}C_y.
+\end{equation}
 
@@
 
-\begin{equation}
-\label{equationofmotion}
-(m+m_a)\ddot{y}+c\dot{y}+ky=F_y
-\end{equation}
-
-\begin{equation}
-\label{lift equation}
-F_y=\frac{1}{2}\rho U^2\mathcal{A}C_y
-\end{equation}
-
- In the QSS  model $C_y$ is determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various angles of attack.
-The order of the interpolation polynomial has varied from study to study.
+In the QSS model, it is assumed that the force on the body at a given instantaneous angle of attack $\theta$ (defined in figure \ref{fig:setup_1}) is the same as the mean force on a static body at the same angle of attack.
+The instantaneous value of $C_y$ is therefore determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various $\theta$.
+Using the relationship between $\theta$ and the instantaneous transverse velocity of the body $\dot{y}$ shown in figure \ref{fig:setup_1}, $C_y$ can be written as a function of $\dot{y}$.
+The order of the interpolation polynomial used to define this functio has varied from study to study.
 For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}.
-\cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order polynomial doesn't provides a significantly better result.
-Thus a $7 ^{th}$ order interpolating polynomial was incorporated in this present study.
-
+\cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order doesn't provides a significantly better result.
+Thus a $7 ^{th}$ order interpolating polynomial is used in this present study.
+As a result, $C_y(\dot{y})$ is defined as
 \begin{equation}
 \label{cy ploynomial}
-C_y(\theta)=a_1\left(\frac{\dot{y}}{U}\right)+a_3\left(\frac{\dot{y}}{U}\right)^3+a_5\left(\frac{\dot{y}}{U}\right)^5+a_7\left(\frac{\dot{y}}{U}\right)^7
+C_y(\theta)=a_1\left(\frac{\dot{y}}{U}\right)+a_3\left(\frac{\dot{y}}{U}\right)^3+a_5\left(\frac{\dot{y}}{U}\right)^5+a_7\left(\frac{\dot{y}}{U}\right)^7.
 \end{equation}
@@
 
- It is expected that vortex shedding will be well correlated across the span and provide significant forcing at low \reynoldsnumber.\cite{Joly2012} introduced  an addition of a sinusoidal forcing function to the hydrodynamic forcing to model this.
-This enables to model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present.
-In this study, the forcing due to vortex shedding in low \reynoldsnumber cases is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the RHS of the equation.
-$\omega_{s}$ and $F_0$ represents shedding frequency and the maximum force due to shedding respectively.
-Thus, the final equation is given by Eq.\eqref{final_equation_motion}.
+ It is expected that vortex shedding will be well correlated along the span and provide significant forcing at low \reynoldsnumber.
+\citet{Joly2012} introduced  an additional sinusoidal forcing function to the hydrodynamic forcing to model this.
+This enables the model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present.
+In this study, the forcing due to vortex shedding in low \reynoldsnumber\ cases is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the right-hand side of equation \ref{equationofmotion}.
+Here, $\omega_{s}$ and $F_0$ represent the angular vortex shedding frequency and the maximum force due to shedding respectively.
+Thus, the final equation for the modified QSS model is
 
@@
 \label{final_equation_motion}
-(m{+}m_a)\ddot{y}{+}c{+}\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}
+(m{+}m_a)\ddot{y}{+}c{+}\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
 \end{equation}
 
-This equation could be solved by time integration methods.
-In  this study  `Ode 45' routine in MATLAB was used to obtain the solutions.
-However in certain cases (low mass ratios) `Ode 15s' routine was used when Ode 45 had issues with stability due to the non-linear nature of the forcing.
+This equation could be solved using standard time integration methods.
+In  this study the fourth-order Runge-Kutta scheme built in to the MATLAB routine `ode45' was generally used to obtain the solutions.
+Some low mass ratio cases used a solver modified for stiff problems, built into the `ode15s' routine in MATLAB.
 
@@
 
- The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore the mean power output could be given by Eq.\eqref{power}.
-
+ The dissipated power due to the mechanical damping represents the ideal potential amount of harvested power output. Therefore, the mean power output can be given by
 \begin{equation}
 \label{power}
-P_{mean}=\frac{1}{T}\int_{0}^{T}(c\dot{y})\dot{y} dt
+P_{mean}=\frac{1}{T}\int_{0}^{T}(c\dot{y})\dot{y} dt,
 \end{equation}
+where $T$ is the period of integration and $c$ is the mechanical damping constant.
+
+It should be noted that this quantity is equal to the work done on the body by the fluid, defined as
+\begin{equation}
+\label{power_alt}
+P_{mean}=\frac{1}{T}\int_{0}^{T}F_y\dot{y} dt,
+\end{equation}
+where $F_y$ is the transverse (lift) force.
+
+These two definitions show two important interpretions of the power with respect to any energy production device.
+The first shows that power will be high for situations where the damping coefficient is high, and the transverse velocity is consistently high.
+The second shows that power will be high for situations where the transverse force and the body velocity are in phase.
 
@@
 
-The stationary data and the fluid-structure interaction (FSI) data were obtained using a high order spectral element routine to simulate the two-dimensional laminar flow.
-The Reynolds number was kept at 165 as it was pointed out by \cite{Sheard2009} and \cite{Tong2008} that the 3 dimensional transition for a square cylinder occurs at approximately Re=160.
-$F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \cite{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.
+For the low \reynoldsnumber\ tests, \reynoldsnumber=165 was maintained as it was pointed out by \citet{Sheard2009} and \citet{Tong2008} that the three-dimensional transition for a square cylinder occurs at approximately \reynoldsnumber=160.
+$F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \citet{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.
 
-Shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^0$.
-Stationary $C_y$ data were obtained at different angles of attack ranging from $0^0$ to $16^0$.
-The average power was obtained by using Eq.\eqref{power}
-
-and the averaging was done over no less than 20 galloping periods.
-Predictions of power output at Re=22300 were obtained using coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \cite{Parkinson1964} in order to provide a comparison between high and low Reynolds numbers.
-$m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \cite{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
+The angular vortex shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^\circ$.
+Stationary $C_y$ data were obtained at different angles of attack ranging from $0^\circ$ to $16^\circ$.
+The average power was obtained by using Eq.\eqref{power}, and the averaging was done over no less than 20 galloping periods.
+Predictions of power output at \reynoldsnumber=22300 were obtained using the coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \citet{Parkinson1964}, in order to provide a comparison between high and low Reynolds numbers.
+The mass ration $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \citet{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
 These parameters were used throughout this study unless otherwise specified.
 
+The stationary data and the fluid-structure interaction (FSI) data were obtained using a high-order spectral element routine to simulate the two-dimensional laminar flow.
 Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model.
@@
 The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study.
-The Naiver-Stokes equations were solved using an accelerated frame of reference using the previously mentioned code.
+The Navier--Stokes equations were solved in an accelerated frame of reference attached to the moving body along with the body equation of motion given in equation \ref{equationofmotion}.
 A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution.
-The details of the method could be found in \cite{Thompson2006,Thompson1996a}.
-This code was incorporated in \cite{Leontini2011,Leontini2007a}  where it was employed in a fluid-structure interaction problems.
+The details of the method can be found in \cite{Thompson2006,Thompson1996a}.
+This code has been very well validated in fluid-structure interaction problems \citep{Leontini2011,Leontini2007a}.
 

### 2013-11-21 research/paper/nomenclature.tex
Committing mathematical_model.tex

--- 2013-11-19 research/paper/nomenclature.tex
@@
 $Re$& Reynolds number  \\
-$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle \\
+$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle of attack\\
 & \\

### 2013-11-21 research/paper/introduction/intro-1.0.tex
Committing mathematical_model.tex
Committing intro after merging versions and minor changes to mathematical_model (title of section)

@@
 
-\JL{Kasun: This is not finished! How does your current study build on these results? Do your conclusions differ from those of Barrero-Gil and Joly?}
-
-\JL{Also, you need to give a description of what is coming in the paper. Something like:
-
-Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically.
-The focus is on the power extraction potential as a function of mass ratio.
-To this end, a series of mass ratios are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 165$, a case that should remain laminar and essentially two-dimensional; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
-Both cases require the input of transverse force coefficients $C_y$ as a function of angle of attack $\alpha$ for a fixed body.
+Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically for low Reynolds numbers.
+The focus is on the power extraction potential as a function of mechanical parameters (i.e.
+frequency of oscillation, damping factor and mass ratio).
+To this end, a series of previously mentioned mechanical parameters are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 165$, a case that should remain laminar and essentially two-dimensional; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
+Both cases require the input of transverse force coefficients $C_y$ as a function of angle of attack $\theta$ for a fixed body.
 These data are provided from direct numerical simulations for the $\reynoldsnumber = 165$ case, while the data provided by \citet{Parkinson1964} are used for the $\reynoldsnumber = 22300$ case.
@@
 Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used.
-Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\alpha$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber\ cases.
-For the low \reynoldsnumber\ case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem.
+Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber cases.
+For the low \reynoldsnumber case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem.
 Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.}

### 2013-11-22 research/paper/figure/coefficient-table.tex
applied kenny's changes
Committing small changes to th mathematical model and some initial changes to the results section

@@
 \caption{Coefficient values used in the 7th order interpolation polynomial for high ($Re=22300$) and low ($Re=165$) Reynolds numbers.
-These data are used as input data to calculate the RHS of Eq.\ref{final_equation_motion} throughout this study.}
+These data are used as input data to calculate the right-hand side of Eq.
+\ref{final_equation_motion} throughout this study.}
 
-\label{table:nonlin} % is used to refer this table in the text
+\label{table:cy-coefficients} % is used to refer this table in the text
 \end{center}

### 2013-11-22 research/paper/results/results-2.3.tex
Committing comments on abstract and introduction.
Committing mathematical_model.tex
Committing small changes to th mathematical model and some initial changes to the results section

@@
 \section{Results}
+\label{sec:results}
 
@@
 
-The stationary the force characteristic data ($C_y$) as a function of incident angle obtained using flow simulations (Fig.\ref{cy ploynomial}(a)) have a good agreement with data presented in \cite{Joly2012}.
-In comparison with the 7th order polynomial curve at \reynoldsnumber=22300 (Fig.\ref{cy ploynomial}(b)),  several differences could be observed.
-The peak value of $C_y$ is  significantly low at \reynoldsnumber=165 ($C_y=0.05$ at $4^0$) in comparison with \reynoldsnumber=22300 ($C_y=0.57$ at $13^0$) .
-The inflection point present at \reynoldsnumber=22300 could not be observed at \reynoldsnumber=165.
+The characteristic lift force data for a stationary body ($C_y$) as a function of incident angle $\theta$ obtained using flow simulations are shown in figure \ref{cy ploynomial}(a).
+They agree well with the low \reynoldsnumber\ data presented in \citet{Joly2012}.
+
+However, there are several differences that can be observed when the low \reynoldsnumber\ data are compared with the $7^{th}$ order polynomial curve at $\reynoldsnumber=22300$ shown in figure \ref{cy ploynomial}(b).
+The peak value of $C_y$ is  significantly lower at $\reynoldsnumber=165$ ($C_y=0.05$ at $4^\circ$) in comparison with $\reynoldsnumber=22300$ ($C_y=0.57$ at $13^\circ$) .
+The inflection point present around $8^\circ$ for $\reynoldsnumber=22300$ is not observed at $\reynoldsnumber=165$.
 This agrees with the findings of \cite{Luo2003}.
-It was concluded by \cite{Luo2003} that hysteresis occur due to the inflection point found in the $C_y$ curve.
-Therefore hysteresis is not expected at \reynoldsnumber=165.
-The range of the incident flow angles where $C_y$ remain positive is narrow at \reynoldsnumber=165 ($0^0 <\theta \leq$ $6^0$) compared to \reynoldsnumber=22300 ($0^0 <\theta \leq 15^0$).
-This feature is what sustains galloping and power is transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder.
-Incident angles beyond this range actually suppresses the galloping and power goes in the opposite direction.
-Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for \reynoldsnumber=165 compared to \reynoldsnumber=22300, it is expected that power output at \reynoldsnumber=165 is significantly lower than at \reynoldsnumber=22300.
+
+It was concluded by \cite{Luo2003} that hysteresis in the system response occurs due to the inflection point in the $C_y$ curve. Therefore hysteresis is not expected at $\reynoldsnumber=165$.
+
+The range of incident flow angles where $C_y$ remains positive is narrow at $\reynoldsnumber=165$ ($0^\circ <\theta \leq$ $6^\circ$) compared to $\reynoldsnumber=22300$ ($0^\circ <\theta \leq 15^\circ$).
+This feature is what sustains galloping.
+Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder, as demonstrated by equation \ref{power_alt}.
+Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; form body to fluid.
+Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=165$ compared to $\reynoldsnumber=22300$, it is expected that power output at $\reynoldsnumber=165$ is significantly lower than at $\reynoldsnumber=22300$.
 
@@
 Hence the damping coefficient reduces when you move from region 1 to 3.
-Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^0$ where it peaks and then falls and at around $6^0$ becomes negative.
+Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls and at around $6^\circ$ becomes negative.
 The maximum amount of power that could be transferred occurs near the peak region.
@@
 The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e.
-$0<\theta \leq 4^0$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
+$0<\theta \leq 4^\circ$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
 In this case, power output is limited by the low fluid forces present at low incident angles.
@@
 This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e.
-$0<\theta<6^0$ in Fig.\ref{cy ploynomial} (a)).
+$0<\theta<6^\circ$ in Fig.\ref{cy ploynomial} (a)).
 In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times.
@@
 In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e.
-$\theta=4^0$ in \ref{cy ploynomial} (a)).
+$\theta=4^\circ$ in \ref{cy ploynomial} (a)).
 The dips in $P_d$ between the two peaks approximately correspond to the time where the transverse velocity is higher than 0.07 and $F_y$ is decreasing with increasing transverse velocity.
@@
 \section{Conclusion}
+\label{sec:conc}
 

### 2013-11-22 research/paper/results/results-2.3.tex
Committing small changes to th mathematical model and some initial changes to the results section
Committing some changes to results, still working

@@
 
-\subsection{Displacement,velocity and power output as a function of reduced velocity}
+\subsection{Displacement, velocity and power output as a function of reduced velocity}
 
- The quasi-steady analysis data reveals that the displacement amplitude tend to grow with increasing $U^*$ (Fig.\ref{fig:uncollapsed_data} (a) and (b)).
-The onset of galloping is delayed with increasing $\zeta$ for both high and low Reynolds numbers.
-This echo the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}.
+ The quasi-steady analysis data reveal that the displacement amplitude grows with increasing $U^*$.
+This is shown for both the high and low \reynoldsnumber\ cases in figures \ref{fig:uncollapsed_data} (a) and (b).
+The onset of galloping is delayed with increasing damping ratio $\zeta$ for both high and low Reynolds numbers.
+This echos the findings of previous studies by \cite{Parkinson1964} and \cite{Barrero-Gil2010a}.
 Hysteresis could be observed for the case with a higher Reynolds number.
@@
 The upper branch was obtained by giving an initial displacement which was higher than the expected amplitude while the lower branch was obtained by providing a lower initial displacement than the expected amplitude.
-Although a third state could be simulate theoretically, it was not possible to achieve numerically.
+Although theory shows a possible third state, it is an unstable branch and as such it could not be achieved numerically.
 This was also observed by \cite{Vio2007}.
@@
 
- The mean power grows, peaks and then reduces as $U^*$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)) for each value of $\zeta$.
-The value of  \ustar at which the peak power occur increases with $\zeta$.
+ The mean power grows, peaks and then slightly reduces as the reduced velocity $U^*$ is increased.
+This is shown in figure \ref{fig:uncollapsed_data}(e) and (f) for each value of $\zeta$.
+The value of  \ustar\ at which the peak power occurs increases with $\zeta$.
 However, the magnitude of the peaks remain constant for all the values of $\zeta$.
-\cite{Barrero-Gil2010a} also observed a similar behaviour.
-The higher Reynolds number case clearly showed hysteresis in the power data.
-The range of hysteresis tend to increase with increasing $\zeta$.
-It could be observed that unlike VIV the  system has no preferred frequency.
-Although the onset of galloping and the point where peak power occur at different $U^*$ values when the damping ratio is varied, the peak power remains constant regardless of $U^*$.
-The efficiency of the system could defined as the ratio of the time average power output to $P_{mean}$ the kinetic energy in the fluid per which is $\rho U^3\frac{D}{2}$(similar to \cite{Barrero-Gil2010a}).
-It was found out that the  system has a peak efficiency of  $0.26\%$  for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300.
-The peak efficiency in \cite{Barrero-Gil2010a} is approximately $5\%$ than what this study obtained.
-This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing near where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.
+\citet{Barrero-Gil2010a} also observed a similar behaviour.
+The higher Reynolds number case clearly shows hysteresis in the power data.
+The range of hysteresis increases with increasing $\zeta$.
+
+Unlike VIV, which is a resonant-type phenomenon, the quasi-steady system describing galloping has no strongly preferred frequency.
+Although the onset of galloping and the value of \ustar\ where peak power occurs varies with the damping ratio $\zeta$, the power extracted remains almost constant for values of \ustar\ beyond that where the peak power occurs.
+
+The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3\frac{D}{2}$, the kinetic energy in the fluid approaching the body.
+A similar definition was given in \citet{Barrero-Gil2010a}).
+The current results show that the system has a peak efficiency of $0.26\%$  for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$.
+The peak efficiency reported in \citet{Barrero-Gil2010a} for \JL{KASUN: include the Re from Barrero-Gil} is approximately $5\%$ less than the current result.
+This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing at values of $\theta$ where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.
+
+\JL{Up to here 12.20pm}
 

### 2013-11-22 research/paper/Theory/mathematical_model.tex
Committing intro after merging versions and minor changes to mathematical_model (title of section)
Committing small changes to th mathematical model and some initial changes to the results section
uploaded 22-11-2013 10.34 pm

@@
-\section{Background theory}
+\section{Problem formulation and methodology}
 \label{sec:theory}
@@
 Using the relationship between $\theta$ and the instantaneous transverse velocity of the body $\dot{y}$ shown in figure \ref{fig:setup_1}, $C_y$ can be written as a function of $\dot{y}$.
-The order of the interpolation polynomial used to define this functio has varied from study to study.
+The order of the interpolation polynomial used to define this function has varied from study to study.
 For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}.
@@
 The details of the method can be found in \cite{Thompson2006,Thompson1996a}.
-This code has been very well validated in fluid-structure interaction problems \citep{Leontini2011,Leontini2007a}.
+This code has been very well validated in a variety of fluid-structure interaction problems \citep{Leontini2007a,Griffith2011,Leontini2011,Leontini2013}.
 

### 2013-11-22 research/paper/introduction/intro-1.0.tex
Committing small changes to th mathematical model and some initial changes to the results section
uploaded 22-11-2013 10.34 pm

@@
 Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber cases.
-For the low \reynoldsnumber case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem.
-Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.}
+For the low \reynoldsnumber case, the results of the QSS model are compared to those of full direct numerical simulations of
+
+the fluid-structure interaction problem. Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.

### 2013-11-22 research/paper/results/results-2.3.tex
uploaded 22-11-2013 10.34 pm
Small changes to work from home

@@
 
-\JL{Up to here 12.20pm}
-
 \subsection{Galloping response and natural frequency}
@@
 Therefore the system is governed by the transverse velocity rather than the natural frequency.
+
+\JL{KASUN: I don't understand the above paragraph.
+What is the main point of this paragraph?
+Are you trying to show that the only the terms dependent on $\dot{y}$ are dissipative, and so only those terms contribute to the transfer of energy or power to the body?
+That is true, but that is also true for VIV, so I don't see how that shows that the ``system is governed by the transverse velocity rather than the natural frequency''.
+I definitely don't understand that last sentence.
+Do you mean ``power'' when you say ``system''?
+The problem is that, as I've pointed out, the exact same argument regarding dissipation applies to VIV, which is strongly dependent on the natural frequency.}
 

### 2013-12-13 research/paper/Theory/mathematical_model.tex
Small changes to work from home
Committing first part of explanation of non-dimensionalization in terms of timescales

@@
 \end{equation}
+\JL{KASUN: why do you have an added mass term here? This implies that you have decomposed the lift force into components. I think you should remove it here and from the rest of the document.}
 where the forcing term $F_y$ is given by
@@
 \label{final_equation_motion}
-(m{+}m_a)\ddot{y}{+}c{+}\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
+(m{+}m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
 \end{equation}
@@
 A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and \reynoldsnumber=$165$.
-A $9^{th}$ order polynomial together with a time step of $\frac{\Delta tU}{D}=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.
+A $9^{th}$ order polynomial together with a time step of $\Delta tU/D=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

### 2013-12-13 research/paper/nomenclature.tex
Committing first part of explanation of non-dimensionalization in terms of timescales

--- 2013-11-19 research/paper/nomenclature.tex
@@
 $c$ & damping constant/damping factor \\
+\cstar & non-dimensionalised damping factor \\
 $k$ & spring constant \\
@@
 $A$ & displacement amplitude\\
-$\mathcal{A}$ & cross sectional area\\ 
-$F_0$& force due to shedding \\
+$\mathcal{A}$ & frontal area of the body\\ 
+$F_0$& amplitude of the oscillatory force due to shedding \\
 $\omega_s$& vortex shedding frequency \\

### 2013-12-13 research/paper/results/results-2.3.tex
Committing first part of explanation of non-dimensionalization in terms of timescales

@@
 This feature is what sustains galloping.
-Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating cylinder, as demonstrated by equation \ref{power_alt}.
+Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating body, as demonstrated by equation \ref{power_alt}.
 Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; form body to fluid.
@@
 The current results show that the system has a peak efficiency of $0.26\%$  for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$.
-The peak efficiency reported in \citet{Barrero-Gil2010a} for \JL{KASUN: include the Re from Barrero-Gil} is approximately $5\%$ less than the current result.
+The peak efficiency reported in \citet{Barrero-Gil2010a} for $\reynoldsnumber=22300$ is approximately $5\%$ less than the current result.
 This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing at values of $\theta$ where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.
@@
 
+%%%%%%%%%
+The data presented in figure \ref{fig:uncollapsed_data} show that, regardless of the damping ratio $\zeta$, the trend of the response with $U^*$ is similar, suggesting the data can be collapsed by a suitable choice of parameters.
+These parameters can be found by considering the natural time scales of the equations of motion presented in equation \ref{final_equation_motion}, and by suitably non-dimensionalizing these equations.
+
+The natural time scales of the system can be found by solving for the eigenvalues of the linearized equation of motion, namely
+\begin{equation}
+\label{eqn:eom_linear}
+(m{+}m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
+\end{equation}
+which is simply the equation of motion presented in equation \ref{final_equation_motion} with the polynomial series for the lift force truncated at the linear term, and the forcing term representing vortex shedding removed.
+
+Combining the $\dot{y}$ terms and solving for eigenvalues gives
+\begin{equation}
+  \label{eqn:eigs}
+  \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}\right]^2-4\frac{k}{m}}.
+\end{equation}
+
+If it is assumed that the spring is relatively weak, $k\rightarrow 0$, a single non-zero eigenvalue remains. This eigenvalue is
+\begin{equation}
+  \label{eqn:eigs_nospring}
+  \lambda=-\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}.
+\end{equation}
+
+Further, if it is assumed that the mechanical damping is significantly weaker than the aerodynamic forces on the body, $c\rightarrow 0$ and
+\begin{equation}
+  \label{eqn:eigs_nospring_nodamp}
+  \lambda=\frac{\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}.
+\end{equation}
+
+In this form, $\lambda$ represents the inverse time scale of the of the motion of the body due to the negative damping effect of the long-time aerodynamic forces.
+In fact, the terms can be regrouped and $\lambda$ written as
+\begin{equation}
+  \label{eqn:timescale}
+  \lambda = \frac{a_1}{m^*}\frac{U}{D}
+\end{equation}
+
+Written this way, the important parameters that dictate this inverse time scale are clear.
+The rate of change in the aerodynamic force with respect to angle of attackwhen the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$.
+The mass ratio is represented by $m^*$.
+The inverse advective time scale of the incoming flow is represented by the ratio $U/D$.
+Increasing $a_1$ would mean the force on the body would increase more rapidly with small changes in the angle of attack, $\theta$, or transverse velocity.
+Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously dcrease the response time of the body.
+Increasing the mass of the body, thereby increasing $m^*$, has the opposite effect.
+The inverse time scale is decreased, or as might be expected, a heavier body will take longer to respond.
+
+This timescale can then be used to non-dimensionalize the equation of motion, and to find the relevant dimensionless groups of the problem.
+If the non-dimensional time, $\tau$, is defined such that $\tau=t(a_1/m^*)(U/D)$, the equation of motion presented in equation \ref{final_equation_motion} can be non-dimensionalized as
+\begin{equation}
+  \label{eqn:eom_nondim}
+  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{k}{m}\frac{D^2}{U^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} \dots
+\end{equation}
+%%%%%%%%%
+
+\JL{Stopped here}
+
  Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because the scale with the natural frequency of the system.
@@
 
- The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve).
+ The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve).
 These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $\frac{c}{\rho\mathcal{A}U}$

### 2013-12-16 research/paper/figure/velocity_compare.tex
uploaded 12.01 11/11 2013
Committing changes and suggestions up to the 'effect of m*' section

@@
 
-    \put(0.03,0.95){ $\frac{V}{D}$} 	
+    \put(0.02,0.95){ $\displaystyle\frac{V}{D}$} 	
     % \put(0.56,1.02){ $\frac{V}{D}$}
 
-    \put(0.25,0.805){ $\frac{tU}{D}$} 	
-    \put(0.73,0.805){ $\frac{tU}{D}$}
+    \put(0.25,0.80){ $\displaystyle\frac{tU}{D}$} 	
+    \put(0.73,0.80){ $\displaystyle\frac{tU}{D}$}
 
-    \put(0.095,1.03){(a)}
-    \put(0.565,1.03){(b)}
+    \put(0.095,1.035){(a)}
+    \put(0.565,1.035){(b)}
 
@@
 Both data sets were obtained using Quasi-steady state assumption using input $C_y$ parameters at $Re=165$.
-Shedding is evident in both signals as a high frequency fluctuation but the amplitude of the slower fluctuations remains constant in both cases.}
+Shedding is evident in both signals as a high frequency fluctuation but the amplitude of the slower fluctuations remains constant in both cases.
+\JL{KASUN: The different scale on the x-axes make these two plots difficult to compare.
+I think a more powerful comparison can be made by keeping the x-scale the same (include more periods of the case at $U^*=60$).
+Then it is clear that even though the oscillation happens over a longer time, the average power output is constant.
+You could also include a plot where you rescale time by the time scale I derived, $\tau=\tau=t(a_1/m^*)(U/D)$.
+I'm pretty certain that, apart from the high frequency shedding component, the two plots would lok the same using this time scale}}
     \label{fig:time_hostory_velocity_same_power}

### 2013-12-16 research/paper/results/results-2.3.tex
Committing changes and suggestions up to the 'effect of m*' section

@@
 
- Now the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective.
+ % Now the oscillator equation Eq.\eqref{final_equation_motion} is considered from a power perspective.
 The shedding forces can be neglected because the net effect is negligible as system oscillates at natural frequency which is far from shedding frequency, for the cases that exhibit galloping.
@@
 
-%%%%%%%%%
 The data presented in figure \ref{fig:uncollapsed_data} show that, regardless of the damping ratio $\zeta$, the trend of the response with $U^*$ is similar, suggesting the data can be collapsed by a suitable choice of parameters.
@@
   \label{eqn:eom_nondim}
-  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{k}{m}\frac{D^2}{U^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} \dots
+  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} \dots,
 \end{equation}
-%%%%%%%%%
 
-\JL{Stopped here}
+where the coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
+\begin{equation}
+  \label{eqn:eom_nondim_regroup}
+  \ddot{Y} + \frac{k^{*2}m^{*2}}{a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} \dots,
+\end{equation}
 
- Using $U^*$ and $\zeta$ assumes that the system has a preferred frequency because the scale with the natural frequency of the system.
-The effect of fixing $\zeta$ and increasing $U^*$ actually decreases the damping constant for a fixed free-stream velocity.
-($U^*=\frac{U}{f \times D}$, $\zeta= \frac{c}{2 m \omega_n}$ ).
-Both these effects leads to the multiple lines that are horizontally transpose when $\zeta$ is increased (Fig.\ref{fig:uncollapsed_data} (e) and (f)).
-Therefore the effect of $\zeta$ essentially scales up the damping coefficient for a fixed $U^*$.
+where $k^*=kD^2/mU^2$ is a non-dimensional stiffness parameter, and $c^*=cD/mU$ is a non-dimensional damping parameter.
 
- The data presented in Fig.\ref{fig:uncollapsed_data} for various damping ratios, $\zeta$, can be collapsed into a single line for a particular force characteristic curve (i.e $C_y$ vs $\theta$ curve).
-These collapsed curves were  obtained for the velocity amplitude  and power by plotting as functions of as a function of  the non dimensionalised  damping constant $\frac{c}{\rho\mathcal{A}U}$
-(Fig \ref{fig:collpased_data} (a),(b),(c) and (d)).
-This further emphasizes that the galloping system is not frequency dependent.
-It is possible to obtain a similar power output at different values of \ustar when the damping constant, $\frac{c}{\rho\mathcal{A}U}$, is kept fixed.
-An example of this case, as shown in Fig.\ref{fig:time_hostory_velocity_same_power}, clearly show that this is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
-As mentioned earlier, it is the transverse velocity that determines the energy provided by the fluid forcing and the mechanical damping.
+Equation \ref{eqn:eom_nondim_regroup} shows there are four non-dimensional parameters that play a role in setting the response of the system.
+These are the stiffness $k^*$, the damping $c^*$, the mass ratio $m^*$, and the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$.
+The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = k^{*2}m^{*2}/a_1^2$ and $\Gamma_2 = c^*m^*/a_1$.
+For a given geometry and Reynolds number, $Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter.
+As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.
+
+Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter $\Gamma_2$.
+The collapse, especially of the velocity amplitude and power output data, is excellent.
+This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, $\Gamma_2$, is kept fixed.
+An example of this is shown in Fig.\ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\Gamma_2=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted.
+The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
 
@@
 
- Power could be expressed as the product of force and velocity.
-Therefore the transferred power form fluid-to-body could be expressed as $P_t=F_y\dot{y}$.
-Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$.
-The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction is neglected .
-Analysing the  time histories of $P_t $ and $P_d$ at key regions (Fig.\ref{fig:regions_1}) on the mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased.
+Power can be expressed as the product of force and velocity.
+Therefore the transferred power fromm the fluid to the body can be expressed as $P_t=F_y\dot{y}$, as shown in equation \ref{power_alt}.
+Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$ as shown in equation \ref{power}.
+The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction losses are neglected.
+The mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased.
 The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar.
+Time histories of $P_t $ and $P_d$ at each of these key regions are presented in figure \ref{fig:power_time_histories}.
+
+\JL{KASUN: why have you established that it is the damping, not $U^*$, that is important, but here you persist with presenting results in terms of $U^*$?
+How do these regions correspond to regions on the curve in terms of your damping parameter (that I have labelled $\Gamma_2$)?
+Can you define these three regions in terms of this new parameter?}
+
 It has been established earlier that the damping factor is a function of $U^*$.
@@
 Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.
+
+\JL{KASUN: I don't understand the point of the above paragraph. What are you trying to say? That maximum power output occurs when the tranverse velocity is such that the lift force is a maximum?}
 
@@
 
- At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal could be observed for both $P_d$ and $P_t$ in Fig.\ref{fig:power_time_histories} (a).
-Fig.\ref{fig:power_time_histories} (d) and (g) shows that $\theta$ is in line or in phase with $F_y$.
-The velocity amplitude in this case is small and the equivalent incident angle within the range where the hydrodynamic force increases with the incident angle (i.e.
-$0<\theta \leq 4^\circ$ in Fig.\ref{fig:lift_curves} (a)) Hence both $P_d$ and $P_t$ becomes sinusoidal.
-In this case, power output is limited by the low fluid forces present at low incident angles.
-In other words damping is significantly high and extracts a lot of power that the velocity amplitude could not grow where the forcing  is significant to produce high level of power.
+At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal is observed for both $P_d$ and $P_t$ in figure \ref{fig:power_time_histories}(a).
+Figures \ref{fig:power_time_histories}(d) and  \ref{fig:power_time_histories}(g) show that equivalent incident angle $\theta$ (which for small values, is proportional to the transverse velocity of the body) is in phase with $F_y$.
+The velocity amplitude in this case is small and $\theta$ is within the range where the hydrodynamic force increases with the incident angle (i.e.
+$0<\theta \leq 4^\circ$ as shown in figure \ref{fig:lift_curves}(a)).
+According to equation \ref{power_alt}, these conditions are suitable for high power output.
+However in this case, the power output is limited by the high damping which limits the amplitude of the oscillation.
 
-  At region 3 ($U^*= 400$) `$c$' is low in comparison with region 1 and 2 which leads to a low mean power output.
+At region 3 ($U^*= 400$) the damping is low in comparison with region 1 and 2.
+While this may lead to larger oscillations, damping is required to dissipate power according to equation \ref{power}.
+Therefore, the low damping in this region leads to a low mean power output.
 Fig.\ref{fig:power_time_histories} (c) shows that $P_t$ becomes negative over some portion of the cycle.
-This is caused by te high velocity amplitude leads to the equivalent incident angle $\theta$, in this case to exceed the range where $C_y$ is positive (i.e.
-$0<\theta<6^\circ$ in Fig.\ref{cy ploynomial} (a)).
+This is caused by the high velocity amplitude leading to the equivalent incident angle $\theta$ to exceed the range where $C_y$ is positive (i.e.
+$0<\theta<6^\circ$ as shown in figure\ref{cy ploynomial}(a)).
 In this portion of the cycle the hydrodynamic force actually opposes the direction of travel and power is transferred from the structure to the fluid during those times.
-From and energy perspective, the mechanical damping is not sufficient to remover the energy transferred from the fluid to the structure during other times of the cycle because $\frac{c}{\rho\mathcal{A}U}$ is substantially low.
-Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories} (c)
+From an energy perspective, the mechanical damping is not sufficient to removerthe energy transferred from the fluid to the structure during other times of the cycle because $\Gamma_2$ is substantially low.
+Therefore this excess energy is transferred back to the fluid as depicted by the negative region of $P_d$ in Fig.\ref{fig:power_time_histories}(c).
 
-At region 2 ($U^*=165$).
-$P_t$ is not a pure sinusoidal signal.
-However, the  signal remains periodic.
-From the time history graph of $P_t$, two `peaks' are present in a single half cycle (Fig \ref{fig:power_time_histories} (b)).
+At region 2 ($U^*=165$), a balance is found between high and low values of damping.
+$P_t$ is not a pure sinusoidal signal, however the signal remains periodic.
+From the time history graph of $P_t$, two `peaks' are present in a single half cycle as shown if figure \ref{fig:power_time_histories}(b).
 In this case, the velocity amplitude actually exceeds the equivalent incident angle where the hydrodynamic forces peaks (i.e.
@@
 The mean power output is at its maximum.
-This is due to the fact that this region is a best compromise between region 1 and 3.
-The damping is substantially high to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.
+This is due to the fact that this region is the best compromise between region 1 and 3.
+The damping is high enough to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.
+
+\JL{KASUN: nothing to change here, just wanted to note that this paragraph is good. Clear, and to the point.}
 

### 2013-12-16 research/paper/results/results-2.3.tex
Committing text changes and suggestions through to the end of the paper. Still need to go back and make sure our parameters are understood in terms of Parkinson's work

@@
 
-\subsection{Galloping response and natural frequency}
+\subsection{Galloping response and governing parameters}
 
@@
 
-The maximum mean power at different $m^*$ (Fig.\ref{fig:m_star_collapsed}(a)) was constant for $m^*>30$ in the low \reynoldsnumber\ case.
-However, at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
-However, when the sinusoidal forcing function in Eq.\ref{equationofmotion} which cater for the vortex shedding was disregarded, the reduction in power could not be observed Fig.\ref{fig:m_star_collapsed}(b).
-The suppression of galloping response at low $m^*$ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}.
+The mean power at different $m^*$ is presented as a function of the mass-damping parameter $\Gamma_2$ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case.
+For $m^*>30$, the power output is essentially independent of $m^*$, while at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
+However, when the sinusoidal forcing function in equation \ref{equationofmotion}, which caters for the vortex shedding, is disregarded, the reduction in power is not observed as shown in figure \ref{fig:m_star_collapsed}(b).
+The suppression of galloping response at low $m^*$ and low \reynoldsnumber\ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}.
 This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding.
@@
 
-At \reynoldsnumber=22300 power output started to increase for cases with $m^*<50$.
+At $\reynoldsnumber=22300$ power output started to increase for cases with $m^*<50$.
 The overall mean power tend to increase as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)).
@@
 
+\JL{KASUN, again this last paragraph is all in terms of $U^*$, but you establish earlier that $U*^$ is not the important parameter, your new damping parameter (which is actually a mass-damping parameter) is the critical parameter.
+Can this argument be rewritten in terms of this new parameter?}
+
 \input{../figure/time_history_msar_mass}
@@
 \subsection{Comparison with FSI simulations}
- Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations (Fig.
-\ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b)).
-Quantitatively a large discrepancy (average of $30\%$) could be observed between QSS and FSI data.
-Therefore the power also becomes significantly low in FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)).
-However, the FSI data (Fig.\ref{fig:FSI_QSS_compare} (c)) were able to produce the main the rise and the fall of mean power when $U^*$ was increased.
-The reasoning behind this fact is that galloping is weak at \reynoldsnumber$=165$  and therefore fluid damping has a significant effect.
+As the results to this point are based on solving equations which come from the quasistatic assumption, it is natural to query how these results compare to the real flow.
+Here, results are presented of full fluid-structure direct numerical simulations (FSI) at $\reynoldsnumber=165$ and compared to the results obtained from the quasistatic model (QSS) at the same \reynoldsnumber.
+
+Qualitatively, the two compare very well.
+Similar trends were captured for both displacement and velocity amplitudes between QSS and FSI simulations as shown in figures \ref{fig:FSI_QSS_compare}(a) and \ref{fig:FSI_QSS_compare}(b).
+However, there is a reasonably large quantitative discrepancy (average of $30\%$) between QSS and FSI data, with the QSS model overpredicting the response of the body.
+Therefore the predicted power output is reduced in the FSI data, as shown in figure \ref{fig:FSI_QSS_compare}(c).
+However, the FSI data does produce the main rise and fall of mean power when $U^*$ was increased.
+
+The exact reason behind this discrepancy is unclear.
+A possible explanation is that galloping is reasonably weak at $\reynoldsnumber=165$.
 It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$.
+It may be that simulations conducted so close to the threshold for the onset of galloping are very sensitive to errors due to blockage or under-resolution, both of which can change the effective \reynoldsnumber of the flow.
+Small changes in effective \reynoldsnumber\ can have a significant impact of the fluid damping, and therefore on the amplitude and transverse velocity of the body.
 As power is a function of $(\dot{y})^2$ the error between QSS and FSI power is compounded.
@@
 In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration.
-At higher $m^*$ ($m^8>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ .
-By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.
-The effect of mass ratio was could also be observed where at \reynoldsnumber=165.
-The peak efficiency was found out to be $0.26\%$ for \reynoldsnumber=165 and $6.7\%$ for \reynoldsnumber=22300  when $\frac{c}{\rho \mathcal{A}U}=0.314$ and $\frac{c}{\rho \mathcal{A}U}=1.04$ respectively.
-The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding.
-At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios.
-When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
-The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$
+At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ .
+By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant.
+The effect of mass ratio was also observed.
+The peak efficiency was found to be $0.26\%$ for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$  when $\Gamma_2=0.314$ and $\Gamma_2=1.04$ respectively.
+In the low \reynoldsnumber\ case, the mean power tends to decrease at $m^*<30$ which appears to be due to the influence of vortex shedding.
+At $\reynoldsnumber=22300$ the opposite is observed where the mean power tends to increase with decreasing mass ratio, as well as the mean power increasing with increasing $U^*$ at low mass ratios.
+For this higher \reynoldsnumber\ case, When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
+The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$.
 

### 2013-12-16 research/paper/Theory/mathematical_model.tex
Committing what I think is my last bit before submission. Kasun still needs to fix some stuff up, there are notes in the document to him

@@
 \label{equationofmotion}
-(m+m_a)\ddot{y}+c\dot{y}+ky=F_y,
+m\ddot{y}+c\dot{y}+ky=F_y,
 \end{equation}
-\JL{KASUN: why do you have an added mass term here? This implies that you have decomposed the lift force into components. I think you should remove it here and from the rest of the document.}
 where the forcing term $F_y$ is given by
@@
 \end{equation}
+\citet{lighthill1986} showed that for systems oscillating in fluid, it is sometimes useful to decompose the fluid forces into components that are in and out of phase with the body acceleration.
+The component in phase with the acceleration effectively adds to the inertia or effective mass of the system.
+Therefore, an added mass term, $m_a$, can be added to the system mass.
+For consistency with previous studies such as \citet{Joly2012}, a value of $m_a=3.5$ has been used here.
 
@@
 
-In the QSS model, it is assumed that the force on the body at a given instantaneous angle of attack $\theta$ (defined in figure \ref{fig:setup_1}) is the same as the mean force on a static body at the same angle of attack.
-The instantaneous value of $C_y$ is therefore determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various $\theta$.
+In the QSS model, it is assumed that the force on the body at a given instantaneous incident angle $\theta$ (defined in figure \ref{fig:setup_1}) is the same as the mean force on a static body at the same incident angle, or angle of attack.
+The instantaneous value of $C_y$ is therefore determined by an interpolating polynomial based on the lift data for flow over a stationary body at various $\theta$.
 Using the relationship between $\theta$ and the instantaneous transverse velocity of the body $\dot{y}$ shown in figure \ref{fig:setup_1}, $C_y$ can be written as a function of $\dot{y}$.
@@
 \label{final_equation_motion}
-(m{+}m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
+m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
 \end{equation}
 
-This equation could be solved using standard time integration methods.
+This equation can be solved using standard time integration methods.
 In this study the fourth-order Runge-Kutta scheme built in to the MATLAB routine `ode45' was generally used to obtain the solutions.
@@
 
-For the low \reynoldsnumber\ tests, \reynoldsnumber=165 was maintained as it was pointed out by \citet{Sheard2009} and \citet{Tong2008} that the three-dimensional transition for a square cylinder occurs at approximately \reynoldsnumber=160.
+For the low \reynoldsnumber\ tests, $\reynoldsnumber=165$ was maintained as it was pointed out by \citet{Sheard2009} and \citet{Tong2008} that the three-dimensional transition for a square cylinder occurs at approximately \reynoldsnumber=160.
 $F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \citet{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.
@@
 Stationary $C_y$ data were obtained at different angles of attack ranging from $0^\circ$ to $16^\circ$.
-The average power was obtained by using Eq.\eqref{power}, and the averaging was done over no less than 20 galloping periods.
-Predictions of power output at \reynoldsnumber=22300 were obtained using the coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \citet{Parkinson1964}, in order to provide a comparison between high and low Reynolds numbers.
-The mass ration $m^*$ was kept at 1163 for \reynoldsnumber=22300 (Similar as \citet{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
+The average power was obtained by using equation \ref{power}, and the averaging was done over no less than 20 galloping periods.
+Predictions of power output at $\reynoldsnumber=22300$ were obtained using the coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \citet{Parkinson1964}, in order to provide a comparison between high and low Reynolds numbers.
+The mass ratio $m^*$ was kept at 1163 for $\reynoldsnumber=22300$ (Similar to \citet{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
 These parameters were used throughout this study unless otherwise specified.
@@
 A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution.
-The details of the method can be found in \cite{Thompson2006,Thompson1996a}.
+The details of the method can be found in \citet{Thompson2006,Thompson1996a}.
 This code has been very well validated in a variety of fluid-structure interaction problems \citep{Leontini2007a,Griffith2011,Leontini2011,Leontini2013}.
 
- The computational domain consists of 690 quadrilateral macro elements where majority of the elements were concentrated near the square section.
+The computational domain consists of 690 quadrilateral macro elements where the majority of the elements were concentrated near the square section.
 A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet.
-A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and \reynoldsnumber=$165$.
+A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and $\reynoldsnumber=165$.
 A $9^{th}$ order polynomial together with a time step of $\Delta tU/D=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.

### 2013-12-16 research/paper/figure/m_star_collapsed.tex
Committing what I think is my last bit before submission. Kasun still needs to fix some stuff up, there are notes in the document to him

@@
   \setlength{\unitlength}{\textwidth}
-
   \begin{picture}(1,0.3)(0.0,0.45)
-
     \put(0.025,0.5){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/mean_power_collapsed_mstar.eps}}
@@
 
-        \put(0.23,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$} 	
-        \put(0.73,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$}
+    % \put(0.23,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$} 	
+    % \put(0.73,0.48){$\displaystyle\frac{c}{\rho\mathcal{A}U}$}
+
+    \put(0.28,0.48){\massdamp} 	
+    \put(0.78,0.48){\massdamp}
 
@@
   \caption{Mean power as a function of damping factor.
-Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 (a) with and (b) without the shedding term in Eq.\ref{final_equation_motion}.
+Data are presented at $m^*=10$ (\ding{108}), $m^*=20$ (\ding{83}), $m^*=40$ (\ding{115}), $m^*=60$ (+) at Re 165 (a) with and (b) without the shedding term in equation \ref{final_equation_motion}.
 A reduction of maximum mean power can be observed when $m^*<40$ with shedding while the maximum power is essentially independent of $m^*$ when shedding is disregarded.}

### 2013-12-16 research/paper/nomenclature.tex
Committing what I think is my last bit before submission. Kasun still needs to fix some stuff up, there are notes in the document to him

--- 2013-11-21 research/paper/nomenclature.tex
@@
 $a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
-$C_y$ & instantaneous force coefficient normal to the induced velocity \\
-$F_y$ & force due to $C_y$  \\ 
-$\rho$ & fluid density  \\
+$A$ & displacement amplitude\\
+$c$ & damping constant \\
+$D$ & characteristic length (side length) of the cross section of the body \\
+$f=\sqrt{k/m}/2\pi$ & natural frequency of the system \\
+$F_y$ & instantaneous force normal to the flow \\ 
+$F_0$& amplitude of the oscillatory force due to vortex shedding \\
+$k$ & spring constant \\
 $m$ & mass of the body \\
 $m_a$ & added mass \\
-$c$ & damping constant/damping factor \\
-$k$ & spring constant \\
-$U_i$ & induced velocity \\
-$\theta$ & induced angle of incidence \\
+$P_d$ & power dissipated due to mechanical damping  \\
+$P_{mean}$ & mean power \\
+$P_t$   & power transferred to the body by the fluid \\
+$t$ & time \\
 $U$ & freestream velocity \\
-$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration   \\
-$A$ & displacement amplitude\\
-$\mathcal{A}$ & cross sectional area\\ 
-$F_0$& amplitude of the oscillatory force due to shedding \\
-$\omega_s$& vortex shedding frequency \\
-$t$ & time \\
-$P_{mean}$& mean power \\
-$f=\frac{1}{2\pi}\sqrt{\frac{k}{m}}$& natural frequency of the system \\
-$\omega_n= 2 \pi f$& natural frequency of the system  \\
-$D$ & characteristic length of the body  \\
-$m^*=\frac{m}{\rho \times \text{Volume of the body}}$& mass ratio \\
-$U^*=\frac{U}{f \times D}$& reduced velocity  \\
-$\zeta= \frac{c}{2 m \omega_n}$& damping ratio \\
-$P_t$   & power transferred to the body by the fluid \\
-$P_d$& power dissipated due to mechanical damping  \\
-$Re$& Reynolds number  \\
-$\theta= \tan^{-1}{(\frac{\dot{y}}{U})}$& instantaneous angle \\
-& \\
-& \\
+$U_i$ & Induced velocity \\
+$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration of the body \\
+$\mathcal{A}=DL$ & frontal area of the body\\ 
+$\rho$ & fluid density  \\
+$\omega_n= 2 \pi f$ & natural angular frequency of the system  \\
+$\omega_s$ & vortex shedding angular frequency \\
+$\cstar=cD/mU$ & non-dimensionalised damping factor \\
+$C_y=F_y/0.5\rho U^2DL$ & normal (lift) force coefficient \\
+$m^*=m/\rho D^2L$ & mass ratio \\
+$Re$ & Reynolds number  \\
+$U^*=U/fD$ & reduced velocity  \\
+$Y=y/D$ & non-dimensional transverse displacement \\
+$\dot{Y}=m^*\dot{y}/a_1U$ & non-dimensional transverse velocity \\
+$\ddot{Y}=m^{*2}D/a_1^2U^2$ & non-dimensional transverse acceleration \\
+$\Gamma_1 = 4\pi^2m^{*2}/U^{*2}a_1^2$ & First dimensionless group arising from linearised, non-dimensionalised equation of motion\\
+$\Gamma_2 = c^*m^*/a_1$ & Second dimensionless group arising from linearised, non-dimensionalised equation of motion\\
+$\zeta= c/2 m \omega_n$ & damping ratio \\
+$\theta= \tan^{-1}{(\dot{y}/U)}$ & instantaneous angle of incidence (angle of attack)\\
+$\massstiff =  4\pi^2m^{*2}/U^{*2}$ & Combined mass-stiffness parameter\\
+$\massdamp = c^*m^*$ & Combined mass-damping parameter\\
 \end{tabular}

### 2013-12-16 research/paper/results/results-2.3.tex
Committing a single sentence explaining our new parameter is the same as Parkinson's
Committing what I think is my last bit before submission. Kasun still needs to fix some stuff up, there are notes in the document to him

@@
 Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating body, as demonstrated by equation \ref{power_alt}.
-Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; form body to fluid.
+Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; from body to fluid.
 Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=165$ compared to $\reynoldsnumber=22300$, it is expected that power output at $\reynoldsnumber=165$ is significantly lower than at $\reynoldsnumber=22300$.
@@
 
-The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3\frac{D}{2}$, the kinetic energy in the fluid approaching the body.
+The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3D/2$, the kinetic energy in the fluid approaching the body.
 A similar definition was given in \citet{Barrero-Gil2010a}).
@@
 
-\JL{KASUN: I don't understand the above paragraph.
-What is the main point of this paragraph?
-Are you trying to show that the only the terms dependent on $\dot{y}$ are dissipative, and so only those terms contribute to the transfer of energy or power to the body?
-That is true, but that is also true for VIV, so I don't see how that shows that the ``system is governed by the transverse velocity rather than the natural frequency''.
-I definitely don't understand that last sentence.
-Do you mean ``power'' when you say ``system''?
-The problem is that, as I've pointed out, the exact same argument regarding dissipation applies to VIV, which is strongly dependent on the natural frequency.}
-
 The data presented in figure \ref{fig:uncollapsed_data} show that, regardless of the damping ratio $\zeta$, the trend of the response with $U^*$ is similar, suggesting the data can be collapsed by a suitable choice of parameters.
@@
 \label{eqn:eom_linear}
-(m{+}m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
+m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
 \end{equation}
@@
 
-In this form, $\lambda$ represents the inverse time scale of the of the motion of the body due to the negative damping effect of the long-time aerodynamic forces.
+In this form, $\lambda$ represents the inverse time scale of the motion of the body due to the negative damping effect of the long-time aerodynamic forces.
 In fact, the terms can be regrouped and $\lambda$ written as
@@
 Written this way, the important parameters that dictate this inverse time scale are clear.
-The rate of change in the aerodynamic force with respect to angle of attackwhen the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$.
+The rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$.
 The mass ratio is represented by $m^*$.
@@
 Increasing $a_1$ would mean the force on the body would increase more rapidly with small changes in the angle of attack, $\theta$, or transverse velocity.
-Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously dcrease the response time of the body.
+Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously decrease the response time of the body.
 Increasing the mass of the body, thereby increasing $m^*$, has the opposite effect.
@@
   \label{eqn:eom_nondim}
-  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} \dots,
+  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} + H.O.T.,
 \end{equation}
 
-where the coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
+where $H.O.T.$ respresents the higher order terms in $\dot{Y}$. The coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
 \begin{equation}
   \label{eqn:eom_nondim_regroup}
-  \ddot{Y} + \frac{k^{*2}m^{*2}}{a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} \dots,
+  \ddot{Y} + \frac{4\pi^{2}m^{*2}}{U^{*2}a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} + H.O.T,
 \end{equation}
 
-where $k^*=kD^2/mU^2$ is a non-dimensional stiffness parameter, and $c^*=cD/mU$ is a non-dimensional damping parameter.
+where $c^*=cD/mU$ is a non-dimensional damping parameter.
 
 Equation \ref{eqn:eom_nondim_regroup} shows there are four non-dimensional parameters that play a role in setting the response of the system.
-These are the stiffness $k^*$, the damping $c^*$, the mass ratio $m^*$, and the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$.
-The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = k^{*2}m^{*2}/a_1^2$ and $\Gamma_2 = c^*m^*/a_1$.
-For a given geometry and Reynolds number, $Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter.
+These are the stiffness (represented by the reduced velocity $U^*$), the damping $c^*$, the mass ratio $m^*$, and the geometry, represented by the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$.
+The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = 4\pi^2m^{*2}/U^{*2}a_1^2$ and $\Gamma_2 = c^*m^*/a_1$.
+For a given geometry and Reynolds number, $\Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter.
 As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.
+In fact, in the classic paper on galloping from \citet{Parkinson1964}, galloping data from wind tunnel tests is presented in terms of a parameter that can be shown to be the same as $\Gamma_2$.
 
-Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter $\Gamma_2$.
+All of the quantities that make up $\Gamma_1$ and $\Gamma_2$ can, in theory, be known before an experiments is conducted.
+However, the quantity $a_1$ is a relatively difficult one to determine, requiring static body experiments or simulations.
+Here, the geometry is unchanged and results are only being compared at the same \reynoldsnumber.
+Hence, suitable parameters can be formed by multiplying $\Gamma_1$ and $\Gamma_2$ by $a_1^2$ and $a_1$ respectively, to arrive at a mass-stiffness parameter $\massstiff =  4\pi^2m^{*2}/U^{*2}$, and a mass-damping parameter defined as $\massdamp = c^*m^*$.
+
+Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter \massdamp.
 The collapse, especially of the velocity amplitude and power output data, is excellent.
-This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, $\Gamma_2$, is kept fixed.
-An example of this is shown in Fig.\ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\Gamma_2=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted.
+This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, \massdamp, is kept fixed.
+An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted.
 The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
@@
 Power can be expressed as the product of force and velocity.
-Therefore the transferred power fromm the fluid to the body can be expressed as $P_t=F_y\dot{y}$, as shown in equation \ref{power_alt}.
-Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$ as shown in equation \ref{power}.
-The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction losses are neglected.
+Therefore the instantaneous power from the fluid to the body can be expressed as $P_t=F_y\dot{y}$.
+Similarly the dissipated power due to the mechanical damping can be expressed as $P_d=(c\dot{y})\dot{y}$.
+The time average of these two quantities, described in equations \ref{power_alt} and \ref{power} should be equal due to energy conservation, provided that the mechanical friction losses are neglected.
 The mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased.
@@
 
-\JL{KASUN: why have you established that it is the damping, not $U^*$, that is important, but here you persist with presenting results in terms of $U^*$?
-How do these regions correspond to regions on the curve in terms of your damping parameter (that I have labelled $\Gamma_2$)?
-Can you define these three regions in terms of this new parameter?}
-
-It has been established earlier that the damping factor is a function of $U^*$.
-Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient.
-Hence the damping coefficient reduces when you move from region 1 to 3.
-Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls and at around $6^\circ$ becomes negative.
-The maximum amount of power that could be transferred occurs near the peak region.
+The non-dimensional damping, $c^*$, can be shown to be inversely proportional to $U^*$.
+Hence the damping parameter, and the mas-damping \massdamp, reduces when moving from region 1 to 3.
+Figure \ref{fig:lift_curves}(a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls, and at around $6^\circ$ becomes negative.
+The maximum amount of power that can be transferred occurs when $\dot{y}$ is such that $\theta$ is near the peak region.
 At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$.
-Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.
-
-\JL{KASUN: I don't understand the point of the above paragraph. What are you trying to say? That maximum power output occurs when the tranverse velocity is such that the lift force is a maximum?}
+Data at $\zeta=0.1$, $m^*=40$ and $\reynoldsnumber=165$ are shown in figure \ref{fig:power_time_histories} and are analysed as an example.
 
@@
 \end{figure}
+
+\JL{KASUN: remember to also include the value of the mass-damping as well as $U^*$ in the following paragraphs. I have set things up so that \massdamp\ is the same as your original parameter}
 
@@
 
-The mean power at different $m^*$ is presented as a function of the mass-damping parameter $\Gamma_2$ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case.
+The mean power at different $m^*$ is presented as a function of the mass-damping parameter \massdamp\ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case.
 For $m^*>30$, the power output is essentially independent of $m^*$, while at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range.
@@
 
-At $\reynoldsnumber=22300$ power output started to increase for cases with $m^*<50$.
+At $\reynoldsnumber=22300$ power output increases with decreasing $m^*$ for cases with $m^*<50$.
 The overall mean power tend to increase as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)).
@@
 It should be noted that the influence of $U^*$ was observed only for low mass ratios.
-The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave.
-The corresponding displacement signal tend to become more like a triangular wave.
+This is perhaps not surprising, as the definition of $\massstiff$ shows that this mass-stiffness parameter goes quickly to zero as $U^*$ grows, but that it will be of comparable order to the mass-damping \massdamp\ when $U^*$ approaches unity.
+Therefore, the influence of this second parameter \massstiff\ cannot be ignored for cases where $U^*$ is low.
+
+The velocity time traces of example cases of both scenarios presented in figure \ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} show that essentially the same phenomenon occurs in both cases whereby the velocity signal tends to shift from a sinusoidal signal towards a square wave.
+The corresponding displacement signal tends to become more like a triangular wave.
 When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity.
-Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping.
-However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.
-Physical systems may not realize the full potential due to practical limitations.
-Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output.
-For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.
-
-\JL{KASUN, again this last paragraph is all in terms of $U^*$, but you establish earlier that $U*^$ is not the important parameter, your new damping parameter (which is actually a mass-damping parameter) is the critical parameter.
-Can this argument be rewritten in terms of this new parameter?}
+Higher velocities are favourable because they result in higher hydrodynamic forcing and power output from mechanical damping.
+However, the velocity is limited by the characteristics of the hydrodynamic forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which corresponds to a transverse velocity of $\dot{y}/U=0.235$.
+It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\massdamp=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.
 
@@
 In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration.
-At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ .
+At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised mass-damping constant \massdamp .
 By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant.
@@
 For this higher \reynoldsnumber\ case, When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
-The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$.
+The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\massdamp=1.22$ by analysing the data trend by lowering the $m^*$.
 

### 2013-12-17 research/paper/figure/velocity_compare.tex
corrected some stuff uploaded 11.01 PM Malaysia

@@
     % % %90
-    \put(0.025,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_60_0.075.eps}}
-    \put(0.495,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_165_0.175.eps}}
+    \put(0.025,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_65_0.075.eps}}
+    \put(0.495,0.83){\includegraphics[width=0.5\unitlength]{../FnP/gnuplot/vel_time_history_150_0.175.eps}}
 
@@
 
-  \caption{Time histories of velocity at two different $\zeta$ and $U^*$ which produce the same mean power ($1.2\times10^{-3}$).
-Data presented in (a) are at $\ustar=60$, $\zeta=0.075$ and (b) are at $\ustar=165$, $\zeta=0.175$.
+  \caption{Time histories of velocity at two different $\zeta$ and $U^*$ at $m^*=20$ which produce the same mean power ($1.2\times10^{-3}$).
+Data presented in (a) are at $\ustar=65$, $\zeta=0.075$ and (b) are at $\ustar=150$, $\zeta=0.175$.
 Both data sets were obtained using Quasi-steady state assumption using input $C_y$ parameters at $Re=165$.

### 2013-12-17 research/paper/results/results-2.3.tex
corrected some stuff uploaded 11.01 PM Malaysia

@@
 This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, \massdamp, is kept fixed.
-An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted.
+An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=0.3$, are plotted.
 The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.
@@
 
-\JL{KASUN: remember to also include the value of the mass-damping as well as $U^*$ in the following paragraphs. I have set things up so that \massdamp\ is the same as your original parameter}
-
-At region 1 where $U^*=90$ the damping constant is high and a clear sinusoidal signal is observed for both $P_d$ and $P_t$ in figure \ref{fig:power_time_histories}(a).
+At region 1 where $U^*=90$, $\massdamp=0.56$ the damping constant is high and a clear sinusoidal signal is observed for both $P_d$ and $P_t$ in figure \ref{fig:power_time_histories}(a).
 Figures \ref{fig:power_time_histories}(d) and  \ref{fig:power_time_histories}(g) show that equivalent incident angle $\theta$ (which for small values, is proportional to the transverse velocity of the body) is in phase with $F_y$.
@@
 
-At region 3 ($U^*= 400$) the damping is low in comparison with region 1 and 2.
+At region 3 ($U^*= 400$, $\massdamp=0.13$) the damping is low in comparison with region 1 and 2.
 While this may lead to larger oscillations, damping is required to dissipate power according to equation \ref{power}.
@@
 
-At region 2 ($U^*=165$), a balance is found between high and low values of damping.
+At region 2 ($U^*=165$, $\massdamp=0.3$), a balance is found between high and low values of damping.
 $P_t$ is not a pure sinusoidal signal, however the signal remains periodic.
@@
 The damping is high enough to obtain a high power output while not too high to allow the induced angle of attack to enter the region where the forcing opposes the direction of travel.
-
-\JL{KASUN: nothing to change here, just wanted to note that this paragraph is good. Clear, and to the point.}
 

### 2013-12-19 research/paper/results/results-2.3.tex
Committing what I think is my final edit before submission. Kasun needs to check over references

@@
 
-The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3D/2$, the kinetic energy in the fluid approaching the body.
+The efficiency of the system can be defined as the ratio of the time average power output to $P_{in}=\rho U^3D/2$, the kinetic energy in the fluid approaching the body.
 A similar definition was given in \citet{Barrero-Gil2010a}).
@@
 \label{eqn:eom_linear}
-m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
+(m+m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
 \end{equation}
@@
   \label{eqn:eigs}
-  \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}\right]^2-4\frac{k}{m}}.
+  \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{(m+m_a)U}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{(m+m_a)U}\right]^2-4\frac{k}{(m+m_a)}}.
 \end{equation}
@@
   \label{eqn:eigs_nospring}
-  \lambda=-\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{mU}.
+  \lambda=-\frac{c-\frac{1}{2}\rho U^2\mathcal{A}a_1}{(m+m_a)U}.
 \end{equation}
@@
 Further, if it is assumed that the mechanical damping is significantly weaker than the aerodynamic forces on the body, $c\rightarrow 0$ and
+\begin{equation}
+  \label{eqn:eigs_nospring_nodamp}
+  \lambda=\frac{\frac{1}{2}\rho U^2\mathcal{A}a_1}{(m+m_a)U}.
+\end{equation}
+
+For reasonably heavy bodies, the impact of the added mass can also be neglected, to arrive at a definition of $\lambda$ as
 \begin{equation}
@@
 
-All of the quantities that make up $\Gamma_1$ and $\Gamma_2$ can, in theory, be known before an experiments is conducted.
+All of the quantities that make up $\Gamma_1$ and $\Gamma_2$ can, in theory, be known before an experiment is conducted.
 However, the quantity $a_1$ is a relatively difficult one to determine, requiring static body experiments or simulations.
@@
 Similarly the dissipated power due to the mechanical damping can be expressed as $P_d=(c\dot{y})\dot{y}$.
-The time average of these two quantities, described in equations \ref{power_alt} and \ref{power} should be equal due to energy conservation, provided that the mechanical friction losses are neglected.
+The time average of these two quantities, described in equations \ref{power} and \ref{power_alt} should be equal due to energy conservation, provided that the mechanical friction losses are neglected.
 The mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased.
@@
 It was reported by \cite{Barrero-Gil2009} that galloping only starts to occur ar Re $\geq 159$.
-It may be that simulations conducted so close to the threshold for the onset of galloping are very sensitive to errors due to blockage or under-resolution, both of which can change the effective \reynoldsnumber of the flow.
+It may be that simulations conducted so close to the threshold for the onset of galloping are very sensitive to errors due to blockage or under-resolution, both of which can change the effective \reynoldsnumber\ of the flow.
 Small changes in effective \reynoldsnumber\ can have a significant impact of the fluid damping, and therefore on the amplitude and transverse velocity of the body.
@@
 In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration.
-At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised mass-damping constant \massdamp .
+At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber\ and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised mass-damping constant \massdamp .
 By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant.

### 2014-05-12 research/paper/main/article.tex
revision file added

--- 2013-12-16 research/paper/Theory/mathematical_model.tex
@@
+\section{Introduction}
+
+Fluid-elastic galloping is one of the sub-areas of research in fluid structure interactions.
+This area has been of interest due to the vibrations crated by galloping on transmission lines and civil structures and leading them to failure.
+Therefore understanding this phenomenon in order to suppresses these vibrations was quite important.
+However, the search for alternate energy sources with minimal environmental impact has become an important area of research in the modern word.
+Therefore researchers are moving towards investigating the possibility of extracting useful energy from this vibrations rather than suppressing them.
+Therefore, it is quite important to understand the governing parameters and analyse the influence of them on the energy transfer from the fluid to the body, because this understanding will lead to develop better practical applications.
+Therefore, in this paper we focus on understanding the energy transfer from the fluid to the body and isolate the governing parameters influencing it.
+
+According to \citet{Paidoussis2010}, \citet{Glauert1919} provided a criterion for galloping by considering the auto-rotation of an aerofoil.
+\citet{DenHartog1956} provided a theoretical explanation for galloping for iced electric transmission lines.
+A weakly non-linear theoretical aeroelastic model to predict the response of galloping was developed by \citet{Parkinson1964} based on the quasi-steady state hypothesis.
+Experimental lift and drag data on a fixed square prism at different angles of attack were used as an input for the theoretical model.
+It essentially used a curve fit of the transverse force to predict the galloping response.
+The study managed to achieve a good agreement with experimental data.
+
+However, the QSS model equation when solved analytically using the sinusoidal solution method cannot predict the response for cases with low mass ratios.
+\citet{Joly2012} observed that finite element simulations show a sudden change in amplitude below a critical value of the mass ratio.
+The model equation defined in \citet{Parkinson1964} was modified to account for the vortex shedding and solved numerically to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
+\citet{Barrero-Gil2010a} investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
+In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low.
+The same study investigated the influence of the characteristics of the $C_y$ curve on maximum power output.
+
+Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically for low Reynolds numbers.
+The focus is on the power extraction potential as a function of mechanical parameters (i.e.
+frequency of oscillation, damping factor and mass ratio).
+To this end, a series of previously mentioned mechanical parameters are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 165$, a case that should remain laminar and essentially two-dimensional; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
+Both cases require the input of transverse force coefficients $C_y$ as a function of angle of attack $\theta$ for a fixed body.
+These data are provided from direct numerical simulations for the $\reynoldsnumber = 165$ case, while the data provided by \citet{Parkinson1964} are used for the $\reynoldsnumber = 22300$ case.
+
+The structure of the paper is as follows.
+Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used.
+Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber\ cases.
+For the low \reynoldsnumber\ case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem.
+Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+\section*{Nomenclature}
+%\textbf{Nomenclature}
+
+\begin{tabular}{ll}
+$a_1,a_3,a_5,a_7$ & coefficients of the polynomial to determine $C_y$ \\ 
+$A$ & displacement amplitude\\
+$c$ & damping constant \\
+$D$ & characteristic length (side length) of the cross section of the body \\
+$f=\sqrt{k/m}/2\pi$ & natural frequency of the system \\
+$F_y$ & instantaneous force normal to the flow \\ 
+$F_0$& amplitude of the oscillatory force due to vortex shedding \\
+$k$ & spring constant \\
+$m$ & mass of the body \\
+$m_a$ & added mass \\
+$P_d$ & power dissipated due to mechanical damping  \\
+$P_{in}=\rho U^3D/2$ & Energy flux of the approaching flow \\
+$P_{mean}$ & mean power \\
+$P_t$   & power transferred to the body by the fluid \\
+$t$ & time \\
+$U$ & freestream velocity \\
+$U_i$ & Induced velocity \\
+$y,\dot{y},\ddot{y}$ & transverse displacement, velocity and acceleration of the body \\
+$\mathcal{A}=DL$ & frontal area of the body\\ 
+$\lambda$ & Inverse time scale of a galloping dominated flow \\
+$\lambda_{1,2}$ & Eigenvalues of linearized equation of motion \\
+$\rho$ & fluid density  \\
+$\omega_n= 2 \pi f$ & natural angular frequency of the system  \\
+$\omega_s$ & vortex shedding angular frequency \\
+$\cstar=cD/mU$ & non-dimensionalised damping factor \\
+$C_y=F_y/0.5\rho U^2DL$ & normal (lift) force coefficient \\
+$m^*=m/\rho D^2L$ & mass ratio \\
+$Re$ & Reynolds number  \\
+$U^*=U/fD$ & reduced velocity  \\
+$Y=y/D$ & non-dimensional transverse displacement \\
+$\dot{Y}=m^*\dot{y}/a_1U$ & non-dimensional transverse velocity \\
+$\ddot{Y}=m^{*2}D/a_1^2U^2$ & non-dimensional transverse acceleration \\
+$\Gamma_1 = 4\pi^2m^{*2}/U^{*2}a_1^2$ & First dimensionless group arising from linearised, non-dimensionalised equation of motion\\
+$\Gamma_2 = c^*m^*/a_1$ & Second dimensionless group arising from linearised, non-dimensionalised equation of motion\\
+$\zeta= c/2 m \omega_n$ & damping ratio \\
+$\theta= \tan^{-1}{(\dot{y}/U)}$ & instantaneous angle of incidence (angle of attack)\\
+$\massstiff =  4\pi^2m^{*2}/U^{*2}$ & Combined mass-stiffness parameter\\
+$\massdamp = c^*m^*$ & Combined mass-damping parameter\\
+\end{tabular}
+
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
 \section{Problem formulation and methodology}
@@
 
-The base quasi-steady state (QSS) model was first developed by \citet{Parkinson1964} for a square cross section. The equation of motion of the body is given by 
+The equation of motion of the body is given by 
 \begin{equation}
 \label{equationofmotion}
-m\ddot{y}+c\dot{y}+ky=F_y,
+(m+m_a)\ddot{y}+c\dot{y}+ky=F_y,
 \end{equation}
@@
 Thus a $7 ^{th}$ order interpolating polynomial is used in this present study.
-As a result, $C_y(\dot{y})$ is defined as
+As a result, $C_y(\theta)$ (noting that theta is proportional to $\dot{y}/U$) is defined as
 \begin{equation}

### 2014-05-13 research/paper/main/article.tex
modifications 2.28 13 may

@@
 Therefore researchers are moving towards investigating the possibility of extracting useful energy from this vibrations rather than suppressing them.
-Therefore, it is quite important to understand the governing parameters and analyse the influence of them on the energy transfer from the fluid to the body, because this understanding will lead to develop better practical applications.
-Therefore, in this paper we focus on understanding the energy transfer from the fluid to the body and isolate the governing parameters influencing it.
+Thus, it is quite important to understand the governing parameters and analyse the influence of them on the energy transfer from the fluid to the structure, because this understanding will lead to develop better practical applications.
+Hence, in this paper we focus on understanding the energy transfer from the fluid to the body and isolate the governing parameters influencing it.
 
@@
 \citet{Joly2012} observed that finite element simulations show a sudden change in amplitude below a critical value of the mass ratio.
-The model equation defined in \citet{Parkinson1964} was modified to account for the vortex shedding and solved numerically to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
+The quasi-oscillator equation in \citet{Parkinson1964} was altered to account for the vortex shedding and solved numerically to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
 \citet{Barrero-Gil2010a} investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
@@
 Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically for low Reynolds numbers.
-The focus is on the power extraction potential as a function of mechanical parameters (i.e.
+The focus is on the power transfer from the fluid to the structure and the influence of mechanical parameters (i.e.
 frequency of oscillation, damping factor and mass ratio).
@@
 The structure of the paper is as follows.
-Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used.
+Section \ref{sec:theory} presents the governing equations and the oscillator model used to obtain data, the method for the calculation of the power transferred from the fluid to the structure.
+The governing parameters namely, the combined mass-stiffness and the combined mass-damping obtained using linearised time scales of the oscillator model are also being introduced.
 Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber\ cases.
@@
 
+ % % % % % % % % % % % % % Time scales % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+ The natural time scales of the system can be found by solving for the eigenvalues of the linearized equation of motion, namely
+ \begin{equation}
+ \label{eqn:eom_linear}
+ (m+m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
+ \end{equation}
+ which is simply the equation of motion presented in equation \ref{final_equation_motion} with the polynomial series for the lift force truncated at the linear term, and the forcing term representing vortex shedding removed.
+
+ Combining the $\dot{y}$ terms and solving for eigenvalues gives
+ \begin{equation}
+   \label{eqn:eigs}
+   \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}\right]^2-4\frac{k}{(m+m_a)}}.
+ \end{equation}
+
+ If it is assumed that the spring is relatively weak, $k\rightarrow 0$, a single non-zero eigenvalue remains. This eigenvalue is
+ \begin{equation}
+   \label{eqn:eigs_nospring}
+   \lambda=-\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}.
+ \end{equation}
+
+ Further, if it is assumed that the mechanical damping is significantly weaker than the aerodynamic forces on the body, $c\rightarrow 0$ and
+ \begin{equation}
+   \label{eqn:eigs_nospring_nodamp}
+   \lambda=\frac{\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}.
+ \end{equation}
+
+ For reasonably heavy bodies, the impact of the added mass can also be neglected, to arrive at a definition of $\lambda$ as
+ \begin{equation}
+   \label{eqn:eigs_nospring_nodamp}
+   \lambda=\frac{\frac{1}{2}\rho U\mathcal{A}a_1}{m}.
+ \end{equation}
+
+ In this form, $\lambda$ represents the inverse time scale of the motion of the body due to the negative damping effect of the long-time aerodynamic forces.
+In fact, the terms can be regrouped and $\lambda$ written as
+ \begin{equation}
+   \label{eqn:timescale}
+   \lambda = \frac{a_1}{m^*}\frac{U}{D}
+ \end{equation}
+
+ Written this way, the important parameters that dictate this inverse time scale are clear.
+The rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$.
+The mass ratio is represented by $m^*$.
+The inverse advective time scale of the incoming flow is represented by the ratio $U/D$.
+Increasing $a_1$ would mean the force on the body would increase more rapidly with small changes in the angle of attack, $\theta$, or transverse velocity.
+Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously decrease the response time of the body.
+Increasing the mass of the body, thereby increasing $m^*$, has the opposite effect.
+The inverse time scale is decreased, or as might be expected, a heavier body will take longer to respond.
+
+ This timescale can then be used to non-dimensionalize the equation of motion, and to find the relevant dimensionless groups of the problem.
+If the non-dimensional time, $\tau$, is defined such that $\tau=t(a_1/m^*)(U/D)$, the equation of motion presented in equation \ref{final_equation_motion} can be non-dimensionalized as
+ \begin{equation}
+   \label{eqn:eom_nondim}
+   \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} + H.O.T.,
+ \end{equation}
+
+ where $H.O.T.$ respresents the higher order terms in $\dot{Y}$. The coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
+ \begin{equation}
+   \label{eqn:eom_nondim_regroup}
+   \ddot{Y} + \frac{4\pi^{2}m^{*2}}{U^{*2}a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} + H.O.T,
+ \end{equation}
+
+ where $c^*=cD/mU$ is a non-dimensional damping parameter.
+
+ Equation \ref{eqn:eom_nondim_regroup} shows there are four non-dimensional parameters that play a role in setting the response of the system.
+These are the stiffness (represented by the reduced velocity $U^*$), the damping $c^*$, the mass ratio $m^*$, and the geometry, represented by the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$.
+The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = 4\pi^2m^{*2}/U^{*2}a_1^2$ and $\Gamma_2 = c^*m^*/a_1$.
+For a given geometry and Reynolds number, $\Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter.
+As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.
+In fact, in the classic paper on galloping from \citet{Parkinson1964}, galloping data from wind tunnel tests is presented in terms of a parameter that can be shown to be the same as $\Gamma_2$.
+
+ All of the quantities that make up $\Gamma_1$ and $\Gamma_2$ can, in theory, be known before an experiment is conducted.
+However, the quantity $a_1$ is a relatively difficult one to determine, requiring static body experiments or simulations.
+Here, the geometry is unchanged and results are only being compared at the same \reynoldsnumber.
+Hence, suitable parameters can be formed by multiplying $\Gamma_1$ and $\Gamma_2$ by $a_1^2$ and $a_1$ respectively, to arrive at a mass-stiffness parameter $\massstiff =  4\pi^2m^{*2}/U^{*2}$, and a mass-damping parameter defined as $\massdamp = c^*m^*$.
+
 \subsection{Parameters used}

### 2014-05-14 research/paper/main/article.tex
update 6.19 13th may

@@
 
-\subsection{Parameters used}
+ % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+ \section{Results}
+ \label{sec:results}
 
-For the low \reynoldsnumber\ tests, $\reynoldsnumber=165$ was maintained as it was pointed out by \citet{Sheard2009} and \citet{Tong2008} that the three-dimensional transition for a square cylinder occurs at approximately \reynoldsnumber=160.
-$F_0$ was kept at $0.4937$ which was obtained by scaling the value used by \citet{Joly2012} with the amplitude ratios of the lift forces obtained at the different Reynolds numbers.
+ \input{../figure/uncollapsed_data}
+ \input{../figure/collapsed_data}
 
-The angular vortex shedding frequency $\omega_s$, was set to $0.98$ which was obtained by performing a power spectral analysis of the stationary data at $0^\circ$.
-Stationary $C_y$ data were obtained at different angles of attack ranging from $0^\circ$ to $16^\circ$.
-The average power was obtained by using equation \ref{power}, and the averaging was done over no less than 20 galloping periods.
-Predictions of power output at $\reynoldsnumber=22300$ were obtained using the coefficients for curve fitting $C_y$ (Table (\ref{table:cy-coefficients})) from \citet{Parkinson1964}, in order to provide a comparison between high and low Reynolds numbers.
-The mass ratio $m^*$ was kept at 1163 for $\reynoldsnumber=22300$ (Similar to \citet{Parkinson1964}) and $m^*=20$ for \reynoldsnumber=165.
-These parameters were used throughout this study unless otherwise specified.
-
-The stationary data and the fluid-structure interaction (FSI) data were obtained using a high-order spectral element routine to simulate the two-dimensional laminar flow.
-Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model.
-The inlet was placed $20D$ while the outlet situated $60D$ away from the centroid of the body.
-The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study.
-The Navier--Stokes equations were solved in an accelerated frame of reference attached to the moving body along with the body equation of motion given in equation \ref{equationofmotion}.
-A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution.
-The details of the method can be found in \citet{Thompson2006,Thompson1996a}.
-This code has been very well validated in a variety of fluid-structure interaction problems \citep{Leontini2007a,Griffith2011,Leontini2011,Leontini2013}.
-
-The computational domain consists of 690 quadrilateral macro elements where the majority of the elements were concentrated near the square section.
-A freestream condition was given to the inlet, top and bottom boundaries and the normal velocity gradient was set to zero at the outlet.
-A convergence study was performed by changing the order of the polynomial ($p$-refinement) at $U^*=40$ and $\reynoldsnumber=165$.
-A $9^{th}$ order polynomial together with a time step of $\Delta tU/D=0.001$ was sufficient to ensure an accuracy of $2\%$ with regards to amplitude of oscillation.
+  \input{../figure/m_star_collapsed}
+  \input{../figure/mstar_parkinson}

### 2014-06-09 research/paper/figure/coefficient-table.tex
upload 9-6-2014

@@
 \\[0.8ex]% inserts single horizontal line
-Re=165 & 1.3 & 125.3 & 1825.73 & 8765.3 \\[0.8ex] % inserting body of the table
+Re=165 & 1.97 & 71.28  & -6937 & -25943  \\[0.8ex] % inserting body of the table
 Re=22300 & 2.69 & 168 & 1670 & 59900 \\ [1ex] % [1ex] adds vertical space

### 2014-06-09 research/paper/main/article.tex
upload 9-6-2014

@@
 
-However, the QSS model equation when solved analytically using the sinusoidal solution method cannot predict the response for cases with low mass ratios.
+However, the QSS model equation when solved analytically using the sinusoidal solution, cannot predict the response for cases with low mass ratios.
 \citet{Joly2012} observed that finite element simulations show a sudden change in amplitude below a critical value of the mass ratio.
-The quasi-oscillator equation in \citet{Parkinson1964} was altered to account for the vortex shedding and solved numerically to predict the reduced amplitude at low mass ratios to the point where galloping is no longer present.
+The quasi-oscillator equation in \citet{Parkinson1964} was altered to account for the vortex shedding and solved numerically to predict the reduced displacement amplitude at low mass ratios to the point where galloping is no longer present.
 \citet{Barrero-Gil2010a} investigated the possibility of extracting power from vibrations caused by galloping using the quasi-steady state model.
-In the conclusions of that paper it was pointed out that in order to obtain a high power to area ratio, the mass-damping ($m^*\zeta$) parameter should be kept low.
-The same study investigated the influence of the characteristics of the $C_y$ curve on maximum power output.
+So far the studies on galloping using quasi-steady state assumption has been mainly focused on understanding the behaviour of the displacement amplitude.
+Although, it is quite important to analyse the behaviour of the velocity when studying the power transfer from the fluid to the body.
+This is because power could be simply defined as the product the force and velocity.
+This study also focuses on how well the QSS model perform at high damping at low Reynolds numbers.
 
 Here, the modified QSS model developed by \citet{Joly2012} is integrated numerically for low Reynolds numbers.
-The focus is on the power transfer from the fluid to the structure and the influence of mechanical parameters (i.e.
-frequency of oscillation, damping factor and mass ratio).
-To this end, a series of previously mentioned mechanical parameters are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 165$, a case that should remain laminar and essentially two-dimensional; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
+The power transfer from the fluid to the structure and the influence of mechanical parameters was investigated (i.e.
+mass, stiffness and damping).
+To this end, a series of previously mentioned mechanical parameters are tested at two different values of \reynoldsnumber: $\reynoldsnumber = 200$, a case that should remain laminar and closer to two-dimensional behaviour; $\reynoldsnumber = 22300$, a case where the flow is expected to be turbulent and three-dimensional.
 Both cases require the input of transverse force coefficients $C_y$ as a function of angle of attack $\theta$ for a fixed body.
-These data are provided from direct numerical simulations for the $\reynoldsnumber = 165$ case, while the data provided by \citet{Parkinson1964} are used for the $\reynoldsnumber = 22300$ case.
+These data are provided from direct numerical simulations for the $\reynoldsnumber = 200$ case, while the data provided by \citet{Parkinson1964} are used for the $\reynoldsnumber = 22300$ case.
 
-The structure of the paper is as follows.
+%The structure of the paper is as follows.
 Section \ref{sec:theory} presents the governing equations and the oscillator model used to obtain data, the method for the calculation of the power transferred from the fluid to the structure.
@@
 \label{equationofmotion}
-(m+m_a)\ddot{y}+c\dot{y}+ky=F_y,
+(m)\ddot{y}+c\dot{y}+ky=F_y,
 \end{equation}
@@
 \end{equation}
-\citet{lighthill1986} showed that for systems oscillating in fluid, it is sometimes useful to decompose the fluid forces into components that are in and out of phase with the body acceleration.
-The component in phase with the acceleration effectively adds to the inertia or effective mass of the system.
-Therefore, an added mass term, $m_a$, can be added to the system mass.
-For consistency with previous studies such as \citet{Joly2012}, a value of $m_a=3.5$ has been used here.
 
@@
 In this study the fourth-order Runge-Kutta scheme built in to the MATLAB routine `ode45' was generally used to obtain the solutions.
-Some low mass ratio cases used a solver modified for stiff problems, built into the `ode15s' routine in MATLAB.
 
@@
 
-These two definitions show two important interpretions of the power with respect to any energy production device.
+These two definitions show two important interpretations of the power with respect to any energy production device.
 The first shows that power will be high for situations where the damping coefficient is high, and the transverse velocity is consistently high.
@@
 
+ \subsection{Validation}
+ \label{ubsec:validation}
+
  % % % % % % % % % % % % % Time scales % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
- The natural time scales of the system can be found by solving for the eigenvalues of the linearized equation of motion, namely
+
+ \section{Results}
+  \label{sec:results}
+
+  The natural time scales of the system can be found by solving for the eigenvalues of the linearised equation of motion, namely
  \begin{equation}
  \label{eqn:eom_linear}
- (m+m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
+ (m)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
  \end{equation}
@@
    \label{eqn:eigs}
-   \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}\right]^2-4\frac{k}{(m+m_a)}}.
+   \lambda_{1,2}= -\frac{1}{2}\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m)}\pm\frac{1}{2}\sqrt{\left[\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m)}\right]^2-4\frac{k}{(m+m_a)}}.
  \end{equation}
@@
    \label{eqn:eigs_nospring}
-   \lambda=-\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}.
+   \lambda=-\frac{c-\frac{1}{2}\rho U\mathcal{A}a_1}{(m)}.
  \end{equation}
@@
    \label{eqn:eigs_nospring_nodamp}
-   \lambda=\frac{\frac{1}{2}\rho U\mathcal{A}a_1}{(m+m_a)}.
- \end{equation}
-
- For reasonably heavy bodies, the impact of the added mass can also be neglected, to arrive at a definition of $\lambda$ as
- \begin{equation}
-   \label{eqn:eigs_nospring_nodamp}
-   \lambda=\frac{\frac{1}{2}\rho U\mathcal{A}a_1}{m}.
+   \lambda=\frac{\frac{1}{2}\rho U\mathcal{A}a_1}{(m)}.
  \end{equation}
@@
 
- where $H.O.T.$ respresents the higher order terms in $\dot{Y}$. The coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
+ where $H.O.T.$ represents the higher order terms in $\dot{Y}$. The coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
  \begin{equation}
@@
 For a given geometry and Reynolds number, $\Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter.
-As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.
+As it is assumed that during galloping the stiffness plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.
 In fact, in the classic paper on galloping from \citet{Parkinson1964}, galloping data from wind tunnel tests is presented in terms of a parameter that can be shown to be the same as $\Gamma_2$.
@@
  % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
- \section{Results}
- \label{sec:results}
+
+ The range of incident flow angles where $C_y$ remains positive is narrow at $\reynoldsnumber=200$ ($0^\circ <\theta \leq$ $7^\circ$) compared to $\reynoldsnumber=22300$ ($0^\circ <\theta \leq 15^\circ$).
+This feature is what sustains galloping.
+Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating body, as demonstrated by equation \ref{power_alt}.
+Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; from body to fluid.
+Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=200$ compared to $\reynoldsnumber=22300$, it is expected that the transferred power at $\reynoldsnumber=200$ is significantly lower than at $\reynoldsnumber=22300$.
 
@@
   \input{../figure/collapsed_data}
+ \subsection{Displacement, velocity and power}
 
-  \input{../figure/m_star_collapsed}
-  \input{../figure/mstar_parkinson}
+ A similar result to \cite{Barrero-Gil2010a} could be observed in figure \ref{fig:uncollapsed_data} (f)  where the peak power remains the same but the \ustar which corresponds to the peak power shifts to the right as the damping ratio is increased.
+comparing Figures \ref{fig:uncollapsed_data} and \ref{fig:collapsed_data} it is evident that the velocity and mean power data are well collapsed when represented by \massdamp derived using natural time scales earlier in this article compared to the conventional VIV parameters.
+Thus reinforcing the fact that unlike in VIV power transfer is not bounded by a resonant range of frequencies.
+
+\subparagraph{limitation of the quasi-steady hypothesis at low Reynolds numbers}
+
+Work done by \cite{Joly2012} has also been focused on the displacement of a body under galloping at low Reynolds numbers as well as at zero or minimal damping.
+Therefore studies were carried out analyse the behaviour of the velocity as the damping is increased.
+The quasi-steady results were compared with the DNS results.
+From the comparison it was found out that the discrepancy of the power output is quite high as \massdamp is increased.
+
+ \input{../figure/spectrum_pi_1_10}

### 2014-07-03 research/paper/main/article.tex
spectum plots

@@
 This enables the model to provide accurate predictions even at low mass ratios where galloping excitation is suppressed or not present.
-In this study, the forcing due to vortex shedding in low \reynoldsnumber\ cases is incorporated using a sinusoidal forcing function $F_0\sin{\omega_{s}t}$ added to the right-hand side of equation \ref{equationofmotion}.
-Here, $\omega_{s}$ and $F_0$ represent the angular vortex shedding frequency and the maximum force due to shedding respectively.
-Thus, the final equation for the modified QSS model is
+However, in this study we also focus on isolating the regions where the QSS model predicts well and therefore the additional sinusoidal forcing function is disregarded.
 
@@
 \label{final_equation_motion}
-m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7 \Bigg){+} F_0\sin{(\omega_s t)}.
-\end{equation}
+m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal  {A} \Bigg(a_1\left(\frac{\dot{y}}{U}\right){+}a_3\left(\frac{\dot{y}}{U}\right)^3{+}a_5\left(\frac{\dot{y}}{U}\right)^5{+}a_7\left(\frac{\dot{y}}{U}\right)^7}.
+\end{equation}%
 
@@
 
-\subparagraph{limitation of the quasi-steady hypothesis at low Reynolds numbers}
+\subsection{limitations of the quasi-steady hypothesis at low Reynolds numbers}
 
-Work done by \cite{Joly2012} has also been focused on the displacement of a body under galloping at low Reynolds numbers as well as at zero or minimal damping.
-Therefore studies were carried out analyse the behaviour of the velocity as the damping is increased.
-The quasi-steady results were compared with the DNS results.
-From the comparison it was found out that the discrepancy of the power output is quite high as \massdamp is increased.
+\cite{Joly2012} showed that the displacement data obtained using the QSS assumption and DNS agree well at low Reynolds numbers, with the modification implemented to the oscillator equation which accounts for the vortex shedding.
+These data were obtained at zero damping levels.
+Since the current study was focused on the power transfer, more focus was put on analyzing he behaviour od the velocity as the damping is increased.
+The comparison between the QSS and the DNS results revealed that the discrepancy of the power data  increases significantly as \massdamp \ is increased.
+From figure \ref{fig:spectrum_pi1_10} (powers spectrum analysis done on the DNS results) it is evident that the relative strength of the galloping signal decreases as the \massdamp \ is increased from $ 0 \rightarrow 0.7$.
+Therefore the influence of the vortex shedding becomes more significant and the interactions between galloping and shedding become more complex as the damping is increased.
 
  \input{../figure/spectrum_pi_1_10}
+ \input{../figure/power_data}

### 2014-07-03 research/paper/main/article.tex
3rd july

--- 2014-06-09 research/paper/main/article.tex
@@
 
-These two definitions show two important interpretations of the power with respect to any energy production device.
+ \hilight{have to repharase} These two definitions show two important interpretations of the power with respect to any energy production device.
 The first shows that power will be high for situations where the damping coefficient is high, and the transverse velocity is consistently high.
@@
   \input{../figure/collapsed_data}
+
  \subsection{Displacement, velocity and power}
@@
 
-\subparagraph{limitation of the quasi-steady hypothesis at low Reynolds numbers}
+\subsection{limitation of the quasi-steady hypothesis at low Reynolds numbers}
 
-Work done by \cite{Joly2012} has also been focused on the displacement of a body under galloping at low Reynolds numbers as well as at zero or minimal damping.
-Therefore studies were carried out analyse the behaviour of the velocity as the damping is increased.
-The quasi-steady results were compared with the DNS results.
-From the comparison it was found out that the discrepancy of the power output is quite high as \massdamp is increased.
+The QSS hypothesis assumes that the only force driving the system is the instantaneous lift generated by the induced velocity.
+However, vortex shedding is also present in this system.
+Therefore, an essential assumption when this model is used is that the effect of vortex shedding is minimal.
+Hence, the model has been always used at high \reynoldsnumber and high mass ratios.
+The present study is focused on quantifying the limiting parameters of the QSS model at low Reynolds numbers by providing a comparison with DNS results.
 

### 2014-07-03 research/paper/main/article.tex

@@
  \input{../figure/spectrum_pi_1_10}
+ \input{../figure/power_data}
